### 2020-06-03 paper-v0.tex
added material from previous paper to work on

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
Polytechnic of Turin\\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}

\section{Background}
\subsection{Peer-review}
Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times. Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications. This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research. Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work. On top of this, author-level metrics that measure the scientific impact and productivity of academics, such as the h-index, and are taken into account by the funding agencies, are purely based on the number of citations per each publications while neglecting the full spectrum of scientific contributions (software, data collection, presentations, reviews…). Therefore, peer-reviewing is an intellectual investment without any external return for researchers’ career. A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5]. Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas). Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...). These trust problems are one of the major issues facing scholarly communication.
\subsection{Blockchain for science}
An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8]. As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1]. Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic. Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers. From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).

\section{System concept}
For the above mentioned reasons, we propose an incentive-based protocol called Ants-Review to reward open peer-reviews while preserving the anonymity of the reviewers. The name originates from the idea that the work behind a finished scientific paper resembles a complex organism such as an anthill, which emerges from the sum of many individualities: in it, all contributions (even if ‘micro’) are essential to the whole and are worth recognition.
This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.

\subsection{Design}
When authors of a paper submit their draft to an open access journal or preprint, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor. Reviews fulfilling the smart-contract requirements are audited by external editors who validate the content. If the reviews are accepted (bounty fulfillment), reviewers awarded a token, an internal digital currency specific for this bounty, called ‘ANT’. The ideal scenario envisages multiple contributions both from the reviewers actors and the editors actors. To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].

\subsection{Implementation}
As an initial Proof of Concept (PoC) we wrote our smart contract with Solidity [19], a contract-oriented, high-level language designed for implementing smart contracts on the Ethereum Virtual Machine (EVM). We relied on tools and pipelines from Truffle Suite [18], a development environment and testing framework for Ethereum, and Ganache [17], its private test blockchain tool for the Ethereum ecosystem.
We adopted a standard template for smart contracts (Standard Bounties) like that from Bounties-Network [16]. The bounty contains some requirements for fulfillment like: time-stamped deadline, value of the bounty. Within AntsReview access management is granted to three actors: the owner of the deployed smart contract AntsReview.sol, a Pauser, assigned to the owner of the deployed smart contract, able to Pause the functions in case of emergency and the authors of the paper or AntsReview Issuers;   upon which we added four options expressed by the functions: issueAntReview( ), to instantiate a new bounty; fulfillAntReview(), to submit a fulfillment for the given AntReview; acceptFulfillment(): to accept a given fulfillment; cancelAntReview(), to cancel the AntReview and send the funds back to the issuer. Evidence of the fulfillments are tracked via  IPFS hashing.
For code optimization we used OpenZeppelin Contracts, a library for secure smart contract development. We deployed the contract on an Ethereum Test Network, Rinkeby Testnet [21], a proof-of-authority blockchain.
The dApp was implemented with an user interface (UI) to interact with the smart contract: for that we used the libraries React.js and RimbleUI.

\subsubsection{Future steps}
Future integrations that were not contemplated in the above presented PoC /demo but that we plan to cover for the development of the AntsReview bounty include: an ERC20 token, named Ant,  symbol ANT; Proof of Existence (PoE) service; memory storage on IPFS; moreover, since we wanted to anonymize peer-reviews to protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum. Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is. We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol [15]. We will also use Ethereum Name Service (ENS) [14] to allow for human-readable Ethereum addresses; Upgradability Design Patterns [13] via Proxy, to allow the logic to be extended and improved; De-Fi integrations such as Dai, Chai. Finally, we would like to propose for AntsReview Quadratic Funding, a design written by Vitalik Buterin and co [20] and which applies concepts inspired by quadratic voting to funding public goods.

\section{Conclusion and Discussions}
In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.

\section{Supplementary material}
Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references.bib}

\end{document}

### 2020-06-03 paper-v0.tex
small changes

@@
 We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review.
-We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.
+We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain ecosystem.
 
 \section{Supplementary material}
-Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
+The source code is open and available at the Github repository. A demo of the project is available at Youtube channel.
 \section{CRediT Authorship Contribution Statement}

### 2020-06-04 paper-v1.tex
add tech points + test solidity smart contract + cleanup
add implementation intro

--- 2020-06-03 paper-v0.tex
@@
 \usepackage{graphicx}
+\input{solidity-highlighting.tex}	% copy the file from this repo
 % Used for displaying a sample figure. If possible, figure files should
@@
 \email{bianca.trovo@alumni.unitn.it}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
+\and
 Polytechnic of Turin\\
@@
 \subsection{Implementation}
-As an initial Proof of Concept (PoC) we wrote our smart contract with Solidity [19], a contract-oriented, high-level language designed for implementing smart contracts on the Ethereum Virtual Machine (EVM).
-We relied on tools and pipelines from Truffle Suite [18], a development environment and testing framework for Ethereum, and Ganache [17], its private test blockchain tool for the Ethereum ecosystem.
-We adopted a standard template for smart contracts (Standard Bounties) like that from Bounties-Network [16].
-The bounty contains some requirements for fulfillment like: time-stamped deadline, value of the bounty.
-Within AntsReview access management is granted to three actors: the owner of the deployed smart contract AntsReview.sol, a Pauser, assigned to the owner of the deployed smart contract, able to Pause the functions in case of emergency and the authors of the paper or AntsReview Issuers;   upon which we added four options expressed by the functions: issueAntReview( ), to instantiate a new bounty; fulfillAntReview(), to submit a fulfillment for the given AntReview; acceptFulfillment(): to accept a given fulfillment; cancelAntReview(), to cancel the AntReview and send the funds back to the issuer.
-Evidence of the fulfillments are tracked via  IPFS hashing.
-For code optimization we used OpenZeppelin Contracts, a library for secure smart contract development.
-We deployed the contract on an Ethereum Test Network, Rinkeby Testnet [21], a proof-of-authority blockchain.
-The dApp was implemented with an user interface (UI) to interact with the smart contract: for that we used the libraries React.js and RimbleUI.
+AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network, ERC20, AZTEC Protocol, IPFS, Proof of Existence, DAO, ...
+\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
+\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
+\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:
+
+\begin{enumerate}}
+  \item \textbf{Bounty} - manage access management and the basic system.
+  \item \textbf{Token Economics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
+  \item \textbf{Privacy} - mantains the anonymity of the system via AZTEC Protocol.
+  \item \textbf{DAO} - manage the governance of the system via DemocracyDAO.
+\end{enumerate}
+
+\subsubsection{Bounty}
+
+\begin{lstlisting}[language=Solidity]
+pragma solidity 0.4.16;
+
+contract TestContract {
+
+	string private myString = "foo";
+
+	function getString() constant returns (string) {
+	    return myString;
+	}
+
+	function setString (string _string) {
+	    myString = _string;
+	}
+}
+\end{lstlisting}
+
+\subsubsection{Token Economics}
+
+\subsubsection{Quadratic Funding}
+
+\subsubsection{Privacy}
+
+\subsubsection{DAO}
 

### 2020-06-04 paper-v1.tex
Updates from Overleaf

--- 2020-06-03 paper-v0.tex
@@
 
+\subsubsection{Bounty}
+
+\begin{lstlisting}[language=Solidity]
+pragma solidity 0.4.16;
+
+contract TestContract {
+
+	string private myString = "foo";
+
+	function getString() constant returns (string) {
+	    return myString;
+	}
+
+	function setString (string _string) {
+	    myString = _string;
+	}
+}
+\end{lstlisting}
+
+\subsubsection{Token Economics}
+
+\subsubsection{Quadratic Funding}
+
+\subsubsection{Privacy}
+
+\subsubsection{DAO}
+
 \subsubsection{Future steps}
@@
 \section{CRediT Authorship Contribution Statement}
-Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing.
+Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review \& editing.
 Nazzareno Massari: Project administration, Methodology, Validation, Software development.

### 2020-06-05 paper-v1.tex
Updates from Overleaf
add smart contracts flow-chart
update smart contracts flow-chart

--- 2020-06-04 paper-v1.tex
@@
 \usepackage{graphicx}
+\graphicspath{ {./img/} }
+
 \input{solidity-highlighting.tex}	% copy the file from this repo
@@
 %
-\authorrunning{B. Trovò et al.}
+\authorrunning{B. Trovò et N. Massari}
 % First names are abbreviated in the running head.
@@
 \section{Introduction}
+blockchain for science here and application to open science and to peer review as a specific case
+An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
+As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1].
+Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
+Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
+From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
 
 \section{Background}
-\subsection{Peer-review}
+\subsection{Peer-review: problem}
 Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination.
@@
 These trust problems are one of the major issues facing scholarly communication.
-\subsection{Blockchain for science}
-An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
-As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1].
-Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
-Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
-From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
+
+\subsubsection{Types of peer-review}
+\begin{itemize}
+    \item single-blind peer review
+    \item double-blind peer review
+    \item transparent peer review
+\end{itemize}
+
+\subsubsection{Traditional editorial process}
+\begin{enumerate}
+    \item The author submits a manuscript to the journal.
+    \item  An editor is assigned to the manuscript: at this stage the assessment of the paper concerns the requirements of the journal's Author's Guideline (composition, sections...).
+    \item
+
+\end{enumerate}2.
+3.
+The editorial team decides whether to send the manuscript out to review.
+If the decision is not to send the manuscript for review, the editor contacts the author with the decision.
+4.
+The editor assigns potential reviewers to the manuscript and the author is notiﬁed.
+5.
+Reviewers agree to review the manuscript.
+6.
+Reviewers submit their reports to the editor.
+7.
+The editorial team discusses the reports and the editor makes the ﬁnal decision.
+This process may involve further consultation with the reviewers and editor-mediated communications between the reviewers.
+8.
+The editor contacts the author with the decision.
+9.
+If the decision is negative, the author can choose to transfer their manuscript to another journal.
+If the manuscript was peer reviewed the referee comments are also transferred.
+Please see our Manuscript Transfer FAQ for more information about this service.
+\subsection{Related work}
+
+Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
+
+Crossref primary DOI provider, announced that review reports could be now registered as part of their services
+Publons provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
+ScienceOpen
+DEIP
+Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
+Peerage of Science that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews. 
+Blockchain for Peer Review, pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
+
+The project will develop a protocol where information about peer review activities (submitted by publishers) are stored on a blockchain.
+This will allow the review process to be independently validated, and data to be fed to relevant vehicles to ensure recognition and validation for reviewers.
+By sharing peer review information, while adhering to laws on privacy, data protection and confidentiality, we will foster innovation and increase interoperability.
 
@@
 \subsection{Design}
+
+Anonymity
+Accountability
+Reputation
+Reward
+Gamification model
+
+open identities open reports open participation open interaction open platform ('decoupled review')
+Basic architecture 
 When authors of a paper submit their draft to an open access journal or preprint, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor.
@@
 To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].
+Scenario 1 (journal-dependent)
+Scenario 2 (community-driven): peer-review is decoupled from journal
 
@@
 \newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:
+
+\includegraphics[scale=0.28]{Ants-Review}
 
@@
 
-\section{Conclusion and Discussions}
-In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process.
+\section{Discussions}
+
+- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declaired that will do the same.
+
+- new business model?
+at some point pre-print platforms (dissemination) might want to integrate peer-review (validation) into their platforms - dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt: how will they justify their added value?
+as Tennant points out: branding archiving
+
+- peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction
+
+- community-organized peer  reviews: peer reviews will be more and more out of the hands of publishers, researchers will be the ones seeking the papers to review (like in Rubriq).
+
+future of quality control and moderation: open participation model, community-driven | certification and reputation: expansion of reviewer pool with fewer barriers to enter and more inclusion of young scientists, reputation build within community and not journals
+
+- portable peer review not only within a consortium of journals
+
+-value of peer review as 'academic capital' recognized by research funders and hiring committees
+
+-a bit off topic but: automated peer review (services such as StatReviewers) might fasten the formal aspects of the job allowing reviewers to focus on the content.
+
+\section{Conclusion}
+In this paper we addressed a central problem within the quality control academic dissemination: the peer-review process.
 We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication.
@@
 
-\section{Supplementary material}
+\subsubsection{Supplementary material}
 Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
-\section{CRediT Authorship Contribution Statement}
-Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing.
-Nazzareno Massari: Project administration, Methodology, Validation, Software development.
-Both authors equally contributed and supervised the project.
-\section{Declaration of Competing Interest}
+
+\subsubsection{CRediT Authorship Contribution Statement}
+TDB
+
+\subsubsection{Declaration of Competing Interest}
 The authors declare no competing interests.
+
+\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi for his comments and edits.
 

### 2020-06-05 paper-v1.tex
add bounty tech point

--- 2020-06-04 paper-v1.tex
@@
 \subsection{Implementation}
-AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network, ERC20, AZTEC Protocol, IPFS, Proof of Existence, DAO, ...
+AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
 \newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
@@
 
-\begin{enumerate}}
+\includegraphics[scale=0.28]{AntsReview}
+
+\begin{enumerate}
   \item \textbf{Bounty} - manage access management and the basic system.
@@
   \item \textbf{Privacy} - mantains the anonymity of the system via AZTEC Protocol.
-  \item \textbf{DAO} - manage the governance of the system via DemocracyDAO.
 \end{enumerate}
@@
 \subsubsection{Bounty}
+AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
+\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
+\begin{itemize}
+  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
+  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
+  \item to send the amount of ether for the reward.
+\end{itemize}
+
+AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
 
 \begin{lstlisting}[language=Solidity]
-pragma solidity 0.4.16;
 
-contract TestContract {
+pragma solidity 0.6.8;
 
-	string private myString = "foo";
+import "@openzeppelin/contracts/access/AccessControl.sol";
 
-	function getString() constant returns (string) {
-	    return myString;
-	}
+contract AntsReviewRoles is AccessControl {
 
-	function setString (string _string) {
-	    myString = _string;
-	}
+/// Roles
+bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
+bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
+
 }
 \end{lstlisting}
+
+In this way, only the Issuer (author) can create a new AntReview.
+\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
+\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
+\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
+One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
+\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with Bitcoin and Blockchain.
+\newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
+\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
 

### 2020-06-05 paper-v1.tex
update bounty tech point

@@
 \newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
-One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
-\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with Bitcoin and Blockchain.
+\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
+\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
 \newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.

### 2020-06-05 paper-v1.tex

--- 2020-06-05 paper-v1.tex
@@
 
-\includegraphics[scale=0.28]{Ants-Review}
+\includegraphics[scale=0.28]{AntsReview}
 
-\begin{enumerate}}
+\begin{enumerate}
   \item \textbf{Bounty} - manage access management and the basic system.
@@
 \subsubsection{Bounty}
+AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
+\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
+\begin{itemize}
+  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
+  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
+  \item to send the amount of ether for the reward.
+\end{itemize}
+
+AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
 
 \begin{lstlisting}[language=Solidity]
-pragma solidity 0.4.16;
 
-contract TestContract {
+pragma solidity 0.6.8;
 
-	string private myString = "foo";
+import "@openzeppelin/contracts/access/AccessControl.sol";
 
-	function getString() constant returns (string) {
-	    return myString;
-	}
+contract AntsReviewRoles is AccessControl {
 
-	function setString (string _string) {
-	    myString = _string;
-	}
+/// Roles
+bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
+bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
+
 }
 \end{lstlisting}
+
+In this way, only the Issuer (author) can create a new AntReview.
+\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
+\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
+\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
+\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
+\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
+\newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
+\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
 

### 2020-06-05 paper-v1.tex
Updates from Overleaf

@@
 %
-\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
+\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{}}
 %
@@
 \author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
-Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
+Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
 %
@@
 \and
-Polytechnic of Turin\\
+Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
+Independent blockchain engineer, London, UK \\
 \email{nazzareno@nazzarenomassari.com}}
@@
 
-\subsubsection{Traditional editorial process}
+\subsubsection{Traditional peer-review process}
 \begin{enumerate}
     \item The author submits a manuscript to the journal.
-    \item  An editor is assigned to the manuscript: at this stage the assessment of the paper concerns the requirements of the journal's Author's Guideline (composition, sections...).
-    \item
+    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
+    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria.
+If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
+    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers.
+Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
+    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability.
+They then accept or decline.
+If they decline, they might suggest alternative reviewers.
+Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
+    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified.
+The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves.
+    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
+    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
+    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
+The same reviewers might be contacted again and if they want they can follow up the peer-review process.
+    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.
 
-\end{enumerate}2.
-3.
-The editorial team decides whether to send the manuscript out to review.
-If the decision is not to send the manuscript for review, the editor contacts the author with the decision.
-4.
-The editor assigns potential reviewers to the manuscript and the author is notiﬁed.
-5.
-Reviewers agree to review the manuscript.
-6.
-Reviewers submit their reports to the editor.
-7.
-The editorial team discusses the reports and the editor makes the ﬁnal decision.
-This process may involve further consultation with the reviewers and editor-mediated communications between the reviewers.
-8.
-The editor contacts the author with the decision.
-9.
-If the decision is negative, the author can choose to transfer their manuscript to another journal.
-If the manuscript was peer reviewed the referee comments are also transferred.
-Please see our Manuscript Transfer FAQ for more information about this service.
+\end{enumerate}
+
 \subsection{Related work}
@@
 This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
-
-\subsection{Design}
-
 Anonymity
@@
 open identities open reports open participation open interaction open platform ('decoupled review')
-Basic architecture 
-When authors of a paper submit their draft to an open access journal or preprint, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor.
+
+\subsection{Design}
+
+\subsubsection{AnstReview process: scenario 1  (journal-dependent)}\\
+
+\begin{enumerate}
+    \item The author submits a manuscript to the journal.
+    \item If the papers passes stage 2-3 of editorial decision (appropriateness of style and coherence with the journal's scope)
+    \item the editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
+    \item (footnote?) the bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
+    \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
+    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
+    \item Not all reviews will have the same quality and depth.
+However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting.
+\end{enumerate}
+When authors of a paper submit their draft to an open access journal or pre-print, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor.
 Reviews fulfilling the smart-contract requirements are audited by external editors who validate the content.
@@
 To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].
-Scenario 1 (journal-dependent)
+
 Scenario 2 (community-driven): peer-review is decoupled from journal
-
+or to the pre-print service or to an hypothetical AntsReview platform).
 \subsection{Implementation}
-AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
+AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network, ERC20, AZTEC Protocol, IPFS, Proof of Existence, DAO, ...
 \newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
@@
 \subsubsection{Bounty}
-AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
-\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
-\begin{itemize}
-  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
-  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
-  \item to send the amount of ether for the reward.
-\end{itemize}
-
-AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
 
 \begin{lstlisting}[language=Solidity]
+pragma solidity 0.4.16;
 
-pragma solidity 0.6.8;
+contract TestContract {
 
-import "@openzeppelin/contracts/access/AccessControl.sol";
+	string private myString = "foo";
 
-contract AntsReviewRoles is AccessControl {
+	function getString() constant returns (string) {
+	    return myString;
+	}
 
-/// Roles
-bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
-bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
-
+	function setString (string _string) {
+	    myString = _string;
+	}
 }
 \end{lstlisting}
-
-In this way, only the Issuer (author) can create a new AntReview.
-\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
-\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
-\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
-\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
-\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
-\newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
-\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
 

### 2020-06-05 paper-v1.tex
added point about review process and how it would change with AntsReview (scenario 1/ scenario 2) -- WATCH OUT INCONGRUENCES

@@
 
-\subsubsection{AnstReview process: scenario 1  (journal-dependent)}\\
+\subsubsection{AnstReview process: scenario 1  (journal-dependent)}
 
@@
 However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting.********* POINT OF FAILURE?
+who votes?
+
 \end{enumerate}
-When authors of a paper submit their draft to an open access journal or pre-print, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor.
-Reviews fulfilling the smart-contract requirements are audited by external editors who validate the content.
-If the reviews are accepted (bounty fulfillment), reviewers awarded a token, an internal digital currency specific for this bounty, called ‘ANT’.
-The ideal scenario envisages multiple contributions both from the reviewers actors and the editors actors.
-To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].
 
-Scenario 2 (community-driven): peer-review is decoupled from journal
+\subsubsection{AnstReview process: scenario 2  (community-driven):
+
+peer-review is decoupled from journal
 or to the pre-print service or to an hypothetical AntsReview platform).

### 2020-06-06 paper-v1.tex
few changes mostly on the style

@@
 %
-\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{}}
+\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
 %
@@
 %
-\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
+\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author} \and
 Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
@@
 blockchain for science here and application to open science and to peer review as a specific case
+
 An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
 As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1].
-Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
+Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
+\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
+\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
+\paragraph{Transparency} (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
 Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
@@
 \section{Background}
-\subsection{Peer-review: problem}
+\subsection{Peer-review: a flawed and outdated system}
 Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination.
 However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times.
-Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
-This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research.
-Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work.
-On top of this, author-level metrics that measure the scientific impact and productivity of academics, such as the h-index, and are taken into account by the funding agencies, are purely based on the number of citations per each publications while neglecting the full spectrum of scientific contributions (software, data collection, presentations, reviews…).
-Therefore, peer-reviewing is an intellectual investment without any external return for researchers’ career.
-A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5].
-Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas).
-Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...).
-These trust problems are one of the major issues facing scholarly communication.
-
-\subsubsection{Types of peer-review}
-\begin{itemize}
-    \item single-blind peer review
-    \item double-blind peer review
-    \item transparent peer review
-\end{itemize}
-
-\subsubsection{Traditional peer-review process}
+\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
+\paragraph{Traditional peer-review process}
 \begin{enumerate}
@@
 \end{enumerate}
+\subsubsection{It's unaccredited and unpaid.} This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research.
+Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work.
+On top of this, author-level metrics that measure the scientific impact and productivity of academics, such as the h-index, and are taken into account by the funding agencies, are purely based on the number of citations per each publications while neglecting the full spectrum of scientific contributions (software, data collection, presentations, reviews…).
+Therefore, peer-reviewing is an intellectual investment without any external return for researchers’ career.
+A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5].
+\subsubsection{It's vulnerable to bias and fraud.} Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas).
+Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...).
+These trust problems are one of the major issues facing scholarly communication.
+
+\subsubsection{Types of peer-review}
+\begin{itemize}
+    \item single-blind peer review
+    \item double-blind peer review
+    \item transparent peer review
+    open identities open reports open participation open interaction open platform ('decoupled review')
+\end{itemize}
 
 \subsection{Related work}
+Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
+In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
+\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
+\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
+ScienceOpen
+\emph{DEIP}
+Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
+\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews. 
+\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
+\emph{ReviewCoin}
+\emph{I8X Platform}
 
-Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
-
-Crossref primary DOI provider, announced that review reports could be now registered as part of their services
-Publons provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
-ScienceOpen
-DEIP
-Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
-Peerage of Science that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews. 
-Blockchain for Peer Review, pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
-
-The project will develop a protocol where information about peer review activities (submitted by publishers) are stored on a blockchain.
-This will allow the review process to be independently validated, and data to be fed to relevant vehicles to ensure recognition and validation for reviewers.
-By sharing peer review information, while adhering to laws on privacy, data protection and confidentiality, we will foster innovation and increase interoperability.
+\subsection{Blockchain solution}
 
@@
 This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
-Anonymity
-Accountability
-Reputation
-Reward
-Gamification model
-
-open identities open reports open participation open interaction open platform ('decoupled review')
+\paragraph{Anonymity} zSNARK
+\paragraph{Accountability} hash
+\paragraph{Reward} bounty
 
@@
 
-\subsubsection{AnstReview process: scenario 2  (community-driven):
+\subsubsection{AnstReview process: scenario 2  (community-driven)}:
+
+\begin{enumerate}
+    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform).
+    \item The paper is accepted by the community for revision in its whatever format.
+    \item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
+    \item (footnote?) the bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
+    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community/contributors.
+    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
+    \item Not all reviews will have the same quality and depth.
+However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community with Quadratic Voting.
+    \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
+Since it's in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit.
+It will also fuel ethical behaviour.
+
+    \end{enumerate}
 
 peer-review is decoupled from journal
-or to the pre-print service or to an hypothetical AntsReview platform).
+or
+
 \subsection{Implementation}
@@
 
-\subsubsection{Quadratic Funding}
+\subsubsection{Quadratic Voting} I don't see the point of introducing QF here. Is it already implemented or it's just in the idea?
 
-\subsubsection{Privacy}
+\subsubsection{Privacy}.
+AZTEC protocol is a cryptographic protocol combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
 

### 2020-06-06 paper-v1.tex
swapped things a bit

@@
 This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
-\paragraph{Anonymity} zSNARK
-\paragraph{Accountability} hash
-\paragraph{Reward} bounty
+
+\subsubsection{Accountability} hash
+\subsubsection{Reward} bounty
+\subsubsection{Quadratic Voting} I don't see the point of introducing QF here. Is it already implemented or it's just in the idea?
+
+\subsubsection{Privacy/anonymity}.
+To protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
+Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
+We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol.
+AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
 
@@
 \subsection{Implementation}
+\subsubsection{Back-end} ??
 AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
@@
 
-\subsubsection{Token Economics}
+\subsubsection{Token Economics} what is this?
 
-\subsubsection{Quadratic Voting} I don't see the point of introducing QF here. Is it already implemented or it's just in the idea?
-
-\subsubsection{Privacy}.
-AZTEC protocol is a cryptographic protocol combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
-
-\subsubsection{DAO}
-
-\subsubsection{Future steps}
-Future integrations that were not contemplated in the above presented PoC /demo but that we plan to cover for the development of the AntsReview bounty include: an ERC20 token, named Ant,  symbol ANT; Proof of Existence (PoE) service; memory storage on IPFS; moreover, since we wanted to anonymize peer-reviews to protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
-Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
-We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol [15].
-We will also use Ethereum Name Service (ENS) [14] to allow for human-readable Ethereum addresses; Upgradability Design Patterns [13] via Proxy, to allow the logic to be extended and improved; De-Fi integrations such as Dai, Chai.
-Finally, we would like to propose for AntsReview Quadratic Funding, a design written by Vitalik Buterin and co [20] and which applies concepts inspired by quadratic voting to funding public goods.
+\subsubsection{Front-end}
 
 \section{Discussions}
-
+\subsection{A new community-driven standard?}
 - a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declaired that will do the same.
@@
 -a bit off topic but: automated peer review (services such as StatReviewers) might fasten the formal aspects of the job allowing reviewers to focus on the content.
+
+\subsubsection{Perspectives for a Decentralized Autonomours Organization (DAO)}
 

### 2020-06-06 paper-v1.tex
editorial process source

@@
 \subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
-\paragraph{Traditional peer-review process}
+\paragraph{Traditional peer-review process} This section takes inspiriration from the editorial processes at Nature Methods and Wiley.
 \begin{enumerate}
@@
 \subsection{Implementation}
-\subsubsection{Back-end} ??
+\subsubsection{Back-end} ?? BETTER HERE SAY WHAT WE HAVE ALREADY DONE, PRESENTED 
 AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
@@
 
-\subsubsection{Bounty}
+\subsubsection{Token economy and Bounty}
 AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
@@
 \newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
-
-\subsubsection{Token Economics} what is this?
 

### 2020-06-06 paper-v1.tex
acknowledgements updated

--- 2020-06-06 paper-v1.tex
@@
 Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
-Independent blockchain engineer, London, UK \\
+Independent Blockchain Engineer, London, UK \\
 \email{nazzareno@nazzarenomassari.com}}
@@
 \subsection{Implementation}
-\subsubsection{Back-end} ??
-AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
+AntsReview is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
 \newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
@@
   \item \textbf{Token Economics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
-  \item \textbf{Privacy} - mantains the anonymity of the system via AZTEC Protocol.
+  \item \textbf{Privacy} - maintains the anonymity of the system via AZTEC Protocol.
 \end{enumerate}
@@
 AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
-\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
+\newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
 \begin{itemize}
   \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
-  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
+  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
   \item to send the amount of ether for the reward.
@@
 \newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
-\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
-\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
-\newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
+\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document".
+\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
+\newline In Ethereum the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
 \newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
 
-\subsubsection{Token Economics} what is this?
+\subsubsection{Token Economics}
 
-\subsubsection{Front-end}
+\subsubsection{Privacy}
 
@@
 \subsection{A new community-driven standard?}
-- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declaired that will do the same.
+- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declared that will do the same.
 
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi for his comments and edits.
+\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for internal review and useful comments.
 

### 2020-06-06 paper-v1.tex
add appendix smart contracts

--- 2020-06-06 paper-v1.tex
@@
 %
-\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
+\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
 %
@@
 %
-\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author} \and
-Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
+\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
+Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
 %
@@
 \and
-Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
-Independent blockchain engineer, London, UK \\
+Polytechnic of Turin\\
 \email{nazzareno@nazzarenomassari.com}}
@@
 \section{Introduction}
-blockchain for science here and application to open science and to peer review as a specific case
-
-An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
-As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1].
-Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
-\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
-\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
-\paragraph{Transparency} (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
-Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
-From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
 
 \section{Background}
-\subsection{Peer-review: a flawed and outdated system}
+\subsection{Peer-review}
 Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination.
 However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times.
-\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
-\paragraph{Traditional peer-review process}
-\begin{enumerate}
-    \item The author submits a manuscript to the journal.
-    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
-    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria.
-If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
-    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers.
-Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
-    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability.
-They then accept or decline.
-If they decline, they might suggest alternative reviewers.
-Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
-    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified.
-The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves.
-    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
-    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
-    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
-The same reviewers might be contacted again and if they want they can follow up the peer-review process.
-    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.
-
-\end{enumerate}
-\subsubsection{It's unaccredited and unpaid.} This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research.
+Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
+This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research.
 Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work.
@@
 A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5].
-\subsubsection{It's vulnerable to bias and fraud.} Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas).
+Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas).
 Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...).
 These trust problems are one of the major issues facing scholarly communication.
-
-\subsubsection{Types of peer-review}
-\begin{itemize}
-    \item single-blind peer review
-    \item double-blind peer review
-    \item transparent peer review
-    open identities open reports open participation open interaction open platform ('decoupled review')
-\end{itemize}
-
-\subsection{Related work}
-Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
-In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
-\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
-\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
-ScienceOpen
-\emph{DEIP}
-Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
-\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews. 
-\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
-\emph{ReviewCoin}
-\emph{I8X Platform}
-
-\subsection{Blockchain solution}
+\subsection{Blockchain for science}
+An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
+As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1].
+Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]: decentralisation, taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process; immutability of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper; transparency (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
+Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
+From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
 
@@
 
-\subsubsection{Accountability} hash
-\subsubsection{Reward} bounty
-\subsubsection{Quadratic Voting} I don't see the point of introducing QF here. Is it already implemented or it's just in the idea?
-
-\subsubsection{Privacy/anonymity}.
-To protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
-Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
-We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol.
-AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
-
 \subsection{Design}
-
-\subsubsection{AnstReview process: scenario 1 (journal-dependent)}
-
-\begin{enumerate}
-    \item The author submits a manuscript to the journal.
-    \item If the papers passes stage 2-3 of editorial decision (appropriateness of style and coherence with the journal's scope)
-    \item the editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
-    \item (footnote?) the bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
-    \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
-    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
-    \item Not all reviews will have the same quality and depth.
-However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting.********* POINT OF FAILURE?
-who votes?
-
-\end{enumerate}
-
-\subsubsection{AnstReview process: scenario 2 (community-driven)}:
-
-\begin{enumerate}
-    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform).
-    \item The paper is accepted by the community for revision in its whatever format.
-    \item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
-    \item (footnote?) the bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
-    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community/contributors.
-    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
-    \item Not all reviews will have the same quality and depth.
-However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community with Quadratic Voting.
-    \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
-Since it's in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit.
-It will also fuel ethical behaviour.
-
-    \end{enumerate}
-
-peer-review is decoupled from journal
-or
+When authors of a paper submit their draft to an open access journal or preprint, they can instantiate a call (bounty issuance) for the paper-review whose fulfillment rules are set in a smart-contract to which any contributor can participate either as a reviewer or as editor.
+Reviews fulfilling the smart-contract requirements are audited by external editors who validate the content.
+If the reviews are accepted (bounty fulfillment), reviewers awarded a token, an internal digital currency specific for this bounty, called ‘ANT’.
+The ideal scenario envisages multiple contributions both from the reviewers actors and the editors actors.
+To reinforce ethical behaviour and the system will implement on AntsReview a quadratic funding [20].
 
 \subsection{Implementation}
-\subsubsection{Back-end} ??
 AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
@@
 AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
+\newline It also integrates a circuit breaker deisgn pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
 
@@
 \newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
-\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
+\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document"[cit.].
 \newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
@@
 
-\subsubsection{Token Economics} what is this?
+\subsubsection{Token Economics}
+AntsReview, to incintivize the system integrates a native ERC20 Token called Ant that is used in the protocol to pay for AntReview and also wrapped into zkAnt to allow anonymous payments.
 
-\subsubsection{Front-end}
+The code below show the implementation of Ant Token via ERC20PresetMinterPauser.sol inherited from OpenZeppelin Library, a preset of ERc20 inlcuding an access management and a circuit breaker pattern.
 
-\section{Discussions}
-\subsection{A new community-driven standard?}
-- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declaired that will do the same.
+\begin{lstlisting}[language=Solidity]
 
-- new business model?
-at some point pre-print platforms (dissemination) might want to integrate peer-review (validation) into their platforms - dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt: how will they justify their added value?
-as Tennant points out: branding archiving
+pragma solidity 0.6.8;
 
-- peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction
+import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
 
-- community-organized peer  reviews: peer reviews will be more and more out of the hands of publishers, researchers will be the ones seeking the papers to review (like in Rubriq).
+contract Ant is ERC20PresetMinterPauser {
 
-future of quality control and moderation: open participation model, community-driven | certification and reputation: expansion of reviewer pool with fewer barriers to enter and more inclusion of young scientists, reputation build within community and not journals
+  constructor()
+  ERC20PresetMinterPauser("Ant", "ANT")
+  public {
 
-- portable peer review not only within a consortium of journals
+  }
+}
+\end{lstlisting}
 
--value of peer review as 'academic capital' recognized by research funders and hiring committees
+\newline
 
--a bit off topic but: automated peer review (services such as StatReviewers) might fasten the formal aspects of the job allowing reviewers to focus on the content.
+\subsubsection{Privacy}
 
-\subsubsection{Perspectives for a Decentralized Autonomours Organization (DAO)}
+\subsubsection{Future steps}
+Future integrations that were not contemplated in the above presented PoC /demo but that we plan to cover for the development of the AntsReview bounty include: an ERC20 token, named Ant,  symbol ANT; Proof of Existence (PoE) service; memory storage on IPFS; moreover, since we wanted to anonymize peer-reviews to protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
+Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
+We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol [15].
+We will also use Ethereum Name Service (ENS) [14] to allow for human-readable Ethereum addresses; Upgradability Design Patterns [13] via Proxy, to allow the logic to be extended and improved; De-Fi integrations such as Dai, Chai.
+Finally, we would like to propose for AntsReview Quadratic Funding, a design written by Vitalik Buterin and co [20] and which applies concepts inspired by quadratic voting to funding public goods.
 
-\section{Conclusion}
-In this paper we addressed a central problem within the quality control academic dissemination: the peer-review process.
+\section{Conclusion and Discussions}
+In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process.
 We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication.
@@
 
-\subsubsection{Supplementary material}
+\section{Supplementary material}
 Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
-
-\subsubsection{CRediT Authorship Contribution Statement}
-TDB
-
-\subsubsection{Declaration of Competing Interest}
+\section{CRediT Authorship Contribution Statement}
+Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review \& editing.
+Nazzareno Massari: Project administration, Methodology, Validation, Software development.
+Both authors equally contributed and supervised the project.
+\section{Declaration of Competing Interest}
 The authors declare no competing interests.
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi for his comments and edits.
+\newpage
+
+\section{Appendix}
+
+\appendix
+
+\section{AntsReviewRoles.sol}
+
+\begin{lstlisting}[language=Solidity]
+
+  /// SPDX-License-Identifier: GPL-3.0
+  pragma solidity 0.6.8;
+
+  ///@title AntsReview
+  ///@author Nazzareno Massari
+  ///@notice AntsReviewRoles Access Management for Issuer and Peer-Reviewer
+  ///@dev All function calls are currently implemented without side effecs through TDD approach
+  ///@dev OpenZeppelin library is used for secure contract development
+
+  import "@openzeppelin/contracts/access/Ownable.sol";
+  import "@openzeppelin/contracts/access/AccessControl.sol";
+  import "@openzeppelin/contracts/utils/Pausable.sol";
+
+  contract AntsReviewRoles is Ownable, AccessControl, Pausable {
+
+    /// Roles
+    bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
+    bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
+    bytes32 public constant PAUSER_ROLE = keccak256("PAUSER_ROLE");
+
+    constructor() public {
+            _setupRole(DEFAULT_ADMIN_ROLE, owner());
+            _setupRole(PAUSER_ROLE, owner());
+    }
+
+      /// Modifiers
+      modifier onlyAdmin() {
+          require(isAdmin(msg.sender), "Caller is not an admin");
+          _;
+        }
+
+      modifier onlyIssuer() {
+          require(isIssuer(msg.sender), "Caller is not an issuer");
+          _;
+      }
+
+      modifier onlyPeerReviewer() {
+          require(isPeerReviewer(msg.sender), "Caller is not a peer-reviewer");
+          _;
+      }
+
+      /// Functions
+
+      function isAdmin(address account) public view returns (bool) {
+        return hasRole(DEFAULT_ADMIN_ROLE, account);
+      }
+
+      function isIssuer(address account ) public view returns (bool) {
+        return hasRole(ISSUER_ROLE, account);
+      }
+
+      function isPeerReviewer(address account ) public view returns (bool) {
+        return hasRole(PEER_REVIEWER_ROLE, account);
+      }
+
+      function addIssuer(address account) public onlyAdmin returns (bool) {
+        require(!isIssuer(account), "Account is already an issuer");
+        grantRole(ISSUER_ROLE, account);
+        return true;
+      }
+
+      function addPeerReviewer(address account) public onlyAdmin returns (bool) {
+        require(!isPeerReviewer(account), "Account is already a peer-reviewer");
+        grantRole(PEER_REVIEWER_ROLE, account);
+        return true;
+      }
+
+      function removeIssuer(address account) public onlyAdmin returns (bool) {
+        require(isIssuer(account), "Account is not an issuer");
+        revokeRole(ISSUER_ROLE, account);
+        return true;
+      }
+
+      function removePeerReviewer(address account) public onlyAdmin returns (bool) {
+        require(isPeerReviewer(account), "Account is not a peer-reviewer");
+        revokeRole(PEER_REVIEWER_ROLE, account);
+        return true;
+      }
+
+      /// @notice Pause all the functions
+      /// @dev the caller must have the 'PAUSER_ROLE'
+      function pause() public {
+        require(hasRole(PAUSER_ROLE, msg.sender), "BadgeFactory: must have pauser role to pause");
+        _pause();
+      }
+
+      /// @notice Unpause all the functions
+      /// @dev the caller must have the 'PAUSER_ROLE'
+      function unpause() public {
+            require(hasRole(PAUSER_ROLE, msg.sender), "BadgeFactory: must have pauser role to unpause");
+            _unpause();
+      }
+  }
+
+\end{lstlisting}
+
+\newpage
+\section{AntsReview.sol}
+
+\begin{lstlisting}[language=Solidity]
+  /// SPDX-License-Identifier: GPL-3.0
+  pragma solidity 0.6.8;
+
+  ///@title AntsReview
+  ///@author Nazzareno Massari
+  ///@notice AntsReview to allows issuer to issue an antReview which peer-reviewers can fulfill
+  ///@dev All function calls are currently implemented without side effecs through TDD approach
+  ///@dev OpenZeppelin library is used for secure contract development
+
+  import "./AntsReviewRoles.sol";
+  import "@openzeppelin/contracts/math/SafeMath.sol";
+  import "@openzeppelin/contracts/utils/Address.sol";
+  import "@openzeppelin/contracts/utils/Counters.sol";
+
+  interface AntToken {
+    function transfer(address reciptient, uint amount) external returns (bool);
+    function balanceOf(address account) external view returns (uint);
+  }
+
+  contract AntsReview is AntsReviewRoles {
+
+    using SafeMath for uint256;
+    using Address for address payable;
+    using Counters for Counters.Counter;
+
+    /// Enums
+    enum AntReviewStatus { CREATED, ACCEPTED, CANCELLED }
+
+    /// Token
+    AntToken internal ant;
+
+    /// Counter
+    Counters.Counter private _antReviewIdTracker;
+
+    /// Storage
+    AntReview[] public antreviews;
+
+    mapping(uint256 => Peer_Review[]) peer_reviews;
+
+    /// Structs
+    struct AntReview {
+        address payable issuer;
+        uint256 deadline;
+        string ipfs_hash;
+        AntReviewStatus status;
+        uint256 amount; //in wei
+    }
+
+    struct Peer_Review {
+        bool accepted;
+        address payable peer_reviewer;
+        string ipfs_hash;
+    }
+
+    /// Events
+
+    event AntReviewIssued(address issuer, uint256 amount, string ipfsHash);
+    event AntReviewFulfilled(uint256 antReviewId, address peer_reviewer, uint256 peerReviewId, string ipfsHash);
+    event AntReviewAccepted(uint256 antReviewId, address issuer, address peer_reviewer, uint256 indexed peerReviewId, uint256 amount);
+    event AntReviewCancelled(uint256 indexed antReviewId, address indexed issuer, uint256 amount);
+
+    constructor(address ant_) public {
+      ant = AntToken(ant_);
+    }
+
+    /// Fallback
+
+    fallback() external payable {
+      revert();
+    }
+
+    receive() external payable {
+      revert();
+    }
+
+    /// Modifiers
+
+    modifier hasValue() {
+        require(msg.value > 0);
+        _;
+    }
+
+    modifier antReviewExists(uint256 _antReviewId){
+      require(_antReviewId < antreviews.length);
+      _;
+    }
+
+    modifier peerReviewExists(uint256 _antReviewId, uint256 _peerReviewId){
+      require(_peerReviewId < peer_reviews[_antReviewId].length);
+      _;
+    }
+
+    modifier hasStatus(uint256 _antReviewId, AntReviewStatus _desiredStatus) {
+      require(antreviews[_antReviewId].status == _desiredStatus);
+      _;
+    }
+
+    modifier peerReviewNotYetAccepted(uint256 _antReviewId, uint256 _peerReviewId) {
+      require(peer_reviews[_antReviewId][_peerReviewId].accepted == false);
+      _;
+    }
+
+    modifier validateDeadline(uint256 _newDeadline) {
+        require(_newDeadline > now);
+        _;
+    }
+
+    modifier isBeforeDeadline(uint256 _antReviewId) {
+      require(now < antreviews[_antReviewId].deadline);
+      _;
+    }
+
+    ///@notice Instantiates a new AntReview
+    ///@dev Access restricted to Issuer
+    ///@param _deadline The unix timestamp after which fulfillments will no longer be accepted
+    ///@param _ipfsHash The IPFS Hash of the Scientific Paper
+    ///@return True If the antReview is successfully issued
+    function issueAntReview(
+        string calldata _ipfsHash,
+        uint64 _deadline
+    )
+        external
+        payable
+        hasValue()
+        validateDeadline(_deadline)
+        onlyIssuer()
+        whenNotPaused()
+        returns (bool)
+    {
+        _antReviewIdTracker.increment();
+        antreviews.push(AntReview(msg.sender, _deadline, _ipfsHash, AntReviewStatus.CREATED, msg.value));
+        emit AntReviewIssued(msg.sender, msg.value, _ipfsHash);
+        return true;
+    }
+
+    ///@notice Submit a fulfillment for the given antReview
+    ///@dev Access restricted to Peer-Reviewer
+    ///@param _antReviewId The index of the antReview to be fufilled
+    ///@param _ipfsHash The IPFS Hash which contains evidence of the fufillment
+    ///@return True If the AntReview is successfully fulfilled
+    function fulfillAntReview(uint256 _antReviewId, string memory _ipfsHash)
+      public
+      antReviewExists(_antReviewId)
+      onlyPeerReviewer()
+      hasStatus(_antReviewId, AntReviewStatus.CREATED)
+      isBeforeDeadline(_antReviewId)
+      whenNotPaused()
+      returns (bool)
+    {
+      peer_reviews[_antReviewId].push(Peer_Review(false, msg.sender, _ipfsHash));
+      emit AntReviewFulfilled(_antReviewId, msg.sender, (peer_reviews[_antReviewId].length.sub(1)),_ipfsHash);
+      return true;
+    }
+
+    ///@notice Accept a given Peer-Review
+    ///@dev Access restricted to Issuer
+    ///@param _antReviewId the index of the antReview
+    ///@param _peerReviewId the index of the fulfillment being accepted
+    ///@return True If the AntReview is successfully being accepted
+    function acceptAntReview(uint256 _antReviewId, uint256 _peerReviewId)
+        public
+        antReviewExists(_antReviewId)
+        peerReviewExists(_antReviewId,_peerReviewId)
+        onlyIssuer()
+        hasStatus(_antReviewId, AntReviewStatus.CREATED)
+        peerReviewNotYetAccepted(_antReviewId, _peerReviewId)
+        whenNotPaused()
+        returns (bool)
+    {
+        peer_reviews[_antReviewId][_peerReviewId].accepted = true;
+        antreviews[_antReviewId].status = AntReviewStatus.ACCEPTED;
+        peer_reviews[_antReviewId][_peerReviewId].peer_reviewer.sendValue(antreviews[_antReviewId].amount);
+        emit AntReviewAccepted(
+          _antReviewId,
+          antreviews[_antReviewId].issuer,
+          peer_reviews[_antReviewId][_peerReviewId].peer_reviewer,
+          _peerReviewId, antreviews[_antReviewId].amount
+        );
+        return true;
+    }
+
+    ///@notice Cancels the antReview and send the funds back to the issuer
+    ///@dev Access restricted to Issuer
+    ///@param _antReviewId the index of the antReview
+    ///@return True If the AntReview is successfully cancelled
+    function cancelAntReview(uint256 _antReviewId)
+        public
+        antReviewExists(_antReviewId)
+        onlyIssuer()
+        hasStatus(_antReviewId, AntReviewStatus.CREATED)
+        whenNotPaused()
+        returns (bool)
+    {
+        antreviews[_antReviewId].status = AntReviewStatus.CANCELLED;
+        antreviews[_antReviewId].issuer.sendValue(antreviews[_antReviewId].amount);
+        emit AntReviewCancelled(_antReviewId, msg.sender, antreviews[_antReviewId].amount);
+        return true;
+    }
+
+  }
+
+\end{lstlisting}
+
+\newpage
+\section{Ant.sol}
+
+\begin{lstlisting}[language=Solidity]
+  /// SPDX-License-Identifier: GPL-3.0
+  pragma solidity 0.6.8;
+
+  ///@title AntsReview
+  ///@author Nazzareno Massari
+  ///@notice Ant ERC20 Token
+  ///@dev All function calls are currently implemented without side effecs through TDD approach
+  ///@dev OpenZeppelin library is used for secure contract development
+
+  import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
+
+  contract Ant is ERC20PresetMinterPauser {
+
+    constructor()
+    ERC20PresetMinterPauser("Ant", "ANT")
+    public {
+
+    }
+
+  }
+\end{lstlisting}
 

### 2020-06-06 paper-v1.tex

--- 2020-06-06 paper-v1.tex
@@
 
-AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
-
-\begin{lstlisting}[language=Solidity]
-
-pragma solidity 0.6.8;
-
-import "@openzeppelin/contracts/access/AccessControl.sol";
-
-contract AntsReviewRoles is AccessControl {
-
-/// Roles
-bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
-bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
-
-}
-\end{lstlisting}
-
-In this way, only the Issuer (author) can create a new AntReview.
+AntsReviewRoles[appendix A], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
+\newline It also integrates a circuit breaker deisgn pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
+\newline In this way, only the Issuer (author) can create a new AntReview.
 \newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
@@
 
+\newpage
+
+\section{Appendix}
+
+\appendix
+
+\section{AntsReviewRoles.sol}
+
+\begin{lstlisting}[language=Solidity]
+
+  /// SPDX-License-Identifier: GPL-3.0
+  pragma solidity 0.6.8;
+
+  ///@title AntsReview
+  ///@author Nazzareno Massari
+  ///@notice AntsReviewRoles Access Management for Issuer and Peer-Reviewer
+  ///@dev All function calls are currently implemented without side effecs through TDD approach
+  ///@dev OpenZeppelin library is used for secure contract development
+
+  import "@openzeppelin/contracts/access/Ownable.sol";
+  import "@openzeppelin/contracts/access/AccessControl.sol";
+  import "@openzeppelin/contracts/utils/Pausable.sol";
+
+  contract AntsReviewRoles is Ownable, AccessControl, Pausable {
+
+    /// Roles
+    bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
+    bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
+    bytes32 public constant PAUSER_ROLE = keccak256("PAUSER_ROLE");
+
+    constructor() public {
+            _setupRole(DEFAULT_ADMIN_ROLE, owner());
+            _setupRole(PAUSER_ROLE, owner());
+    }
+
+      /// Modifiers
+      modifier onlyAdmin() {
+          require(isAdmin(msg.sender), "Caller is not an admin");
+          _;
+        }
+
+      modifier onlyIssuer() {
+          require(isIssuer(msg.sender), "Caller is not an issuer");
+          _;
+      }
+
+      modifier onlyPeerReviewer() {
+          require(isPeerReviewer(msg.sender), "Caller is not a peer-reviewer");
+          _;
+      }
+
+      /// Functions
+
+      function isAdmin(address account) public view returns (bool) {
+        return hasRole(DEFAULT_ADMIN_ROLE, account);
+      }
+
+      function isIssuer(address account ) public view returns (bool) {
+        return hasRole(ISSUER_ROLE, account);
+      }
+
+      function isPeerReviewer(address account ) public view returns (bool) {
+        return hasRole(PEER_REVIEWER_ROLE, account);
+      }
+
+      function addIssuer(address account) public onlyAdmin returns (bool) {
+        require(!isIssuer(account), "Account is already an issuer");
+        grantRole(ISSUER_ROLE, account);
+        return true;
+      }
+
+      function addPeerReviewer(address account) public onlyAdmin returns (bool) {
+        require(!isPeerReviewer(account), "Account is already a peer-reviewer");
+        grantRole(PEER_REVIEWER_ROLE, account);
+        return true;
+      }
+
+      function removeIssuer(address account) public onlyAdmin returns (bool) {
+        require(isIssuer(account), "Account is not an issuer");
+        revokeRole(ISSUER_ROLE, account);
+        return true;
+      }
+
+      function removePeerReviewer(address account) public onlyAdmin returns (bool) {
+        require(isPeerReviewer(account), "Account is not a peer-reviewer");
+        revokeRole(PEER_REVIEWER_ROLE, account);
+        return true;
+      }
+
+      /// @notice Pause all the functions
+      /// @dev the caller must have the 'PAUSER_ROLE'
+      function pause() public {
+        require(hasRole(PAUSER_ROLE, msg.sender), "BadgeFactory: must have pauser role to pause");
+        _pause();
+      }
+
+      /// @notice Unpause all the functions
+      /// @dev the caller must have the 'PAUSER_ROLE'
+      function unpause() public {
+            require(hasRole(PAUSER_ROLE, msg.sender), "BadgeFactory: must have pauser role to unpause");
+            _unpause();
+      }
+  }
+
+\end{lstlisting}
+
+\newpage
+\section{AntsReview.sol}
+
+\begin{lstlisting}[language=Solidity]
+  /// SPDX-License-Identifier: GPL-3.0
+  pragma solidity 0.6.8;
+
+  ///@title AntsReview
+  ///@author Nazzareno Massari
+  ///@notice AntsReview to allows issuer to issue an antReview which peer-reviewers can fulfill
+  ///@dev All function calls are currently implemented without side effecs through TDD approach
+  ///@dev OpenZeppelin library is used for secure contract development
+
+  import "./AntsReviewRoles.sol";
+  import "@openzeppelin/contracts/math/SafeMath.sol";
+  import "@openzeppelin/contracts/utils/Address.sol";
+  import "@openzeppelin/contracts/utils/Counters.sol";
+
+  interface AntToken {
+    function transfer(address reciptient, uint amount) external returns (bool);
+    function balanceOf(address account) external view returns (uint);
+  }
+
+  contract AntsReview is AntsReviewRoles {
+
+    using SafeMath for uint256;
+    using Address for address payable;
+    using Counters for Counters.Counter;
+
+    /// Enums
+    enum AntReviewStatus { CREATED, ACCEPTED, CANCELLED }
+
+    /// Token
+    AntToken internal ant;
+
+    /// Counter
+    Counters.Counter private _antReviewIdTracker;
+
+    /// Storage
+    AntReview[] public antreviews;
+
+    mapping(uint256 => Peer_Review[]) peer_reviews;
+
+    /// Structs
+    struct AntReview {
+        address payable issuer;
+        uint256 deadline;
+        string ipfs_hash;
+        AntReviewStatus status;
+        uint256 amount; //in wei
+    }
+
+    struct Peer_Review {
+        bool accepted;
+        address payable peer_reviewer;
+        string ipfs_hash;
+    }
+
+    /// Events
+
+    event AntReviewIssued(address issuer, uint256 amount, string ipfsHash);
+    event AntReviewFulfilled(uint256 antReviewId, address peer_reviewer, uint256 peerReviewId, string ipfsHash);
+    event AntReviewAccepted(uint256 antReviewId, address issuer, address peer_reviewer, uint256 indexed peerReviewId, uint256 amount);
+    event AntReviewCancelled(uint256 indexed antReviewId, address indexed issuer, uint256 amount);
+
+    constructor(address ant_) public {
+      ant = AntToken(ant_);
+    }
+
+    /// Fallback
+
+    fallback() external payable {
+      revert();
+    }
+
+    receive() external payable {
+      revert();
+    }
+
+    /// Modifiers
+
+    modifier hasValue() {
+        require(msg.value > 0);
+        _;
+    }
+
+    modifier antReviewExists(uint256 _antReviewId){
+      require(_antReviewId < antreviews.length);
+      _;
+    }
+
+    modifier peerReviewExists(uint256 _antReviewId, uint256 _peerReviewId){
+      require(_peerReviewId < peer_reviews[_antReviewId].length);
+      _;
+    }
+
+    modifier hasStatus(uint256 _antReviewId, AntReviewStatus _desiredStatus) {
+      require(antreviews[_antReviewId].status == _desiredStatus);
+      _;
+    }
+
+    modifier peerReviewNotYetAccepted(uint256 _antReviewId, uint256 _peerReviewId) {
+      require(peer_reviews[_antReviewId][_peerReviewId].accepted == false);
+      _;
+    }
+
+    modifier validateDeadline(uint256 _newDeadline) {
+        require(_newDeadline > now);
+        _;
+    }
+
+    modifier isBeforeDeadline(uint256 _antReviewId) {
+      require(now < antreviews[_antReviewId].deadline);
+      _;
+    }
+
+    ///@notice Instantiates a new AntReview
+    ///@dev Access restricted to Issuer
+    ///@param _deadline The unix timestamp after which fulfillments will no longer be accepted
+    ///@param _ipfsHash The IPFS Hash of the Scientific Paper
+    ///@return True If the antReview is successfully issued
+    function issueAntReview(
+        string calldata _ipfsHash,
+        uint64 _deadline
+    )
+        external
+        payable
+        hasValue()
+        validateDeadline(_deadline)
+        onlyIssuer()
+        whenNotPaused()
+        returns (bool)
+    {
+        _antReviewIdTracker.increment();
+        antreviews.push(AntReview(msg.sender, _deadline, _ipfsHash, AntReviewStatus.CREATED, msg.value));
+        emit AntReviewIssued(msg.sender, msg.value, _ipfsHash);
+        return true;
+    }
+
+    ///@notice Submit a fulfillment for the given antReview
+    ///@dev Access restricted to Peer-Reviewer
+    ///@param _antReviewId The index of the antReview to be fufilled
+    ///@param _ipfsHash The IPFS Hash which contains evidence of the fufillment
+    ///@return True If the AntReview is successfully fulfilled
+    function fulfillAntReview(uint256 _antReviewId, string memory _ipfsHash)
+      public
+      antReviewExists(_antReviewId)
+      onlyPeerReviewer()
+      hasStatus(_antReviewId, AntReviewStatus.CREATED)
+      isBeforeDeadline(_antReviewId)
+      whenNotPaused()
+      returns (bool)
+    {
+      peer_reviews[_antReviewId].push(Peer_Review(false, msg.sender, _ipfsHash));
+      emit AntReviewFulfilled(_antReviewId, msg.sender, (peer_reviews[_antReviewId].length.sub(1)),_ipfsHash);
+      return true;
+    }
+
+    ///@notice Accept a given Peer-Review
+    ///@dev Access restricted to Issuer
+    ///@param _antReviewId the index of the antReview
+    ///@param _peerReviewId the index of the fulfillment being accepted
+    ///@return True If the AntReview is successfully being accepted
+    function acceptAntReview(uint256 _antReviewId, uint256 _peerReviewId)
+        public
+        antReviewExists(_antReviewId)
+        peerReviewExists(_antReviewId,_peerReviewId)
+        onlyIssuer()
+        hasStatus(_antReviewId, AntReviewStatus.CREATED)
+        peerReviewNotYetAccepted(_antReviewId, _peerReviewId)
+        whenNotPaused()
+        returns (bool)
+    {
+        peer_reviews[_antReviewId][_peerReviewId].accepted = true;
+        antreviews[_antReviewId].status = AntReviewStatus.ACCEPTED;
+        peer_reviews[_antReviewId][_peerReviewId].peer_reviewer.sendValue(antreviews[_antReviewId].amount);
+        emit AntReviewAccepted(
+          _antReviewId,
+          antreviews[_antReviewId].issuer,
+          peer_reviews[_antReviewId][_peerReviewId].peer_reviewer,
+          _peerReviewId, antreviews[_antReviewId].amount
+        );
+        return true;
+    }
+
+    ///@notice Cancels the antReview and send the funds back to the issuer
+    ///@dev Access restricted to Issuer
+    ///@param _antReviewId the index of the antReview
+    ///@return True If the AntReview is successfully cancelled
+    function cancelAntReview(uint256 _antReviewId)
+        public
+        antReviewExists(_antReviewId)
+        onlyIssuer()
+        hasStatus(_antReviewId, AntReviewStatus.CREATED)
+        whenNotPaused()
+        returns (bool)
+    {
+        antreviews[_antReviewId].status = AntReviewStatus.CANCELLED;
+        antreviews[_antReviewId].issuer.sendValue(antreviews[_antReviewId].amount);
+        emit AntReviewCancelled(_antReviewId, msg.sender, antreviews[_antReviewId].amount);
+        return true;
+    }
+
+  }
+
+\end{lstlisting}
+
+\newpage
+\section{Ant.sol}
+
+\begin{lstlisting}[language=Solidity]
+  /// SPDX-License-Identifier: GPL-3.0
+  pragma solidity 0.6.8;
+
+  ///@title AntsReview
+  ///@author Nazzareno Massari
+  ///@notice Ant ERC20 Token
+  ///@dev All function calls are currently implemented without side effecs through TDD approach
+  ///@dev OpenZeppelin library is used for secure contract development
+
+  import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
+
+  contract Ant is ERC20PresetMinterPauser {
+
+    constructor()
+    ERC20PresetMinterPauser("Ant", "ANT")
+    public {
+
+    }
+
+  }
+\end{lstlisting}
+
 % ---- Bibliography ----

### 2020-06-06 paper-v1.tex

@@
 \subsection{Implementation}
-AntsReview is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
+\begin{figure}
+\centering
+\includegraphics[scale=0.28]{AntsReview}
+\caption{AntsReview Smart Contracts}
+\label{fig:contracts}
+\end{figure}
+
+AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
 \newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
@@
 \newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:
-
-\includegraphics[scale=0.28]{AntsReview}
 
@@
 \subsubsection{Bounty}
-AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
+AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
 \newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
@@
 \section{AntsReviewRoles.sol}
+\label{appendix:a}
 
@@
 \section{AntsReview.sol}
+\label{appendix:b}
 
@@
 \section{Ant.sol}
+\label{appendix:c}
 

### 2020-06-06 paper-v1.tex
add tokenomics tech point

@@
 \subsection{Implementation}
+
 \begin{figure}
@@
   \item \textbf{Bounty} - manage access management and the basic system.
-  \item \textbf{Token Economics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
+  \item \textbf{Tokenomics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
   \item \textbf{Privacy} - maintains the anonymity of the system via AZTEC Protocol.
@@
 
-\subsubsection{Token Economics}
+\subsubsection{Tokenomics}
+AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+\newline Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
+\newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: Ant ans symbol: ANT.
+\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai, ...
+with the possibity to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
+\newline An AntsReview DAO will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings accross the protocol.
+\newline Hive, When a Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
+\newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accures interest from MakerDAO's DSR (Dai Saving Rate)
+\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wraped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
+\newline zkAnt, is token wraped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkAnt will be implemented via AZTEC 2.0 that will allow to securily wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
 

### 2020-06-06 paper-v1.tex
Updates from Overleaf
update tokenomics + privacy tech point intro

@@
 \newline zkAnt will be implemented via AZTEC 2.0 that will allow to securily wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin to match donations for Grants.
+This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
+\subsubsection{Privacy}
 
-\subsubsection{Privacy}
+The Anonymity of an agent in the system is achieved in two ways:
+
+\begin{itemize}
+  \item PseudoAnonimity granted by an Etherum address that can obscure the identity of the agent.
+  \item Private Transactions thanks to AZTEC Protocol security layer via zkAnt.
+\end{itemize}
 

### 2020-06-06 paper-v1.tex

@@
 \newline In Ethereum the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
-\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
+\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
+\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
+\newline In order to verify if a spefic hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that rapresent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
+\newline On the Front-End the file will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
 
@@
 AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
-\newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: Ant ans symbol: ANT.
+\newline \textbf{Ant}, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
+\newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \textbf{\emph{Ant}} ans symbol: \textbf{\emph{ANT}}.
 \newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai, ...
 with the possibity to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
-\newline An AntsReview DAO will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings accross the protocol.
-\newline Hive, When a Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
+\newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings accross the protocol.
+\newline \textbf{Hive}. When a Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accures interest from MakerDAO's DSR (Dai Saving Rate)
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accures interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wraped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
-\newline zkAnt, is token wraped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
+\newline \textbf{zkAnt}, is token wrapped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
 \newline zkAnt will be implemented via AZTEC 2.0 that will allow to securily wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
@@
 \begin{itemize}
-  \item PseudoAnonimity granted by an Etherum address that can obscure the identity of the agent.
-  \item Private Transactions thanks to AZTEC Protocol security layer via zkAnt.
+  \item PseudoAnonimity granted by an Etherum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
+  \item Private Transactions thanks to AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
 \end{itemize}
+
+\newline Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code.
+An user can send messages from an externally owned account by creating and signing a transaction.
+\newline
+
+\newline AZTEC Protocol
 

### 2020-06-06 paper-v1.tex
Updates from Overleaf

--- 2020-06-06 paper-v1.tex
@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage[nottoc]{tocbibind}
 
@@
 Therefore, scientific dissemination is affected.
-Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system.
-We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication.
-If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer.
-To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
+Here, to solve this issue we propose a blockchain based privacy-preserving incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system.
+We designed a Protocol of smart contracts called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication.
+If requirements are met, peer-reviews will be accepted and payed by the Issuer.
+To promote ethical behaviour the system will ideally implement a quadratic funding on AntsReview.
 \keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
@@
 \section{Introduction}
-blockchain for science here and application to open science and to peer review as a specific case
+Blockchain for science here and application to open science and to peer review as a specific case.
 
@@
 \paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
-\paragraph{Transparency} (meaning that we have a viewable record of all the transactions), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
+\paragraph{Transparency} (meaning that we have a viewable record of all the papers and peer-reviews), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
 Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
@@
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wraped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
-\newline zkAnt, is token wraped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkAnt, is token wrapped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
 \newline zkAnt will be implemented via AZTEC 2.0 that will allow to securily wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
@@
 \subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for internal review and useful comments.
-
+Important citations are here \cite{10.1016/j.respol.2012.04.014,10.1038/s41467-018-08250-2,10.12688/f1000research.11369.2} and here \cite{undefined}. \cite{patentiimages}
 \newpage
@@
 \bibliographystyle{splncs04}
-\bibliography{references.bib}
+\bibliography{ourreferences.bib}
 

### 2020-06-06 paper-v1.tex

--- 2020-06-06 paper-v1.tex
@@
 \subsubsection{Bounty}
+
 AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
@@
 \newline In order to verify if a spefic hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that rapresent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
-\newline On the Front-End the file will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
+\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
 
 \subsubsection{Tokenomics}
+
 AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
@@
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wraped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
-\newline \textbf{zkAnt}, is token wrapped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
+\newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol ZK-SNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
 \newline zkAnt will be implemented via AZTEC 2.0 that will allow to securily wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
@@
 This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
+
 \subsubsection{Privacy}
@@
   \item PseudoAnonimity granted by an Etherum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
-  \item Private Transactions thanks to AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
+  \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
 \end{itemize}
@@
 An user can send messages from an externally owned account by creating and signing a transaction.
-\newline
-
-\newline AZTEC Protocol
+\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
+\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimiy of Peer-Reviewers.
+\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
+\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
+\newline Zero-Knowledge proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
+\newline Future developements will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
+This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
 

### 2020-06-06 paper-v1.tex
Updates from Overleaf

--- 2020-06-06 paper-v1.tex
@@
 \newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
-\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
+\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending on top with a single root hash.
 \newline In order to verify if a spefic hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that rapresent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
-\newline On the Front-End the file will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
+\newline The paper and peer-reviews documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
 
@@
 AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+\medskip
 \newline \textbf{Ant}, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
@@
 with the possibity to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
+\medskip
 \newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings accross the protocol.
+\medskip
 \newline \textbf{Hive}. When a Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accures interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accures interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: 
+\textbf{\emph{HIVE}}
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wraped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
+\medskip
 \newline \textbf{zkAnt}, is token wrapped into AZTEC Protocol zkSNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
@@
 An user can send messages from an externally owned account by creating and signing a transaction.
-\newline
-
 \newline AZTEC Protocol
@@
 \subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for internal review and useful comments.
-
+here I want to \cite{10.5281/zenodo.3828087,10.1093/biosci/bix034} 
 \newpage
@@
 \bibliographystyle{splncs04}
-\bibliography{references.bib}
+\bibliography{ourreferences.bib,privacy.bib}
 

### 2020-06-06 samplepaper.tex
Updates from Overleaf

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2020-06-06 paper-v1.tex
playing with BibTeX

--- 2020-06-06 paper-v1.tex
@@
 
-\newline Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code.
+ Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code.
 An user can send messages from an externally owned account by creating and signing a transaction.

### 2020-06-07 paper-v1.tex
modified complex system paragraph

@@
 From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
+\newline The paper is structured as follows.
+Sections 2 presents research background and related works.
+Section 3 explains the proposed Ethereum-based protocol illustrating the system architecture and the current status of implementation.
+In Sect.
+4 we discuss the implication of our work.
+Section 5 contains the conclusions.
+Appendixes present the smart contracts.
 
@@
 \section{System concept}
-For the above mentioned reasons, we propose an incentive-based protocol called Ants-Review to reward open peer-reviews while preserving the anonymity of the reviewers.
-The name originates from the idea that the work behind a finished scientific paper resembles a complex organism such as an anthill, which emerges from the sum of many individualities: in it, all contributions (even if ‘micro’) are essential to the whole and are worth recognition.
-This project is intended to be open source and was developed during the ETH Turin 2020 Hackathon and it’s design and attempt of implementation are exposed in the following section.
+In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors and that .
+We imagine a final paper originating from the peer-review process as a complex system that emerges from the product of interactions between the authors and the reviewers, a whole that is more than the sum of its parts.
+Therefore, the name hints at the ant colony as a model of self-organization in which all micro-contributions of the individuals add up to complex behaviour.
+A previous version of this paper can be found here \cite{10.5281/zenodo.3828087}, as a proposal submitted for the ETH Turin 2020 Hackathon.
+and it’s design and attempt of implementation are exposed in the following section.
 
@@
 \end{figure}
+In this section we provide an overview of how we implemented the system by focusing on its components.
 

### 2020-06-07 paper-v1.tex
throwing ideas

@@
 
-\subsection{Blockchain solution}
+\subsection{Ideas here}
 
@@
 and it’s design and attempt of implementation are exposed in the following section.
+Here I expose the main traits/features of AR
+\begin{itemize}
+\item accountability: both for recognition and for security vs fraud abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest.
+this means the platform acts like a version control system where commit are permanent and hashed
+\item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
+\item incentivisation: via symbolic and material recognition of the performed work. tokens and bounty
+\item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
+\end{itemize}
 
-\subsubsection{Accountability} hash
-\subsubsection{Reward} bounty
-\subsubsection{Quadratic Voting} I don't see the point of introducing QF here. Is it already implemented or it's just in the idea?
-
-\subsubsection{Privacy/anonymity}.
-To protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
-Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
-We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol.
-AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
+In the following sessions we describe the architecture of the system and its building blocks
 
 \subsection{Design}
+
+There are two possible scenarios depending if we save the role of the editor and we integrate an existing journal or if AntsReview becomes a platform completely decoupled from journals.
 
@@
 
-peer-review is decoupled from journal
-or
-
 \subsection{Implementation}
@@
 AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
-\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
-\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
+
 \newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:
@@
 This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
-
+\subsubsection{Privacy/anonymity}.
+To protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
+Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
+We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol.
+AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
 \section{Discussions}
@@
 \section{Conclusion}
-In this paper we addressed a central problem within the quality control academic dissemination: the peer-review process.
+In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
 We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication.
@@
 \subsubsection{Supplementary material}
-Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
+TBD
 

### 2020-06-07 paper-v1.tex
Citations from important reports done yesterday night

@@
 blockchain for science here and application to open science and to peer review as a specific case
+to cite "" The essence of blockchain is that it allows transactions of value without intermediaries, and can enable decentralised business models." "
 
+Dr.
+Soenke Bartling is a German radiologist and founder of Blockchain for Science2, a think tank based in Berlin.
+Launched in 2016, its aim is to ‘open up science and knowledge creation by means of the blockchain (r)evolution’.
+Besides meetings, hackathons3 and stimulating knowledge sharing through its online platform, the organisation also launched and maintains a living document4 on blockchain and science, collecting ideas on how blockchain could open up science and knowledge creation.
+
+\begin{itemize}
+\item reproducibility crisis (a fix)
+\item openness of access and data 
+\item 'blockchainefied science':  "a more flexible, grass-root and reputation-based governance of science."
+\end{itemize}
+reputation metrics -- "blockchain would make much larger parts of the research cycle open to scientific self-correction.
+This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’.
+Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation." https://docs.google.com/document/d/1Uhjb4K69l0bSx7UXYUStV_rjuPC7VGo0ERa-7xEsr58/edit#heading=h.z4w0uvttpvgt
+Decentralized
+Distributed 
+Immutable (≈’append only database’)
+Transparent (provable to the external world)
+"One such system, the Ethereum blockchain, goes so far as to provide its own programming language to run distributed, unstoppable, and provable applications [27].
+This includes smart contracts [28] which can be used to realize distributed, autonomous applications and organizations [29]." they propose permissioned public blockchain for science
+"Figure 3: Large parts of the research cycle can make use of blockchain (yellow arch); only the experiment/initial data collection itself cannot.
+From data collection onwards, the rest of the research circle would then become immutable, comprehensible, and externally provable.
+This would make larger parts of the research cycle open to scientific self-correction and may make more research results reproducible, true, and useful."
+\begin{itemize}
+\item scientific ideas/data/lab notebooks via time-stamping and proof of existence - Blockchains provide a ‘notarization’ functionality.
+\item pre-registration in open science, now managed by open platforms like OSF 
+\item The recommendation to reduce waste in science which reads: ‘Public availability of raw data and complete scripts of statistical analysis could be required by journals and funding agencies sponsoring new research’ [5,49] could be realized through blockchain.
+to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
+\item stress on scientific self-correction: from open data science to blockchain based science 
+\end{itemize}
+"Figure 5: In closed science, scientists just publish a description of their research data and results in their final publication (I).
+Currently, researchers can publish their research data in data repositories, but that leaves no trace of the data collection or handling process (II).
+Of course, the final repository could be a blockchain based, decentralized database (III).
+However, blockchain technology could take the whole process one step further: the whole data handling process could take place in a blockchain system and would therefore be provable and open to scientific self-correction (at will) (IV)."
+Blockchain systems make it possible to publish research anonymously [70] or with a second online identity - and yet one could still get money or other research impact appreciation for it [71,72]
+Science reputation systems can be built using blockchain without a trusted third party. 
+As such, a Decentralized Autonomous Academic Endorsement System has been proposed and interesting implementation ideas and next implementation steps have been disclosed [72].
+Research funding: A DARO (distributed autonomous research organization) allocates and distributes research resources.
+could also engage the public through a more transparent research process. 
+token economy could be applied to scientific ideas and groundbreaking discoveries, we could incentivise scientist to spread ideas early and strongly.
+This stands in contrast to the current system, which incentivises scientists to remain inert until publication, patent application, etc.
+It has been claimed that this could also be a solution to the famous innovators dilemma [9
+What should token for science/research projects represent?
+One thing would be ‘asset-backed’ tokens as described here [96] as a bet on the commercially usable part of the intellectual property.
+However, is that enough?
+Couldn't there be tokens that represent a purely scientific value of a research project?
+Researchers are used to immaterial rewards called “reputation”.
+For instance, I could place bets (as outlined below on relativity and will receive reputation tokens for properly predicting outcomes.
+I would also receive “reputation” if my own research results can be validated by “the crowd” or will be used by their future work, i.e.
+represent the equivalent of citations.)
+The blockchain revolution is a game changer and hence chances are that this can be used to break with inappropriate cultures.
+Indeed, blockchain technology could be used to ‘Increase value and reduce waste’ [5], by opening the research cycle to scientific self-control beyond the final publication and might therefore be a fix to the current reproducibility crisis in science.
+
+Through the blockchain, ownership of content is automatically established, and the use of content and the payment of royalties are executed through smart contracts in which the rights are stored."
+
+commercial landscape in scholarly communication. For example, the platforms allow micropayments t
+New Metrics Research on the blockchain could have a huge impact on the way researchers build their reputation and become recognised.The big advantage of a blockchain for research is that all activities of scientists can be automatically stored.Whenever a researcher uploads data, performs statistical analyses, writes and submits an article or reviews a manuscript, this is automatically tracked and recorded.
+By working on a blockchain, the risk of fraud is significantly reduced making it significantly easier to collect reliable and complete data on the performance of researchers, research groups and universities.This would allow for more sophisticated as well as reliable metrics to be built on top of that.
+Moreover, it will allow metrics to be based on activities that are currently not well recognised (e.g., peer review).
+Alternative Economic Models
+A blockchain for research could accompany the introduction of a cryptocurrency, which would add an economic layer to the blockchain.
+This ‘bitcoin for research’ could be used to make micro payments to publishers for consuming content, and could also introduce a monetary reward scheme to researchers themselves.
+For example, the blockchain could disintermediate publishers and reward authors directly with cryptocurrencies that can be used to purchase other content or services.
+It could also introduce rewards for research activities, such as peer review, statistical support, exchange of lab equipment, outsourcing specific research, or the hosting of data.
+Eventually, initial coin offerings (ICOs12), a form of crowdfunding using cryptocurrencies, could be used to fund entire research projects.
+In this way, a crypto economy could evolve in science reflecting the value merits of a number of activities.
+
+REWRITE
 An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
@@
 From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
+
 \newline The paper is structured as follows.
@@
 \subsection{Peer-review: a flawed and outdated system}
+
+"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers.Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9.
+Overall, the review process is considered opaque and expensive, slowing down the speed of scientific discovery and progress."
+
 Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination.
@@
 \subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
-\paragraph{Traditional peer-review process} This section takes inspiriration from the editorial processes at Nature Methods and Wiley.
+\paragraph{Traditional peer-review process} This section takes inspiration from the editorial processes at \emph{Nature Methods} and \emph{Wiley}.
 \begin{enumerate}
@@
 \emph{I8X Platform}
+A more comprehensive reform of academic endorsement has been proposed in the manifesto ‘Towards Open Science:The Case for a Decentralized Autonomous Endorsement System11’, published anonymously.The author(s) propose a new academic endorsement system that is not based on current journal publication practices which are argued to be expensive, slow, disregard non-traditional output and negative results, and which give too much power to editors and publishers.
+Built on the blockchain, the Academic Endorsement System (AES) is based on a new form of currency, coined academic endorsement points (AEP), which can be used by scientists to reward scientific work that is worthy of endorsement.
+Moreover, the amount of AEP credited to a scientist is based on the AEP received for previous work.
+Researchers whose output has been endorsed to a high degree will have a larger influence in the community.
+Any kind of research output could be endorsed, for example blog posts, data sets, software etc.Another advantage is that this system would be faster than the time it takes for citation metrics to accrue.
+The startup Matryx.ai13 aims to transform the nature of research collaboration itself.
+Its initiators claim that one of the problems with current scientific practices is its incentive structure.
+Scientific awards, for example, are based on competition rather than on collaboration, despite the fact that new ideas are usually collaborative in nature.
+Moreover, different researchers and research groups are often working on the same problems, wasting, as they claim on their website,‘brain power’, time and money.
+Matryx intends to provide a platform enabling and incentivising research collaboration while discouraging solitary and siloed research.
+On Matryx, a research project starts when users set a bounty on a problem that they want the community to solve.
+Contributors solve these problems by working with each other on the platform.The collaboration is tracked through the blockchain thus ensuring contributors are credited appropriately when the problem is solved.
+In principle, everyone can contribute in the collaboration: scientists, PhD students and even enthusiastic amateurs.
 
@@
 \end{itemize}
-
+crowdfunding schemes leveraged by blockchain technology
 In the following sessions we describe the architecture of the system and its building blocks
+AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
 
@@
 However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the editors with Quadratic Voting.********* POINT OF FAILURE?
-who votes?
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by Anters (members of the community) via Quadratic Voting to rank the most prolific peer-reviewers.
 
@@
 
-AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
-
 \newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:
@@
 
-AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
+AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart [Fig. \ref{fig:contracts}].
 \newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
@@
 
-AntsReviewRoles[appendix A], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].
-\newline It also integrates a circuit breaker deisgn pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
+AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer.
+\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
 \newline In this way, only the Issuer (author) can create a new AntReview.
@@
 \newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
-\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document".
+\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W.
+Scott Stornetta with the paper "How to time-stamp a digital document" \bibliography{}
 \newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
@@
 \newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
-\newline In order to verify if a spefic hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that rapresent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
+\newline In order to verify if a specific hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
 \newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
@@
 \newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai, ...
-with the possibity to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
-\newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings accross the protocol.
-\newline \textbf{Hive}. When a Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
+with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
+\newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
+\newline \textbf{Hive}.
+When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accures interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
-\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wraped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
+\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
 \newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol ZK-SNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkAnt will be implemented via AZTEC 2.0 that will allow to securily wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline zkAnt will be implemented via AZTEC 2.0 that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
 \newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin to match donations for Grants.
@@
 \begin{itemize}
-  \item PseudoAnonimity granted by an Etherum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
+  \item PseudoAnonimity granted by an Ethereum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
   \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
@@
 \newline Zero-Knowledge proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
-\newline Future developements will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
+\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
 This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
 \subsubsection{Privacy/anonymity}.
-To protect the contributors privacy, we would like to implement on the ANT token a fast, non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
+To enhance the peer-reviewer's privacy, we would like to implement zkANT, an ERC20 token, Ant, wrapped into AZTEC Protocol ZK-SNARKs, a non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
 Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.

### 2020-06-07 paper-v1.tex
try \cite{Rinkeby} - citekeys

@@
 
-\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:
+\newline The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
 
-\begin{enumerate}
-  \item \textbf{Bounty} - manage access management and the basic system.
-  \item \textbf{Tokenomics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
-  \item \textbf{Privacy} - maintains the anonymity of the system via AZTEC Protocol.
-\end{enumerate}
+\begin{itemize}
+\item AntsReview - manage access management and the basic system.
+\item Tokenomics - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
+\item Privacy - maintains the anonymity of the system via AZTEC Protocol.
+\end{itemize}
 
-\subsubsection{Bounty}
+\subsubsection{AntsReview}
 
-AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart [Fig. \ref{fig:contracts}].
+AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}
 \newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:

### 2020-06-07 paper-v1.tex
Update

@@
 Therefore, the name hints at the ant colony as a model of self-organization in which all micro-contributions of the individuals add up to complex behaviour.
-A previous version of this paper can be found here \cite{10.5281/zenodo.3828087}, as a proposal submitted for the ETH Turin 2020 Hackathon.
+A previous version of this paper can be found here \cite{AntsReview}, as a proposal submitted for the ETH Turin 2020 Hackathon.
 and it’s design and attempt of implementation are exposed in the following section.
@@
 \begin{itemize}
-  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
+  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}.
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
@@
 
-AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer.
+AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library\cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
 \newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
@@
 \newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W.
-Scott Stornetta with the paper "How to time-stamp a digital document" \bibliography{}
-\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
-\newline In Ethereum the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
+Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
+\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin\cite{Bitcoin} as its first application.
+\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
 \newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
 \newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
-\newline In order to verify if a specific hash is included into a Markle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
-\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidiy, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
+\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
+\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
 
-\subsubsection{Tokenomics}
+\subsubsection{Tokenomics
 
@@
 \newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \textbf{\emph{Ant}} ans symbol: \textbf{\emph{ANT}}.
-\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai, ...
+\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai \cite{Chai}, ...
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
@@
 \bibliographystyle{splncs04}
-\bibliography{references.bib}
+\bibliography{ref1-intro.bib, ref2-peerreview.bib, ref2-relatedwork.bib, ref3-system.bib}
 

### 2020-06-07 paper-v1.tex
Update tech refs by @naszam

@@
 This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’.
-Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation." https://docs.google.com/document/d/1Uhjb4K69l0bSx7UXYUStV_rjuPC7VGo0ERa-7xEsr58/edit#heading=h.z4w0uvttpvgt
+Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation."
 Decentralized
 Distributed 
-Immutable (≈’append only database’)
+Immutable (’append only database’)
 Transparent (provable to the external world)
@@
 This would make larger parts of the research cycle open to scientific self-correction and may make more research results reproducible, true, and useful."
+
 \begin{itemize} 
@@
 \end{itemize}
+
 "Figure 5: In closed science, scientists just publish a description of their research data and results in their final publication (I).
@@
 
-\newline The paper is structured as follows.
+ The paper is structured as follows.
 Sections 2 presents research background and related works.
@@
 
-\newline The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
+The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
 
@@
 
-AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library\cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
+AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
 \newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
@@
 
-\subsubsection{Tokenomics
+\subsubsection{Tokenomics}
 
@@
 \newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \textbf{\emph{Ant}} ans symbol: \textbf{\emph{ANT}}.
-\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai \cite{Chai}, ...
-with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
+\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
+with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR \cite{DSR} or Compound to cite a few.
 \newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
@@
 \section{AntsReviewRoles.sol}
+
 \label{appendix:a}
@@
 \section{AntsReview.sol}
+
 \label{appendix:b}

### 2020-06-07 paper-v1.tex
blockchain-tech

@@
 \section{Introduction}
-blockchain for science here and application to open science and to peer review as a specific case
-to cite "" The essence of blockchain is that it allows transactions of value without intermediaries, and can enable decentralised business models." "
-
-Dr.
-Soenke Bartling is a German radiologist and founder of Blockchain for Science2, a think tank based in Berlin.
-Launched in 2016, its aim is to ‘open up science and knowledge creation by means of the blockchain (r)evolution’.
-Besides meetings, hackathons3 and stimulating knowledge sharing through its online platform, the organisation also launched and maintains a living document4 on blockchain and science, collecting ideas on how blockchain could open up science and knowledge creation.
-
-\begin{itemize}
-\item reproducibility crisis (a fix)
-\item openness of access and data 
-\item 'blockchainefied science':  "a more flexible, grass-root and reputation-based governance of science."
-\end{itemize}
-reputation metrics -- "blockchain would make much larger parts of the research cycle open to scientific self-correction.
-This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’.
-Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation."
-Decentralized
-Distributed 
-Immutable (’append only database’)
-Transparent (provable to the external world)
-"One such system, the Ethereum blockchain, goes so far as to provide its own programming language to run distributed, unstoppable, and provable applications [27].
-This includes smart contracts [28] which can be used to realize distributed, autonomous applications and organizations [29]." they propose permissioned public blockchain for science
-"Figure 3: Large parts of the research cycle can make use of blockchain (yellow arch); only the experiment/initial data collection itself cannot.
-From data collection onwards, the rest of the research circle would then become immutable, comprehensible, and externally provable.
-This would make larger parts of the research cycle open to scientific self-correction and may make more research results reproducible, true, and useful."
-
-\begin{itemize} 
-\item scientific ideas/data/lab notebooks via time-stamping and proof of existence - Blockchains provide a ‘notarization’ functionality.
-\item pre-registration in open science, now managed by open platforms like OSF 
-\item The recommendation to reduce waste in science which reads: ‘Public availability of raw data and complete scripts of statistical analysis could be required by journals and funding agencies sponsoring new research’ [5,49] could be realized through blockchain.
-to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
-\item stress on scientific self-correction: from open data science to blockchain based science 
-\end{itemize}
-
-"Figure 5: In closed science, scientists just publish a description of their research data and results in their final publication (I).
-Currently, researchers can publish their research data in data repositories, but that leaves no trace of the data collection or handling process (II).
-Of course, the final repository could be a blockchain based, decentralized database (III).
-However, blockchain technology could take the whole process one step further: the whole data handling process could take place in a blockchain system and would therefore be provable and open to scientific self-correction (at will) (IV)."
-Blockchain systems make it possible to publish research anonymously [70] or with a second online identity - and yet one could still get money or other research impact appreciation for it [71,72]
-Science reputation systems can be built using blockchain without a trusted third party. 
-As such, a Decentralized Autonomous Academic Endorsement System has been proposed and interesting implementation ideas and next implementation steps have been disclosed [72].
-Research funding: A DARO (distributed autonomous research organization) allocates and distributes research resources.
-could also engage the public through a more transparent research process. 
-token economy could be applied to scientific ideas and groundbreaking discoveries, we could incentivise scientist to spread ideas early and strongly.
-This stands in contrast to the current system, which incentivises scientists to remain inert until publication, patent application, etc.
-It has been claimed that this could also be a solution to the famous innovators dilemma [9
-What should token for science/research projects represent?
-One thing would be ‘asset-backed’ tokens as described here [96] as a bet on the commercially usable part of the intellectual property.
-However, is that enough?
-Couldn't there be tokens that represent a purely scientific value of a research project?
-Researchers are used to immaterial rewards called “reputation”.
-For instance, I could place bets (as outlined below on relativity and will receive reputation tokens for properly predicting outcomes.
-I would also receive “reputation” if my own research results can be validated by “the crowd” or will be used by their future work, i.e.
-represent the equivalent of citations.)
-The blockchain revolution is a game changer and hence chances are that this can be used to break with inappropriate cultures.
-Indeed, blockchain technology could be used to ‘Increase value and reduce waste’ [5], by opening the research cycle to scientific self-control beyond the final publication and might therefore be a fix to the current reproducibility crisis in science.
-
-Through the blockchain, ownership of content is automatically established, and the use of content and the payment of royalties are executed through smart contracts in which the rights are stored."
-
-commercial landscape in scholarly communication. For example, the platforms allow micropayments t
-New Metrics Research on the blockchain could have a huge impact on the way researchers build their reputation and become recognised.The big advantage of a blockchain for research is that all activities of scientists can be automatically stored.Whenever a researcher uploads data, performs statistical analyses, writes and submits an article or reviews a manuscript, this is automatically tracked and recorded.
-By working on a blockchain, the risk of fraud is significantly reduced making it significantly easier to collect reliable and complete data on the performance of researchers, research groups and universities.This would allow for more sophisticated as well as reliable metrics to be built on top of that.
-Moreover, it will allow metrics to be based on activities that are currently not well recognised (e.g., peer review).
-Alternative Economic Models
-A blockchain for research could accompany the introduction of a cryptocurrency, which would add an economic layer to the blockchain.
-This ‘bitcoin for research’ could be used to make micro payments to publishers for consuming content, and could also introduce a monetary reward scheme to researchers themselves.
-For example, the blockchain could disintermediate publishers and reward authors directly with cryptocurrencies that can be used to purchase other content or services.
-It could also introduce rewards for research activities, such as peer review, statistical support, exchange of lab equipment, outsourcing specific research, or the hosting of data.
-Eventually, initial coin offerings (ICOs12), a form of crowdfunding using cryptocurrencies, could be used to fund entire research projects.
-In this way, a crypto economy could evolve in science reflecting the value merits of a number of activities.
-
-REWRITE
-An increasing body of voices in the scientific community has started to speak up for the need of updating current scientific practices with the advances represented by blockchain technology [2, 8].
-As an example, we refer to a ‘manifesto’ written by a few anonymous authors, proposing a blockchain based system of academic endorsement (AES) [1].
-Indeed, we could say that in general “specific blockchain characteristics meet the requirements of an open science infrastructure” [3-7]:
-\paragraph{Decentralisation}Taking out the need of intermediaries, would make useless depending on highly profiting publishing companies for disseminating scientific work and managing the rules of the peer-review process;
-\paragraph{Immutability} of the system in which information can only be appended with tamper proof-time stamping,  but not subsequently modified, would secure the intellectual property and a fairer measure of the scientific contribution of the actors at play during the multiple versions of a paper;
-\paragraph{Transparency} (meaning that we have a viewable record of all the papers and peer-reviews), would also make editorial decisions (publish or not publish a study) more transparent and democratic.
-Finally, cryptographic hashing could allow for a double-blind process that reduces human biases in judgement by assigning hashed pseudonymous to universal researcher identifiers.
-From all these aspects taken together, a more democratic open peer-review  process could rise, in which merit and power (of access to information, of decision…) is more equally redistributed among the stakeholders (researchers, reviewers, taxpayers).
+From its birth in 2008 as a distributed ledger for the cryptocurrency bitcoin \cite{Bitcoin}, blockchain technology has
 

### 2020-06-07 paper-v1.tex
intro

@@
 To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
-\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
+\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
 \end{abstract}
@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the cryptocurrency bitcoin \cite{Bitcoin}, blockchain technology has
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread way beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum.
+Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci}.
 
@@
 \newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
-\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
+\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
 \newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
@@
 \newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
-with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR \cite{DSR} or Compound to cite a few.
+with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
 \newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
@@
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
-\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
-\newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol ZK-SNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkAnt will be implemented via AZTEC 2.0 that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
-\newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin to match donations for Grants.
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR or Compound, with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
+\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent equally to the peer-reviewers that fulfilled the AntReview.
+\newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline Finally, another concept under investigation is Quadratic Funding \cite{QuadraticFunding}, used by Gitcoin to match donations for Grants.
 This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.

### 2020-06-07 paper-v1.tex
Update tech refs by @naszam

@@
 %
-\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author} \and
+\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author: bianca.trovo@alumni.unitn.it} \and
 Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
@@
 From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread way beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum.
-Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci}.
+Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with promising potential of repairing broken scientific practices
 
@@
 \newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
-\newline Finally, another concept under investigation is Quadratic Funding \cite{QuadraticFunding}, used by Gitcoin to match donations for Grants.
+\newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
 This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.

### 2020-06-07 paper-v1.tex
introduction

@@
 From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread way beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum.
-Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with promising potential of repairing broken scientific practices
+Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices.
 

### 2020-06-07 paper-v1.tex
intro

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread way beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum.
 Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices.
+In particular, a 'blockchainefied science'\cite{BlockchainforScience} could 'increase value and reduce waste’\cite{ReducingWaste-Lancet}, by disclosing the research cycle to scientific assessment way before the final publication step and therefore help fixing the current reproducibility crisis in science.
+"blockchain would make much larger parts of the research cycle open to scientific self-correction.
+This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’.
+Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation."
 
@@
 \newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
-\newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
+\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
 This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
@@
 \newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
-\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimiy of Peer-Reviewers.
+\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimity of Peer-Reviewers.
 \newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
-\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Zero-Knowledge proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
+\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
+\newline Zero-Knowledge \cite{ZeroKnoledge} proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
 \newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
@@
 
+\newpage
+
 % ---- Bibliography ----

### 2020-06-07 paper-v1.tex
Update

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum.
-Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices.
-In particular, a 'blockchainefied science'\cite{BlockchainforScience} could 'increase value and reduce waste’\cite{ReducingWaste-Lancet}, by disclosing the research cycle to scientific assessment way before the final publication step and therefore help fixing the current reproducibility crisis in science.
-"blockchain would make much larger parts of the research cycle open to scientific self-correction.
-This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’.
-Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation."
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'Bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum.
+Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.
+In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
+Scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing, that creates a digital footprint able to keep a 'trail of research';
+to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
 
@@
 
-"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers.Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9.
+"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers.
+Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9.
 Overall, the review process is considered opaque and expensive, slowing down the speed of scientific discovery and progress."
@@
 \subsection{Related work}
-Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
+Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like impact factor h-index.
 In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
@@
 \section{System concept}
-In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors and that .
-We imagine a final paper originating from the peer-review process as a complex system that emerges from the product of interactions between the authors and the reviewers, a whole that is more than the sum of its parts.
-Therefore, the name hints at the ant colony as a model of self-organization in which all micro-contributions of the individuals add up to complex behaviour.
+In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors.
+We imagine a final paper originating from the peer-review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts.
+Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
 A previous version of this paper can be found here \cite{AntsReview}, as a proposal submitted for the ETH Turin 2020 Hackathon.
-and it’s design and attempt of implementation are exposed in the following section.
-Here I expose the main traits/features of AR
+and its design and attempt of implementation are exposed in the following section.
+Here we expose the main traits/features of AR
 \begin{itemize}
@@
 \item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
-\item incentivisation: via symbolic and material recognition of the performed work. tokens and bounty
+\item incentivisation: via symbolic and material recognition of the performed work. reputation and bounties
 \item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
@@
 crowdfunding schemes leveraged by blockchain technology
-In the following sessions we describe the architecture of the system and its building blocks
-AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
+In the following sections we describe the architecture of the system and its building blocks
+AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
 
@@
 However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community with Quadratic Voting.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community via Quadratic Voting.
     \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
@@
 In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
-We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication.
+We showed how blockchain technology could provide an efficient and viable solution and open up possible directions for a change in paradigm in scientific communication.
 We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review.

### 2020-06-07 paper-v1.tex
blockchain for open science

@@
 In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
-Scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing, that creates a digital footprint able to keep a 'trail of research';
-to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
+The intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a collaborative open science infrastructure \cite{ReviewBlockchain2019}.
 

### 2020-06-07 paper-v1.tex
introducing the problem

--- 2020-06-07 paper-v1.tex
@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'Bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{Bitcoin}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum-Wood}.
 Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.
 In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
-Scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing, that creates a digital footprint able to keep a 'trail of research';
-to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
-
+Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
+A thorny issue in the academic system that can be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis.
+In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy.
 The paper is structured as follows.
@@
 In principle, everyone can contribute in the collaboration: scientists, PhD students and even enthusiastic amateurs.
-
-\subsection{Ideas here}
 
@@
 Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
-\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin\cite{Bitcoin} as its first application.
+\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin \cite{Bitcoin} as its first application.
 \newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
@@
 \newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimity of Peer-Reviewers.
-\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses ZK-SNARKS to validate encrypted transactions.
+\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Zero-Knowledge \cite{ZeroKnoledge} proofs allow an actor (prover) to prove to another (verifier) that a statement is true, without revealing any information apart from the validity of the statement itself.
+\newline Zero-Knowledge \cite{ZeroKnoledge} proof is a mathematical cryptographic method that through values permutations allow one party (the prover) to prove to another (the verifier) the validity of a statement, without revealing the statement itself.
 \newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
 This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
-\subsubsection{Privacy/anonymity}.
-To enhance the peer-reviewer's privacy, we would like to implement zkANT, an ERC20 token, Ant, wrapped into AZTEC Protocol ZK-SNARKs, a non-interactive type of zero-knowledge privacy protocol to enable private transactions on Ethereum.
-Zero-knowledge proof is a mathematical cryptographic method that through values permutations allows one party (the prover) to prove to another (the verifier) the veracity of a statement, without having to reveal what the statement is.
-We will use ZK-SNARKs (which stands for “Zero-Knowledge Succinct Non-Interactive Argument of Knowledge”) via the open source libraries of AZTEC protocol.
-AZTEC, now TURBOPLONK bla bla (faster?) combines the confidentiality of the transactions (the value of the transaction is hidden, the amount of token (?) is not revealed thus preventing biases in the peer-review quadratic voting process = "I want to bet on this review because I want to win the bounty") with general-purpose computation (it's a Turing-complete Virtual Machine): this means transaction are not limited just to the local cryptocurrency (in our case ANT) but cross-asset trades are allowed (I can exchange ANT tokesn with other crypto-currencies).
+
 \section{Discussions}

### 2020-06-07 paper-v1.tex
citations

@@
 
-\input{solidity-highlighting.tex}	% copy the file from this repo
+\input{solidity-highlighting.tex}
+
+% copy the file from this repo
 % Used for displaying a sample figure. If possible, figure files should
@@
 Therefore, scientific dissemination is affected.
-Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system.
-We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication.
-If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer.
-To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
-\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
+Here, to solve this issue, we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system.
+We designed a Protocol of smart contracts called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication.
+If requirements are met, peer-reviews will be accepted and payed by the Issuer.
+To promote ethical behaviour the system will implement an incentive mechanism on AntsReview.
+\keywords{Blockchain  \and Open Science \and Privacy \and Peer-review \and Incentivization.}
 \end{abstract}
@@
 Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-A thorny issue in the academic system that can be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis.
-In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy.
+A thorny issue in the academic system that can be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
+In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy and in line with the values of Open Science.
 The paper is structured as follows.
@@
 \subsection{Peer-review: a flawed and outdated system}
+peer review is a ﬂawed process,\cite{Smith2006}
 
-"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers.
-Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9.
-Overall, the review process is considered opaque and expensive, slowing down the speed of scientific discovery and progress."
+a study to evaluate the feasibility of an open peer review system.
+\cite{Walsh200-openpeerrev} Of  the  referees  approached,  76%agreed to sign their name. This figure com-agreed to sign their name.
+\cite{PeerRev-NatComm}
+open peer review does not compromise the process, at least when referees are able to protect their anonymity.
+However, it is worth noting that unlike recent survey results14, here only 8.1 of referees agreed to reveal their identity.
+Although certain beneﬁts of open science and open evaluation are incontrovertible21,22, our ﬁndings suggest that the veil of anonymity is key also for open peer review.
+It is probable that this reﬂects the need for protection from possible retaliation or other unforeseen implications of open peer review, p
 
-Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination.
-However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times.
-\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications.
-\paragraph{Traditional peer-review process} This section takes inspiration from the editorial processes at \emph{Nature Methods} and \emph{Wiley}.
-\begin{enumerate}
-    \item The author submits a manuscript to the journal.
-    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
-    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria.
-If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
-    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers.
-Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
-    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability.
-They then accept or decline.
-If they decline, they might suggest alternative reviewers.
-Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
-    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified.
-The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves.
-    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
-    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
-    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
-The same reviewers might be contacted again and if they want they can follow up the peer-review process.
-    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.
+\cite{Gropp-PeerRevStress}
+authors have consistently reported that the purpose of peer review is for improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.
 
-\end{enumerate}
-\subsubsection{It's unaccredited and unpaid.} This is mainly due to the fact that the reviewers that are normally appointed by authors and/or editors are actually full-time researchers themselves, who work on a volunteer basis taking time from their primary research.
-Though things are changing, and now more and more journals encourage a transparent peer review process with the publication of reviewers names and reports, in most of the cases, to guarantee an unbiased output, journals don’t even get credit researchers for this form of unpaid work.
-On top of this, author-level metrics that measure the scientific impact and productivity of academics, such as the h-index, and are taken into account by the funding agencies, are purely based on the number of citations per each publications while neglecting the full spectrum of scientific contributions (software, data collection, presentations, reviews…).
-Therefore, peer-reviewing is an intellectual investment without any external return for researchers’ career.
-A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either have good research unpublished (because unreviewed) and abandoned in preprint archives or bad science published through sloppy and uncritical reviews [5].
-\subsubsection{It's vulnerable to bias and fraud.} Last but not least, the ‘publish or perish’ culture has been more and more inducing malicious behaviour during the peer-review process, such as attempts of scientific fraud (authors trying to review their own papers) and abuse (reviewers producing extremely harsh reviews to damage competitors by blocking the publication of their ideas).
-Finally, the current peer-review system is usually not double-blind, thus making its decisional process vulnerable to all forms of biases (gender bias, cultural bias, professional bias, etc...).
-These trust problems are one of the major issues facing scholarly communication.
+The idea of financially compensating individuals for reviewing manuscripts was suggested, but individuals who have experimented with this model urged caution, noting that it is expensive and does not necessarily produce the desired outcome.
 
-\subsubsection{Types of peer-review}
-\begin{itemize}
-    \item single-blind peer review
-    \item double-blind peer review
-    \item transparent peer review
-    open identities open reports open participation open interaction open platform ('decoupled review')
-\end{itemize}
+The question of how  or whether to incentivize reviews for articles or proposals is challenging.
+Budgets are tight and not expected to grow in the near term.
+Therefore, financial incentives come at the cost of either funding or publishing more research.
+Moreover, some journal editors who have thought about or experimented with providing financial rewards to reviewers urged caution because the efforts were expensive and did not seem to provide an adequate incentive to encourage individuals to review manuscripts.
+
+\cite{Kendall-peerrev}
+His study, done for Nature, found no evidence for lengthening delays2: the median review time — the time between submission and acceptance of a paper — has hovered at around 100 days for more than 30 years (see ‘Paper wait’)
+An analysis of all papers in PubMed up to 2015 with listed submission and acceptance dates suggests that the median time from submission to acceptance has hovered at around 100 days, although it has gone up at some journals.
+
+An analysis of PubMed papers published in 2013 suggests that journals with the lowest and highest impact factors have the longest review times.
+
+He found that the mean review time had roughly doubled in the past decade, from 50–130 days to 150–250 days, depending on the journa
 
@@
 
-AntsReview [\ref{appendix:b}] is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}
+AntsReview \cite{Ant} is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}
 \newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
@@
 
-AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
+AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
 \newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
@@
 \newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
-\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
+\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the ramification derived from the leaf, the root hash and finally the leaf we want to verify.
 \newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
@@
 AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline \textbf{Ant}, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
-\newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \textbf{\emph{Ant}} ans symbol: \textbf{\emph{ANT}}.
+\newline Ant \ref{code:Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
+\newline Ant is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \emph{Ant} ans symbol: \emph{ANT}.
 \newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
-\newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
-\newline \textbf{Hive}.
-When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
+\newline An AntsReview DAO will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
+\newline Hive. When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR or Compound, with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR or Compound, with name: \emph{Hive} and symbol: \emph{HIVE}
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent equally to the peer-reviewers that fulfilled the AntReview.
-\newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkAnt, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
 \newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
@@
 This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
+
+\begin{lstlisting}[language=Solidity]
+/// SPDX-License-Identifier: GPL-3.0
+pragma solidity 0.6.8;
+
+///@title AntsReview
+///@author Nazzareno Massari
+///@notice Ant ERC20 Token
+///@dev All function calls are currently implemented without side effecs through TDD approach
+///@dev OpenZeppelin library is used for secure contract development
+
+import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
+
+contract Ant is ERC20PresetMinterPauser {
+
+  constructor()
+  ERC20PresetMinterPauser("Ant", "ANT")
+  public {
+
+  }
+
+}
+\end{lstlisting}
 
@@
 
-\section{Appendix}
-
-\appendix
-
-\section{AntsReviewRoles.sol}
-
-\label{appendix:a}
-
-\begin{lstlisting}[language=Solidity]
-
-  /// SPDX-License-Identifier: GPL-3.0
-  pragma solidity 0.6.8;
-
-  ///@title AntsReview
-  ///@author Nazzareno Massari
-  ///@notice AntsReviewRoles Access Management for Issuer and Peer-Reviewer
-  ///@dev All function calls are currently implemented without side effecs through TDD approach
-  ///@dev OpenZeppelin library is used for secure contract development
-
-  import "@openzeppelin/contracts/access/Ownable.sol";
-  import "@openzeppelin/contracts/access/AccessControl.sol";
-  import "@openzeppelin/contracts/utils/Pausable.sol";
-
-  contract AntsReviewRoles is Ownable, AccessControl, Pausable {
-
-    /// Roles
-    bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
-    bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");
-    bytes32 public constant PAUSER_ROLE = keccak256("PAUSER_ROLE");
-
-    constructor() public {
-            _setupRole(DEFAULT_ADMIN_ROLE, owner());
-            _setupRole(PAUSER_ROLE, owner());
-    }
-
-      /// Modifiers
-      modifier onlyAdmin() {
-          require(isAdmin(msg.sender), "Caller is not an admin");
-          _;
-        }
-
-      modifier onlyIssuer() {
-          require(isIssuer(msg.sender), "Caller is not an issuer");
-          _;
-      }
-
-      modifier onlyPeerReviewer() {
-          require(isPeerReviewer(msg.sender), "Caller is not a peer-reviewer");
-          _;
-      }
-
-      /// Functions
-
-      function isAdmin(address account) public view returns (bool) {
-        return hasRole(DEFAULT_ADMIN_ROLE, account);
-      }
-
-      function isIssuer(address account ) public view returns (bool) {
-        return hasRole(ISSUER_ROLE, account);
-      }
-
-      function isPeerReviewer(address account ) public view returns (bool) {
-        return hasRole(PEER_REVIEWER_ROLE, account);
-      }
-
-      function addIssuer(address account) public onlyAdmin returns (bool) {
-        require(!isIssuer(account), "Account is already an issuer");
-        grantRole(ISSUER_ROLE, account);
-        return true;
-      }
-
-      function addPeerReviewer(address account) public onlyAdmin returns (bool) {
-        require(!isPeerReviewer(account), "Account is already a peer-reviewer");
-        grantRole(PEER_REVIEWER_ROLE, account);
-        return true;
-      }
-
-      function removeIssuer(address account) public onlyAdmin returns (bool) {
-        require(isIssuer(account), "Account is not an issuer");
-        revokeRole(ISSUER_ROLE, account);
-        return true;
-      }
-
-      function removePeerReviewer(address account) public onlyAdmin returns (bool) {
-        require(isPeerReviewer(account), "Account is not a peer-reviewer");
-        revokeRole(PEER_REVIEWER_ROLE, account);
-        return true;
-      }
-
-      /// @notice Pause all the functions
-      /// @dev the caller must have the 'PAUSER_ROLE'
-      function pause() public {
-        require(hasRole(PAUSER_ROLE, msg.sender), "BadgeFactory: must have pauser role to pause");
-        _pause();
-      }
-
-      /// @notice Unpause all the functions
-      /// @dev the caller must have the 'PAUSER_ROLE'
-      function unpause() public {
-            require(hasRole(PAUSER_ROLE, msg.sender), "BadgeFactory: must have pauser role to unpause");
-            _unpause();
-      }
-  }
-
-\end{lstlisting}
-
-\newpage
-\section{AntsReview.sol}
-
-\label{appendix:b}
-
-\begin{lstlisting}[language=Solidity]
-  /// SPDX-License-Identifier: GPL-3.0
-  pragma solidity 0.6.8;
-
-  ///@title AntsReview
-  ///@author Nazzareno Massari
-  ///@notice AntsReview to allows issuer to issue an antReview which peer-reviewers can fulfill
-  ///@dev All function calls are currently implemented without side effecs through TDD approach
-  ///@dev OpenZeppelin library is used for secure contract development
-
-  import "./AntsReviewRoles.sol";
-  import "@openzeppelin/contracts/math/SafeMath.sol";
-  import "@openzeppelin/contracts/utils/Address.sol";
-  import "@openzeppelin/contracts/utils/Counters.sol";
-
-  interface AntToken {
-    function transfer(address reciptient, uint amount) external returns (bool);
-    function balanceOf(address account) external view returns (uint);
-  }
-
-  contract AntsReview is AntsReviewRoles {
-
-    using SafeMath for uint256;
-    using Address for address payable;
-    using Counters for Counters.Counter;
-
-    /// Enums
-    enum AntReviewStatus { CREATED, ACCEPTED, CANCELLED }
-
-    /// Token
-    AntToken internal ant;
-
-    /// Counter
-    Counters.Counter private _antReviewIdTracker;
-
-    /// Storage
-    AntReview[] public antreviews;
-
-    mapping(uint256 => Peer_Review[]) peer_reviews;
-
-    /// Structs
-    struct AntReview {
-        address payable issuer;
-        uint256 deadline;
-        string ipfs_hash;
-        AntReviewStatus status;
-        uint256 amount; //in wei
-    }
-
-    struct Peer_Review {
-        bool accepted;
-        address payable peer_reviewer;
-        string ipfs_hash;
-    }
-
-    /// Events
-
-    event AntReviewIssued(address issuer, uint256 amount, string ipfsHash);
-    event AntReviewFulfilled(uint256 antReviewId, address peer_reviewer, uint256 peerReviewId, string ipfsHash);
-    event AntReviewAccepted(uint256 antReviewId, address issuer, address peer_reviewer, uint256 indexed peerReviewId, uint256 amount);
-    event AntReviewCancelled(uint256 indexed antReviewId, address indexed issuer, uint256 amount);
-
-    constructor(address ant_) public {
-      ant = AntToken(ant_);
-    }
-
-    /// Fallback
-
-    fallback() external payable {
-      revert();
-    }
-
-    receive() external payable {
-      revert();
-    }
-
-    /// Modifiers
-
-    modifier hasValue() {
-        require(msg.value > 0);
-        _;
-    }
-
-    modifier antReviewExists(uint256 _antReviewId){
-      require(_antReviewId < antreviews.length);
-      _;
-    }
-
-    modifier peerReviewExists(uint256 _antReviewId, uint256 _peerReviewId){
-      require(_peerReviewId < peer_reviews[_antReviewId].length);
-      _;
-    }
-
-    modifier hasStatus(uint256 _antReviewId, AntReviewStatus _desiredStatus) {
-      require(antreviews[_antReviewId].status == _desiredStatus);
-      _;
-    }
-
-    modifier peerReviewNotYetAccepted(uint256 _antReviewId, uint256 _peerReviewId) {
-      require(peer_reviews[_antReviewId][_peerReviewId].accepted == false);
-      _;
-    }
-
-    modifier validateDeadline(uint256 _newDeadline) {
-        require(_newDeadline > now);
-        _;
-    }
-
-    modifier isBeforeDeadline(uint256 _antReviewId) {
-      require(now < antreviews[_antReviewId].deadline);
-      _;
-    }
-
-    ///@notice Instantiates a new AntReview
-    ///@dev Access restricted to Issuer
-    ///@param _deadline The unix timestamp after which fulfillments will no longer be accepted
-    ///@param _ipfsHash The IPFS Hash of the Scientific Paper
-    ///@return True If the antReview is successfully issued
-    function issueAntReview(
-        string calldata _ipfsHash,
-        uint64 _deadline
-    )
-        external
-        payable
-        hasValue()
-        validateDeadline(_deadline)
-        onlyIssuer()
-        whenNotPaused()
-        returns (bool)
-    {
-        _antReviewIdTracker.increment();
-        antreviews.push(AntReview(msg.sender, _deadline, _ipfsHash, AntReviewStatus.CREATED, msg.value));
-        emit AntReviewIssued(msg.sender, msg.value, _ipfsHash);
-        return true;
-    }
-
-    ///@notice Submit a fulfillment for the given antReview
-    ///@dev Access restricted to Peer-Reviewer
-    ///@param _antReviewId The index of the antReview to be fufilled
-    ///@param _ipfsHash The IPFS Hash which contains evidence of the fufillment
-    ///@return True If the AntReview is successfully fulfilled
-    function fulfillAntReview(uint256 _antReviewId, string memory _ipfsHash)
-      public
-      antReviewExists(_antReviewId)
-      onlyPeerReviewer()
-      hasStatus(_antReviewId, AntReviewStatus.CREATED)
-      isBeforeDeadline(_antReviewId)
-      whenNotPaused()
-      returns (bool)
-    {
-      peer_reviews[_antReviewId].push(Peer_Review(false, msg.sender, _ipfsHash));
-      emit AntReviewFulfilled(_antReviewId, msg.sender, (peer_reviews[_antReviewId].length.sub(1)),_ipfsHash);
-      return true;
-    }
-
-    ///@notice Accept a given Peer-Review
-    ///@dev Access restricted to Issuer
-    ///@param _antReviewId the index of the antReview
-    ///@param _peerReviewId the index of the fulfillment being accepted
-    ///@return True If the AntReview is successfully being accepted
-    function acceptAntReview(uint256 _antReviewId, uint256 _peerReviewId)
-        public
-        antReviewExists(_antReviewId)
-        peerReviewExists(_antReviewId,_peerReviewId)
-        onlyIssuer()
-        hasStatus(_antReviewId, AntReviewStatus.CREATED)
-        peerReviewNotYetAccepted(_antReviewId, _peerReviewId)
-        whenNotPaused()
-        returns (bool)
-    {
-        peer_reviews[_antReviewId][_peerReviewId].accepted = true;
-        antreviews[_antReviewId].status = AntReviewStatus.ACCEPTED;
-        peer_reviews[_antReviewId][_peerReviewId].peer_reviewer.sendValue(antreviews[_antReviewId].amount);
-        emit AntReviewAccepted(
-          _antReviewId,
-          antreviews[_antReviewId].issuer,
-          peer_reviews[_antReviewId][_peerReviewId].peer_reviewer,
-          _peerReviewId, antreviews[_antReviewId].amount
-        );
-        return true;
-    }
-
-    ///@notice Cancels the antReview and send the funds back to the issuer
-    ///@dev Access restricted to Issuer
-    ///@param _antReviewId the index of the antReview
-    ///@return True If the AntReview is successfully cancelled
-    function cancelAntReview(uint256 _antReviewId)
-        public
-        antReviewExists(_antReviewId)
-        onlyIssuer()
-        hasStatus(_antReviewId, AntReviewStatus.CREATED)
-        whenNotPaused()
-        returns (bool)
-    {
-        antreviews[_antReviewId].status = AntReviewStatus.CANCELLED;
-        antreviews[_antReviewId].issuer.sendValue(antreviews[_antReviewId].amount);
-        emit AntReviewCancelled(_antReviewId, msg.sender, antreviews[_antReviewId].amount);
-        return true;
-    }
-
-  }
-
-\end{lstlisting}
-
-\newpage
-\section{Ant.sol}
-\label{appendix:c}
-
-\begin{lstlisting}[language=Solidity]
-  /// SPDX-License-Identifier: GPL-3.0
-  pragma solidity 0.6.8;
-
-  ///@title AntsReview
-  ///@author Nazzareno Massari
-  ///@notice Ant ERC20 Token
-  ///@dev All function calls are currently implemented without side effecs through TDD approach
-  ///@dev OpenZeppelin library is used for secure contract development
-
-  import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
-
-  contract Ant is ERC20PresetMinterPauser {
-
-    constructor()
-    ERC20PresetMinterPauser("Ant", "ANT")
-    public {
-
-    }
-
-  }
-\end{lstlisting}
-
-\newpage
-
 % ---- Bibliography ----

### 2020-06-07 paper-v1.tex
Update

@@
 Here, to solve this issue, we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system.
-We designed a Protocol of smart contracts called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication.
+We designed a Protocol of smart contracts called Ants-Review that allows any author to issue a call for peer-reviewing their scientific publication.
 If requirements are met, peer-reviews will be accepted and payed by the Issuer.
@@
 In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy and in line with the values of Open Science.
-The paper is structured as follows.
+\newline The paper is structured as follows.
 Sections 2 presents research background and related works.
@@
 An analysis of all papers in PubMed up to 2015 with listed submission and acceptance dates suggests that the median time from submission to acceptance has hovered at around 100 days, although it has gone up at some journals.
+
+\cite{tragedy-reviewers} overburdened reviewer pool,we observe a progressive increase in journals without an increase in the number of reviewers.
+suggestions for improvements are lost
 
@@
 AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline Ant \ref{code:Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
+\newline Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
 \newline Ant is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \emph{Ant} ans symbol: \emph{ANT}.
@@
 In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
-We showed how blockchain technology could provide an efficient and viable solution and open up possible directions for a change in paradigm in scientific communication.
+We showed how blockchain technology could provide an efficient and viable solution and open up possible directions for a paradigm shift in scientific communication.
 We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review.
-We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.
+We exposed the architecture of our project and our for which we adopted cutting-edge tools from the open source blockchain ecosystem.
 

### 2020-06-07 paper-v1.tex
desperate commit

@@
 Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-A thorny issue in the academic system that can be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
+A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
 In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy and in line with the values of Open Science.
@@
 \section{Background}
-\subsection{Peer-review: a flawed and outdated system}
-peer review is a ﬂawed process,\cite{Smith2006}
-
-a study to evaluate the feasibility of an open peer review system.
-\cite{Walsh200-openpeerrev} Of  the  referees  approached,  76%agreed to sign their name. This figure com-agreed to sign their name.
-\cite{PeerRev-NatComm}
-open peer review does not compromise the process, at least when referees are able to protect their anonymity.
-However, it is worth noting that unlike recent survey results14, here only 8.1 of referees agreed to reveal their identity.
-Although certain beneﬁts of open science and open evaluation are incontrovertible21,22, our ﬁndings suggest that the veil of anonymity is key also for open peer review.
-It is probable that this reﬂects the need for protection from possible retaliation or other unforeseen implications of open peer review, p
-
-\cite{Gropp-PeerRevStress}
-authors have consistently reported that the purpose of peer review is for improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.
-
-The idea of financially compensating individuals for reviewing manuscripts was suggested, but individuals who have experimented with this model urged caution, noting that it is expensive and does not necessarily produce the desired outcome.
-
-The question of how  or whether to incentivize reviews for articles or proposals is challenging.
-Budgets are tight and not expected to grow in the near term.
-Therefore, financial incentives come at the cost of either funding or publishing more research.
-Moreover, some journal editors who have thought about or experimented with providing financial rewards to reviewers urged caution because the efforts were expensive and did not seem to provide an adequate incentive to encourage individuals to review manuscripts.
-
-\cite{Kendall-peerrev}
-His study, done for Nature, found no evidence for lengthening delays2: the median review time — the time between submission and acceptance of a paper — has hovered at around 100 days for more than 30 years (see ‘Paper wait’)
-An analysis of all papers in PubMed up to 2015 with listed submission and acceptance dates suggests that the median time from submission to acceptance has hovered at around 100 days, although it has gone up at some journals.
-
-\cite{tragedy-reviewers} overburdened reviewer pool,we observe a progressive increase in journals without an increase in the number of reviewers.
-suggestions for improvements are lost
-
-An analysis of PubMed papers published in 2013 suggests that journals with the lowest and highest impact factors have the longest review times.
-
-He found that the mean review time had roughly doubled in the past decade, from 50–130 days to 150–250 days, depending on the journa
+\subsection{Peer-review: present problems and mild solutions}
+Peer review is still the only quality control mechanism devoted to evaluate scientific outcomes.
+The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}.
+However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues, here reviewed.
+\paragraph{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
+In the traditional peer-review process the author(s) submit manuscript to the journal where an editorial team assesses if the paper meets meets the scopes of the journal and novelty criteria.
+If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers.
+Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
+The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves (single-blind review).
+Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript.
+The handling editor or the editorial team considers all the submitted reports and makes the final decision.
+If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
+The same reviewers might be contacted again and if they want they can follow up the peer-review process.
+This process can take multiple rounds and is a huge time investment both for authors and reviewers.
+An analysis of all papers published in PubMed for a time period of 30 years claims that the median review time is around 100 days\cite{Kendall-peerrev}.
+Another study, taken in 2013, calculated that approximately 30.5 million researcher hours was spent on reviewing papers.
+\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution.
+To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
+\paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
+Some studies have reported an improvement in the transparency and 'civility; of the review process when open reports are released (open peer review).
+\paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?". 
+\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals and the number of experienced reviewers assigned which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers}.
+\paragraph{Lack of recognition.}
 
@@
 \newline Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
-\newline Ant is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \emph{Ant} ans symbol: \emph{ANT}.
+\newline Ant (as shown below) is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \emph{Ant} ans symbol: \emph{ANT}.
 \newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
@@
 \subsubsection{Supplementary material}
-TBD
+Souce Code, DOI: 10.5281/ZENODO.3829162
+\newline Demo (PoC), DOI: 10.5281/ZENODO.3829183
 
 \subsubsection{CRediT Authorship Contribution Statement}
-TDB
+ Bianca Trovò: Conceptualization, Investigation, Writing - original draft, Writing - review \& editing.
+Nazzareno Massari: Project administration, Methodology, Validation, Software development, Visualization, Writing \& editing.
+Both authors equally contributed and supervised the project.
 
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for internal review and useful comments.
-
-\newpage
+\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for useful comments.
 

### 2020-06-07 paper-v1.tex
cutting

@@
 \paragraph{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
-In the traditional peer-review process the author(s) submit manuscript to the journal where an editorial team assesses if the paper meets meets the scopes of the journal and novelty criteria.
-If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers.
-Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
+The traditional peer-review process is completely controlled by the editor(s).
+The author(s) submit manuscript to the journal where an editorial team assesses if the paper meets meets the scopes of the journal and novelty criteria.
+If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
 The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves (single-blind review).
-Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript.
-The handling editor or the editorial team considers all the submitted reports and makes the final decision.
+Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft.
 If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
@@
 An analysis of all papers published in PubMed for a time period of 30 years claims that the median review time is around 100 days\cite{Kendall-peerrev}.
-Another study, taken in 2013, calculated that approximately 30.5 million researcher hours was spent on reviewing papers.
 \paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution.
@@
 \paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?". 
-\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals and the number of experienced reviewers assigned which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers}.
-\paragraph{Lack of recognition.}
-
-\subsection{Related work}
-Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like impact factor h-index.
-In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
-\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
-\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
-ScienceOpen
-\emph{DEIP}
-Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
-\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews.
-\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
-\emph{ReviewCoin}
-\emph{I8X Platform}
-A more comprehensive reform of academic endorsement has been proposed in the manifesto ‘Towards Open Science:The Case for a Decentralized Autonomous Endorsement System11’, published anonymously.The author(s) propose a new academic endorsement system that is not based on current journal publication practices which are argued to be expensive, slow, disregard non-traditional output and negative results, and which give too much power to editors and publishers.
-Built on the blockchain, the Academic Endorsement System (AES) is based on a new form of currency, coined academic endorsement points (AEP), which can be used by scientists to reward scientific work that is worthy of endorsement.
-Moreover, the amount of AEP credited to a scientist is based on the AEP received for previous work.
-Researchers whose output has been endorsed to a high degree will have a larger influence in the community.
-Any kind of research output could be endorsed, for example blog posts, data sets, software etc.Another advantage is that this system would be faster than the time it takes for citation metrics to accrue.
-The startup Matryx.ai13 aims to transform the nature of research collaboration itself.
-Its initiators claim that one of the problems with current scientific practices is its incentive structure.
-Scientific awards, for example, are based on competition rather than on collaboration, despite the fact that new ideas are usually collaborative in nature.
-Moreover, different researchers and research groups are often working on the same problems, wasting, as they claim on their website,‘brain power’, time and money.
-Matryx intends to provide a platform enabling and incentivising research collaboration while discouraging solitary and siloed research.
-On Matryx, a research project starts when users set a bounty on a problem that they want the community to solve.
-Contributors solve these problems by working with each other on the platform.The collaboration is tracked through the blockchain thus ensuring contributors are credited appropriately when the problem is solved.
-In principle, everyone can contribute in the collaboration: scientists, PhD students and even enthusiastic amateurs.
+\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals and the number of experienced reviewers assigned which demands an expansion of the reviewer's pool including early career scientists.
+\cite{tragedy-reviewers}.
+\paragraph{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
+Thus, it does not lead to advancements in career or help securing grants.
+Researchers are motivated in doing peer-review for a sense of belonging and a desire to 'give back' to the community.
+A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science being published through sloppy and uncritical reviews.
+Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
+It's worth mentioning: Publons\cite{Publons}a service integrated with ORCID (researcher identifier) that provides peer-review metric; Peerage of Science\cite{Peerage}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
 
@@
 
-\subsubsection{Perspectives for a Decentralized Autonomours Organization (DAO)}
+\subsubsection{Perspectives for a Decentralized Autonomous Organization (DAO)}
 
@@
 \subsubsection{Supplementary material}
-Souce Code, DOI: 10.5281/ZENODO.3829162
+Source Code, DOI: 10.5281/ZENODO.3829162
 \newline Demo (PoC), DOI: 10.5281/ZENODO.3829183

### 2020-06-07 paper-v1.tex
remove bugs

@@
 Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
-A previous version of this paper can be found here \cite{AntsReview}, as a proposal submitted for the ETH Turin 2020 Hackathon.
-and its design and attempt of implementation are exposed in the following section.
-Here we expose the main traits/features of AR
+A previous version of this paper can be found here \cite{AntsReview}.Its design and implementation are exposed in the following section.
+Here we expose the main features of AntsReview:
 \begin{itemize}
-\item accountability: both for recognition and for security vs fraud abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest.
-this means the platform acts like a version control system where commit are permanent and hashed
-\item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
-\item incentivisation: via symbolic and material recognition of the performed work. reputation and bounties
-\item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
+\item \emph{accountability}: both for recognition and for security against fraud and abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest.
+This means the platform acts like a version control system where commit are permanent and hashed;
+\item \emph{transparency of the records}: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
+\item \emph{incentivisation}: via symbolic and material recognition of the performed work. reputation and bounties
+\item \emph{inclusiveness via gamification}: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
 \end{itemize}
@@
 In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
-We showed how blockchain technology could provide an efficient and viable solution and open up possible directions for a paradigm shift in scientific communication.
-We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review.
-We exposed the architecture of our project and our for which we adopted cutting-edge tools from the open source blockchain ecosystem.
+We showed how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
+We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-reviews.
+We exposed the architecture of our project for which we adopted cutting-edge tools from the open source blockchain ecosystem.
 

### 2020-06-07 paper-v1.tex
typos

@@
 A previous version of this paper can be found here \cite{AntsReview}.Its design and implementation are exposed in the following section.
+\subsection{Design}
 Here we expose the main features of AntsReview:
@@
 This means the platform acts like a version control system where commit are permanent and hashed;
-\item \emph{transparency of the records}: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
+\item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
 \item \emph{incentivisation}: via symbolic and material recognition of the performed work. reputation and bounties
-\item \emph{inclusiveness via gamification}: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
+\item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
 \end{itemize}
-crowdfunding schemes leveraged by blockchain technology
+
 In the following sections we describe the architecture of the system and its building blocks
@@
 
-\subsection{Design}
-
-There are two possible scenarios depending if we save the role of the editor and we integrate an existing journal or if AntsReview becomes a platform completely decoupled from journals.
+There are two possible scenarios depending if AntsReview integrates an existing journal or if AntsReview becomes a platform completely decoupled from journals.
 
@@
     \item The author submits a manuscript to the journal.
-    \item If the papers passes stage 2-3 of editorial decision (appropriateness of style and coherence with the journal's scope)
-    \item the editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
-    \item (footnote?) the bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
+    \item If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope)
+    \item The editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
+    \item The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
     \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
@@
 However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by Anters (members of the community) via Quadratic Voting to rank the most prolific peer-reviewers.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the Anters (members of the community) via Quadratic Voting to rank the most prolific peer-reviewers.
 

### 2020-06-07 paper-v1.tex
push

@@
 
-In the following sections we describe the architecture of the system and its building blocks
-AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
-
 There are two possible scenarios depending if AntsReview integrates an existing journal or if AntsReview becomes a platform completely decoupled from journals.
@@
 However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the Anters (members of the community) via Quadratic Voting to rank the most prolific peer-reviewers.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the Anters (members of the community) via Quadratic Voting to rank the best peer-reviews.
 
@@
 \begin{enumerate}
-    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform).
+    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform.
     \item The paper is accepted by the community for revision in its whatever format.
     \item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
-    \item (footnote?) the bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
-    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community/contributors.
+    \item The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
+    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community of contributors.
     \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
-    \item Not all reviews will have the same quality and depth.
-However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community via Quadratic Voting.
+    \item Reviews will be voted by the community via Quadratic Voting.
     \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
-Since it's in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit.
-It will also fuel ethical behaviour.
+Since it is in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit and therefore will fuel ethical behaviour.
 
@@
 \subsection{Implementation}
-
+In the following sections we describe the architecture of the system and its building blocks.
+AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
 \begin{figure}

### 2020-06-09 paper-v1.tex
fixed bibliography

@@
 \item The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
-    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community of contributors.
+\item Reviews fulfilling the smart\-contract requirements are validated by the AntsReview community of contributors.
 \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
@@
 \subsection{Implementation}
-In the following sections we describe the architecture of the system and its building blocks.
-AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
+
 \begin{figure}
@@
 \end{figure}
+
+In the following sections we describe the architecture of the system and its building blocks.
+AntsReview is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
+
 In this section we provide an overview of how we implemented the system by focusing on its components.
@@
 \begin{itemize}
-\item AntsReview - manage access management and the basic system.
-\item Tokenomics - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
-\item Privacy - maintains the anonymity of the system via AZTEC Protocol.
+\item \emph{AntsReview}, which manages access management and the basic system.
+\item \emph{Tokenomics}, which manages the system of incentivization mechanism by integrating ideas from DeFi (Decentralized Finance) and Quadratic Voting.
+\item \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol.
 \end{itemize}
@@
 \subsubsection{AntsReview}
-
 AntsReview \cite{Ant} is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}
-\newline It implements a Bounty-like system where an issuer (author) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
+\newline It implements a bounty-like system where an issuer (author or editor) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that s/he is creating:
 \begin{itemize}
@@
 \newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
-\newline In this way, only the Issuer (author) can create a new AntReview.
+\newline In this way, only the Issuer can create a new AntReview.
 \newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
-\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
+\newline The AntReview after being validated is then accepted by the Issuer and paid between Peer-Reviewers.
 \newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
@@
 \newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin \cite{Bitcoin} as its first application.
-\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
+\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consensus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
 \newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
@@
 \subsubsection{Tokenomics}
-
 AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
@@
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
-\newline An AntsReview DAO will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
-\newline Hive. When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
-\newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR or Compound, with name: \emph{Hive} and symbol: \emph{HIVE}
-\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent equally to the peer-reviewers that fulfilled the AntReview.
-\newline zkAnt, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
-\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
-This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
 
@@
 \subsubsection{Privacy}
-
 The Anonymity of an agent in the system is achieved in two ways:
@@
 \section{Discussions}
+\subsection{Possible developments}
+ An AntsReview DAO could be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
+\newline Hive. When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
+\newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
+\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR or Compound, with name: \emph{Hive} and symbol: \emph{HIVE}
+\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent equally to the peer-reviewers that fulfilled the AntReview.
+\newline zkAnt, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
+This will allow to incentive prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
+
 \subsection{A new community-driven standard?}
-- a change is already happening: specially new born publishers are opening up review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research) -- from 2020 also Nature declared that will do the same.
-
-- new business model?
-at some point pre-print platforms (dissemination) might want to integrate peer-review (validation) into their platforms - dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt: how will they justify their added value?
-as Tennant points out: branding archiving
-
-- peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction
-
-- community-organized peer reviews: peer reviews will be more and more out of the hands of publishers, researchers will be the ones seeking the papers to review (like in Rubriq).
-
-future of quality control and moderation: open participation model, community-driven | certification and reputation: expansion of reviewer pool with fewer barriers to enter and more inclusion of young scientists, reputation build within community and not journals
-
-- portable peer review not only within a consortium of journals
-
--value of peer review as 'academic capital' recognized by research funders and hiring committees
-
--a bit off topic but: automated peer review (services such as StatReviewers) might fasten the formal aspects of the job allowing reviewers to focus on the content.
-
-\subsubsection{Perspectives for a Decentralized Autonomous Organization (DAO)}
+A change is already happening in the publishing industry specially with new born publishers are opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
+If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt: how will they justify their added value?\cite{Tennant2017-F1000R}.
+We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, researchers will be the ones seeking the papers to review with a reputation build within community and not journals.
+Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising in this direction.
+Our protocol system is not the only one: other prototypes are proposing an endorsement system for peer-review based on token economics \cite{ScienceMiles,ResearchCoin,Sharples-Kudos,Pevo,I8X}.
+We hope that soon such systems will be running and the value of peer review as 'academic capital' recognized by research funders and hiring committees.
 
@@
 \subsubsection{CRediT Authorship Contribution Statement}
- Bianca Trovò: Conceptualization, Investigation, Writing - original draft, Writing - review \& editing.
-Nazzareno Massari: Project administration, Methodology, Validation, Software development, Visualization, Writing \& editing.
+ Bianca Trovò: Conceptualization, Investigation, Design, Writing - original draft, Writing - review \& editing.
+Nazzareno Massari: Project administration, Design, Software development, Visualization, Writing - review \& editing.
 Both authors equally contributed and supervised the project.
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for useful comments.
+\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for useful comments and discussions and Marcelo Colmenero for the Pixel Art.
 
@@
 \bibliographystyle{splncs04}
-\bibliography{ref1-intro.bib, ref2-peerreview.bib, ref2-relatedwork.bib, ref3-system.bib}
+\bibliography{ref-antsrev.bib}
 

### 2020-06-10 paper-v1.tex
review by @naszam

@@
 If requirements are met, peer-reviews will be accepted and payed by the Issuer.
-To promote ethical behaviour the system will implement an incentive mechanism on AntsReview.
+To promote ethical behaviour the system will implement an incentive mechanism on Ants-Review.
 \keywords{Blockchain  \and Open Science \and Privacy \and Peer-review \and Incentivization.}
@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{Bitcoin}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum-Wood}.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
 Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.
@@
 Sections 2 presents research background and related works.
-Section 3 explains the proposed Ethereum-based protocol illustrating the system architecture and the current status of implementation.
+Section 3 explains the proposed protocol on the Ethereum blockchain illustrating the system architecture and the current status of implementation.
 In Sect.
@@
 Section 5 contains the conclusions.
-Appendixes present the smart contracts.
 
@@
 Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
-A previous version of this paper can be found here \cite{AntsReview}.Its design and implementation are exposed in the following section.
+\newline A previous version of this paper can be found here \cite{AntsReview}. 
+\newline Its design and implementation are exposed in the following section.
 \subsection{Design}
-Here we expose the main features of AntsReview:
+Here we describe the main features of AntsReview:
 \begin{itemize}
 \item \emph{accountability}: both for recognition and for security against fraud and abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest.
-This means the platform acts like a version control system where commit are permanent and hashed;
-\item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports
-\item \emph{incentivisation}: via symbolic and material recognition of the performed work. reputation and bounties
+This means the platform acts like a version control system where commits are permanent and their hashes timestamped;
+\item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the obscure system of black boxes of peer reviews in journals that centralize all the reports;
+\item \emph{incentivisation}: via symbolic and material recognition of the performed work. reputation and bounties;
 \item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
@@
 However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the Anters (members of the community) via Quadratic Voting to rank the best peer-reviews.
+In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the members of the community via Quadratic Voting to rank the best peer-reviews.
 
@@
 In the following sections we describe the architecture of the system and its building blocks.
-AntsReview is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
+Ants-Review is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
 
@@
 
-The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
+The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
 
 \begin{itemize}
-\item \emph{AntsReview}, which manages access management and the basic system.
-\item \emph{Tokenomics}, which manages the system of incentivization mechanism by integrating ideas from DeFi (Decentralized Finance) and Quadratic Voting.
+\item \emph{AntsReview}, which manages access management and the core system.
+\item \emph{Tokenomics}, which manages the incentivization mechanism of the system.
 \item \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol.
@@
 \subsubsection{AntsReview}
-AntsReview \cite{Ant} is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}
-\newline It implements a bounty-like system where an issuer (author or editor) is asked a series of actions, to ensure transparency and robustness, regarding the AntReview that s/he is creating:
+AntsReview is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM),  deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
+\newline It implements a bounty-like system where an issuer (author or editor) is asked a series of actions, to ensure transparency and consistency, regarding the AntReview that he/she is creating:
 \begin{itemize}
@@
 
-AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
-\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
+AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on 'AccessControl.sol' by OpenZeppelin Solidity Library \cite{OZ}, through the creation of the Issuer and Peer-Reviewer Roles.
+\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts.
 \newline In this way, only the Issuer can create a new AntReview.
 \newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
-\newline The AntReview after being validated is then accepted by the Issuer and paid between Peer-Reviewers.
+\newline The AntReview after being accepted by the Issuer is then paid between Peer-Reviewers.
 \newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
@@
 \newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin \cite{Bitcoin} as its first application.
-\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consensus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
-\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
-\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
+\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
+\newline AntsReview is considering the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
+\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
 \newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the ramification derived from the leaf, the root hash and finally the leaf we want to verify.
-\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).
+\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity.
 
 \subsubsection{Tokenomics}
-AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline Ant, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
-\newline Ant (as shown below) is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \emph{Ant} ans symbol: \emph{ANT}.
-\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
+AntsReview integrates few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+\newline Ant, is the primary protocol token and can be staked into an AntReview.
+\newline Ant [\ref{lst:code}] is implemented inheriting 'ERC20PresetMinterPauser.sol' from OpenZeppelin Library with name \emph{Ant} and symbol \emph{ANT}.
+\newline An AntReview, issued by an author will be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
 
-\begin{lstlisting}[language=Solidity]
+\begin{lstlisting}[caption={Ant.sol},label={lst:code},language=Solidity]
 /// SPDX-License-Identifier: GPL-3.0
@@
   \item PseudoAnonimity granted by an Ethereum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
-  \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK Proofs to reduce gas costs and improve scalability.
+  \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK\cite{PLONK} Proofs to reduce gas costs and improve scalability.
 \end{itemize}
@@
 An user can send messages from an externally owned account by creating and signing a transaction.
-\newline The limitation of such solution regarding the Privacy of the Protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
+\newline The limitation of such solution regarding the privacy of the protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
 \newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimity of Peer-Reviewers.
@@
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Zero-Knowledge \cite{ZeroKnoledge} proof is a mathematical cryptographic method that through values permutations allow one party (the prover) to prove to another (the verifier) the validity of a statement, without revealing the statement itself.
+\newline Zero-Knowledge \cite{ZeroKnoledge} proof is a mathematical cryptographic method that through value permutations allow one party (the prover) to prove to another (the verifier) the validity of a statement, without revealing the statement itself.
 \newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
@@
  An AntsReview DAO could be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
-\newline Hive. When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
+\newline Hive. When Anters make a deposit into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR or Compound, with name: \emph{Hive} and symbol: \emph{HIVE}
-\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent equally to the peer-reviewers that fulfilled the AntReview.
+\newline Hive will be implemented using a similar approach to Ant and Chai, an ERC20 token that accrues interest from MakerDAO's DSR or Compound, with name \emph{Hive} and symbol \emph{HIVE}
+\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent between the peer-reviewers that fulfilled the AntReview.
 \newline zkAnt, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
@@
 In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
-We showed how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
+We shown how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
 We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-reviews.
@@
 \bibliographystyle{splncs04}
-\bibliography{ref-antsrev.bib}
+\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-related.bib, ref3-system.bib,ref4-discuss.bib}
 

### 2020-06-10 paper-v1.tex
cleanup by @naszam

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{Bitcoin}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
 Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.

### 2020-06-12 paper-v1.tex
new changes in Design

@@
 Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
+\newline A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
 In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy and in line with the values of Open Science.
@@
 A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science being published through sloppy and uncritical reviews.
-Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
+\newline Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
 It's worth mentioning: Publons\cite{Publons}a service integrated with ORCID (researcher identifier) that provides peer-review metric; Peerage of Science\cite{Peerage}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
@@
 \newline Its design and implementation are exposed in the following section.
+
 \subsection{Design}
+
+\emph{Incentivisation.} A typical business model for open source software (OSS) movement is open-source bounty.
+Bounties are a prize or monetary reward given for completing a task before a deadline.
+Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are Gitcoin \cite{Gitcoin} and The Bounties Network \cite{Bounty}.
+Incentives can be cryptographic tokens, unit of values registered on a blockchain network and that represent the quantity and quality of a service within a network.
+\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals)  should be able to retribute with tokens, an internal cryptocurrency that can be spent externally.
+The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
+Thus, the system acts also as a reputation builder.
+\newline \emph{Transparency of the records} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report') even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+following the example of models of 'cascading' or 'portable peer-reviews' offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable
+
 Here we describe the main features of AntsReview:
@@
 \item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the obscure system of black boxes of peer reviews in journals that centralize all the reports;
-\item \emph{incentivisation}: via symbolic and material recognition of the performed work. reputation and bounties;
+\item \emph{incentivisation}: 
 \item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');

### 2020-06-12 paper-v1.tex
related work

@@
 An analysis of all papers published in PubMed for a time period of 30 years claims that the median review time is around 100 days\cite{Kendall-peerrev}.
-\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution.
-To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
-\paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
-Some studies have reported an improvement in the transparency and 'civility; of the review process when open reports are released (open peer review).
-\paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?". 
-\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals and the number of experienced reviewers assigned which demands an expansion of the reviewer's pool including early career scientists.
-\cite{tragedy-reviewers}.
 \paragraph{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
@@
 A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science being published through sloppy and uncritical reviews.
-\newline Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
-It's worth mentioning: Publons\cite{Publons}a service integrated with ORCID (researcher identifier) that provides peer-review metric; Peerage of Science\cite{Peerage}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
+\paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
+Some studies have reported an improvement in the transparency and 'civility; of the review process when open reports are released according to the standards of open peer review.
+\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution.
+To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
+\paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?". 
+\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists.
+\cite{tragedy-reviewers}.
+
+\subsection{Related work} Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
+\newline It's also worth mentioning \emph{Publons}\cite{Publons}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage} of Science\cite{Peerage} and \emph{ResearchSquare}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
+\emph{ScienceMiles} \cite{ScienceMiles} proposes a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process.
+\emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
+The system implements cryptoeconomical incentives for building reputation in the community of users.
 
@@
 
-\emph{Incentivisation.} A typical business model for open source software (OSS) movement is open-source bounty.
+Here we describe the main features of AntsReview.
+\paragraph{Incentivisation and recognition.} A typical business model for open source software (OSS) movement is open-source bounty.
 Bounties are a prize or monetary reward given for completing a task before a deadline.
@@
 Thus, the system acts also as a reputation builder. 
-\newline \emph{Transparency of the records} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report') even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-following the example of models of 'cascading' or 'portable peer-reviews' offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable
+\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews exchange to the same manuscript can have their tokens accrue interest over time (see Implementation).
 
-Here we describe the main features of AntsReview:
-\begin{itemize}
-\item \emph{accountability}: both for recognition and for security against fraud and abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest.
-This means the platform acts like a version control system where commits are permanent and their hashes timestamped;
-\item \emph{transparency of the records}: all reviews should be open access to the community ('open report') to prevent waste of knowledge and disrupt the obscure system of black boxes of peer reviews in journals that centralize all the reports;
-\item \emph{incentivisation}: 
+\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').
+
+\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to righteously attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
+This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
+InterPlanetary File System (IPFS) \cite{IPFS} is a decentralized content-addressable, peer-to-peer protocol which guarantees data immutability and unique file identification.
+
 \item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
-\end{itemize}
 

### 2020-06-12 paper-v1.tex
references related work

@@
 \newline It's also worth mentioning \emph{Publons}\cite{Publons}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage} of Science\cite{Peerage} and \emph{ResearchSquare}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
-\emph{ScienceMiles} \cite{ScienceMiles} proposes a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process.
+Spearpoint\cite{ResearchCoin} proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees.
+\emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process.
+Avital \cite{AvitalToken} suggests a token-based peer-review payment system.
 \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
 The system implements cryptoeconomical incentives for building reputation in the community of users.
+\newline Other proposals to improve the peer-review system have instead focused on features such as decentralization, security \cite{Pevo,CryptSubmit,MarsChain}.
 
@@
 \bibliographystyle{splncs04}
-\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-related.bib, ref3-system.bib,ref4-discuss.bib}
+\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-relatedwork.bib, ref3-system.bib,ref4-discuss.bib}
 

### 2020-06-12 paper-v1.tex
last git

@@
 \newline The paper is structured as follows.
-Sections 2 presents research background and related works.
+Sections 2 presents research background and related work.
 Section 3 explains the proposed protocol on the Ethereum blockchain illustrating the system architecture and the current status of implementation.
@@
 InterPlanetary File System (IPFS) \cite{IPFS} is a decentralized content-addressable, peer-to-peer protocol which guarantees data immutability and unique file identification.
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages
 
-\item \emph{inclusiveness via gamification}: all the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
+\paragraph{Inclusiveness via gamification.} ll the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
 
@@
 \includegraphics[scale=0.28]{AntsReview}
-\caption{AntsReview Smart Contracts}
+\caption{Ants-Review Smart Contracts}
 \label{fig:contracts}
@@
 In the following sections we describe the architecture of the system and its building blocks. 
-Ants-Review is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...
-
-In this section we provide an overview of how we implemented the system by focusing on its components.
-
-The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
+\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
 
@@
 \item \emph{Tokenomics}, which manages the incentivization mechanism of the system.
-\item \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol.
+\item \emph{Privacy}, which maintains the pseudo-anonymity of the system via AZTEC Protocol.
 \end{itemize}
@@
 \subsubsection{AntsReview}
-AntsReview is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM),  deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
-\newline It implements a bounty-like system where an issuer (author or editor) is asked a series of actions, to ensure transparency and consistency, regarding the AntReview that he/she is creating:
+AntsReview is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
+\newline It implements a bounty-like system (AntReview) where an issuer (author or editor) is asked a series of actions to ensure transparency and consistency for the AntReview that he/she is creating:
 \begin{itemize}
@@
 
-AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on 'AccessControl.sol' by OpenZeppelin Solidity Library \cite{OZ}, through the creation of the Issuer and Peer-Reviewer Roles.
-\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts.
-\newline In this way, only the Issuer can create a new AntReview.
-\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
-\newline The AntReview after being accepted by the Issuer is then paid between Peer-Reviewers.
-\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
+AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library \cite{OZ}, through the creation of the Issuer and Peer-Reviewer Roles.
+\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts.
+In this way, only the Issuer can create a new AntReview.
+\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.When the AntReview is accepted by the Issuer, the bounty is paid among Peer-Reviewers.On top of that, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
 \newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W.
-Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
-\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin \cite{Bitcoin} as its first application.
-\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
-\newline AntsReview is considering the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
+Scott Stornetta \cite{TimeStamp-Haber}.
+Pioneers of the blockchain, cited by the Bitcoin whitepaper\cite{Bitcoin}, they were on a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
+In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
+\newline Ants-Review exploits the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
 \newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
-\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the ramification derived from the leaf, the root hash and finally the leaf we want to verify.
+In order to verify if a specific hash is included into a Merkle Tree by leveraging on \emph{MerkleProof.sol} (OpenZeppelin Library), we need to provide a proof, generated from the leaf of interest, that represents the ramification derived from the leaf, the root hash and, finally, the leaf we want to verify.
 \newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity.
@@
 \newline Ant, is the primary protocol token and can be staked into an AntReview.
-\newline Ant [\ref{lst:code}] is implemented inheriting 'ERC20PresetMinterPauser.sol' from OpenZeppelin Library with name \emph{Ant} and symbol \emph{ANT}.
-\newline An AntReview, issued by an author will be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
-with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
+\newline Ant [see \ref{lst:code}] is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ant} and symbol \emph{ANT}.
 
@@
 
-///@title AntsReview
+///@title Ants-Review
 ///@author Nazzareno Massari
 ///@notice Ant ERC20 Token
-///@dev All function calls are currently implemented without side effecs through TDD approach
+///@dev All function calls are currently implemented without side effects through TDD approach
 ///@dev OpenZeppelin library is used for secure contract development
@@
 \subsubsection{Privacy}
-The Anonymity of an agent in the system is achieved in two ways:
+The anonymity of an agent in the system is achieved in two ways:
 
 \begin{itemize}
-  \item PseudoAnonimity granted by an Ethereum's Externally Owned Accounts (EOA) address that can pseudo-obscure the identity of the agent.
-  \item Private Transactions allowed by AZTEC Protocol security layer via zkAnt. Future developments will allow to leverage on PLONK\cite{PLONK} Proofs to reduce gas costs and improve scalability.
+  \item via pseudo-anonimity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
+  \item via private transactions allowed by AZTEC Protocol security layer via zkAnt.
+Future developments will allow to leverage on PLONK\cite{PLONK}proofs, a universal ZK-SNARK construction, to reduce gas costs and improve scalability.
 \end{itemize}
@@
 An user can send messages from an externally owned account by creating and signing a transaction.
-\newline The limitation of such solution regarding the privacy of the protocol is due to the fact that blockchain and transactions are public so anyone can see the details of a transaction, browsing a block explorer like Etherscan, and also they're subjected to data mining to extract value and identify users in the blockchain.
-\newline To avoid that, AntsReview will implement zkAnt, an Ant token wrapped into AZTEC Protocol, where leveraging on zkSNARKS, and PLONK in the future, will allow private transactions in the system to maintain the privacy and anonimity of Peer-Reviewers.
+The limitation of this type of solution concerning the protocol's privacy is due to the fact that blockchain and transactions are public, therefore the details of transactions are visible to anyone by browsing a block explorer (like Etherscan), and are subjected to data mining that could extract value and identify users in the blockchain.
+\newline To avoid that, Ants-Review will implement zkAnt, an Ant token wrapped into AZTEC Protocol.
+In the future zkAnt could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
 \newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
@@
 \section{Discussions}
+In this session we discuss future developments not yet implemented and implications of AntsReview.
 \subsection{Possible developments}
+An AntReview, issued by an author would be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
+with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
  An AntsReview DAO could be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
@@
 \newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
-This will allow to incentive prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.
+This will allow to incentivise prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank the best Peer-Reviewers.
+
+\subsection{Criticism}
+Some criticism towards giving a monetary reward to reviewers tackle the fact that an extrinsic motivation (such as a token system) might decrease the intrinsic motivation that drives researchers to perform scientific contributions.
+Some experimental studies seem indeed to suggest that reviewers are more interested in reputational forms of recognition \cite{Warne-RewRev}.
+However, we think that engaging the whole community towards the peer-review process and rewarding each actor in it could diminish these effects.
 
 \subsection{A new community-driven standard?}
-A change is already happening in the publishing industry specially with new born publishers are opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
-If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt: how will they justify their added value?\cite{Tennant2017-F1000R}.
-We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, researchers will be the ones seeking the papers to review with a reputation build within community and not journals.
-Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising in this direction.
-Our protocol system is not the only one: other prototypes are proposing an endorsement system for peer-review based on token economics \cite{ScienceMiles,ResearchCoin,Sharples-Kudos,Pevo,I8X}.
-We hope that soon such systems will be running and the value of peer review as 'academic capital' recognized by research funders and hiring committees.
+A change is already happening in the publishing industry, especially with new born publishers opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
+As Tennant points out \cite{Tennant2017-F1000R}, if also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt in order to justify their added value.
+In our proposal we posed two possible integrations for Ants-Review, a simpler one which maintains part of the journals' power in the peer-review evaluation and more complex one that completely decouples the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.
+This second option, which requires further implementations, is the one we aim at.
+Indeed, we foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review with a reputation build within community and not journals.
+Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
+We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.
 
@@
 In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
-We shown how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
+We've shown how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
 We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-reviews.

### 2020-06-12 paper-v1.tex
git

@@
 
-\paragraph{Inclusiveness via gamification.} ll the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
+\paragraph{Inclusiveness via gamification.} All the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform') and reviews evaluation are performed via Quadratic Voting.
 

### 2020-06-12 paper-v1.tex
cleanup by @naszam

--- 2020-06-12 paper-v1.tex
@@
 
-Here we describe the main features of AntsReview.
+Here we describe the main features of Ants-Review.
 \paragraph{Incentivisation and recognition.} A typical business model for open source software (OSS) movement is open-source bounty.
@@
 InterPlanetary File System (IPFS) \cite{IPFS} is a decentralized content-addressable, peer-to-peer protocol which guarantees data immutability and unique file identification.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages into maintaining the privacy of both authors and reviewers in a double-blind approach.
 
-\paragraph{Inclusiveness via gamification.} ll the community is involved in the process of peer-reviewing since there is no selection process ('open participation', 'open interaction', 'open platform');
+\paragraph{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}).
+In this way the pool of reviewer is enriched and allows younger researchers to get the appropriate training through interactive feedback.
+An interesting addition would be to introduce Quadratic Voting (QV) for the reviews' evaluation.
 
-There are two possible scenarios depending if AntsReview integrates an existing journal or if AntsReview becomes a platform completely decoupled from journals.
+There are two possible scenarios depending if Ants-Review integrates an existing journal or if Ants-Review becomes a platform completely decoupled from journals.
 
-\subsubsection{AnstReview process: scenario 1 (journal-dependent)}
+\subsubsection{Ants-Review process: scenario 1 (journal-dependent)}
 
@@
 
-\subsubsection{AnstReview process: scenario 2 (community-driven)}:
+\subsubsection{Ants-Review process: scenario 2 (community-driven)}:
 
 \begin{enumerate}
-\item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform.
+\item The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform.
 \item The paper is accepted by the community for revision in its whatever format.
@@
 \item The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
-\item Reviews fulfilling the smart\-contract requirements are validated by the AntsReview community of contributors.
+\item Reviews fulfilling the smart\-contract requirements are validated by the Ants-Review community of contributors.
 \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.

### 2020-06-12 paper-v1.tex
git QV

@@
 \paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').
+Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').
 
@@
 \paragraph{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}).
-In this way the pool of reviewer is enriched and allows younger researchers to get the appropriate training through interactive feedback.
-An interesting addition would be to introduce Quadratic Voting (QV) for the reviews' evaluation.
+In this way, the pool of reviewer is enriched and allows younger researchers to get the appropriate training through interactive feedback.
+Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, ensuring a virtuous loop of verification.
+\newline An interesting addition would be to introduce Quadratic Voting (QV) \cite{QVWeyl} for the reviews' evaluation.
+QV replaces the discrete concept of one-person-one-vote with the non-linear one of n vote at the cost of n \sqrt{2} and is optimal in the context of multiple choices.
+If we consider scientific outputs as public goods, then the community can vote (with voting tokens) 'how much they care' for a specific peer-review.
+A rank of peer-reviews would result from the voting process, with a more fine-graded distribution that might reflect issues that have a high value to few people and low value to more people.
+\newline Finally, it's conceivable that the members of the community participate to the share of the tokens by voting to the best peer-reviews.
+This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.
 
@@
 
-\subsubsection{Ants-Review process: scenario 1 (journal-dependent)}
-
 \begin{enumerate}
-    \item The author submits a manuscript to the journal.
-    \item If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope)
-    \item The editor issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
-    \item The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
-    \item Reviews fulfilling the smart-contract requirements are validated by the journal editors.
-    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
-    \item Not all reviews will have the same quality and depth.
-However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript.
-In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the members of the community via Quadratic Voting to rank the best peer-reviews.
+    \item \textbf{Ants-Review process: scenario 1 (journal-dependent)}: 1.
+The author submits a manuscript to the journal.
+2.
+If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope).
+3.
+The editor issues a bounty (\emph{bounty issuance}) for the paper review.
+Fulfillment rules are set in a smart-contract.
+4.
+The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
+5.
+Reviews fulfilling the smart-contract requirements are validated by the journal editors.
+6.
+When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANT}.
+    \item \textbf{Ants-Review process: scenario 2 (community-driven)}:
 
 \end{enumerate}
-
-\subsubsection{Ants-Review process: scenario 2 (community-driven)}:
 

### 2020-06-12 paper-v1.tex
abstract, last references

@@
 \begin{abstract}
-Peer-review is a necessary and essential quality control step for scientific publications.
-However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher.
-Therefore, scientific dissemination is affected.
-Here, to solve this issue, we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system.
-We designed a Protocol of smart contracts called Ants-Review that allows any author to issue a call for peer-reviewing their scientific publication.
-If requirements are met, peer-reviews will be accepted and payed by the Issuer.
-To promote ethical behaviour the system will implement an incentive mechanism on Ants-Review.
-\keywords{Blockchain  \and Open Science \and Privacy \and Peer-review \and Incentivization.}
+Peer-review is a necessary and essential quality control step for scientific publications but lacks proper  incentives.
+Indeed, the process, which is very costly in terms of time and intellectual investment, not only is not remunerated by the journals but it is also not openly recognized by the academic community as a relevant scientific output for a researcher.
+Therefore, scientific dissemination is affected in the timeliness, quality and fairness.
+Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up a reputational metric.
+We designed a protocol of smart contracts called Ants-Review that allows authors or editors to issue a bounty call for peer-reviewing pseudo-anonymously but in an open report a scientific manuscript.
+If requirements are met, peer-reviews will be accepted and payed by the Issuer proportionally to their quality and  constructiveness, judged by the editor or the community via Quadratic Voting (QV).
+To promote ethical behaviour and inclusiveness the system could implement a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.
+\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
 \end{abstract}
@@
 \paragraph{Incentivisation and recognition.} A typical business model for open source software (OSS) movement is open-source bounty.
-Bounties are a prize or monetary reward given for completing a task before a deadline.
+Bounties are a prize or monetary reward given for completing a task before a deadline \cite{BountyGit}.
 Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are Gitcoin \cite{Gitcoin} and The Bounties Network \cite{Bounty}.
@@
 \paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').
+Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare \cite{ResSqu} and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').
 
@@
 \newline An interesting addition would be to introduce Quadratic Voting (QV) \cite{QVWeyl} for the reviews' evaluation.
-QV replaces the discrete concept of one-person-one-vote with the non-linear one of n vote at the cost of n \sqrt{2} and is optimal in the context of multiple choices.
+QV replaces the discrete concept of one-person-one-vote with the non-linear one of n vote at the cost of $n^2$ and is optimal in the context of multiple choices.
 If we consider scientific outputs as public goods, then the community can vote (with voting tokens) 'how much they care' for a specific peer-review.
@@
 \begin{enumerate}
-    \item \textbf{Ants-Review process: scenario 1 (journal-dependent)}: 1.
-The author submits a manuscript to the journal.
-2.
+    \item \textbf{Ants-Review process - scenario 1 (journal-dependent)}: The author submits a manuscript to the journal.
 If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope).
-3.
 The editor issues a bounty (\emph{bounty issuance}) for the paper review.
 Fulfillment rules are set in a smart-contract.
-4.
 The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
-5.
-Reviews fulfilling the smart-contract requirements are validated by the journal editors.
-6.
+Reviews fulfilling the smart-contract requirements are validated by the journal editors and voted via QV.
 When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANT}.
-    \item \textbf{Ants-Review process: scenario 2 (community-driven)}:
-
-\end{enumerate}
-
-\begin{enumerate}
-\item The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform.
-\item The paper is accepted by the community for revision in its whatever format.
-\item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
-\item The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
-\item Reviews fulfilling the smart\-contract requirements are validated by the Ants-Review community of contributors.
-\item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
-\item Reviews will be voted by the community via Quadratic Voting.
-\item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
+    \item \textbf{Ants-Review process - scenario 2 (community-driven)}: The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform.
+The paper is accepted by the community for revision in its whatever format.
+The author issues a bounty (\emph{bounty issuance}) for the paper review.
+Fulfillment rules are set in a smart-contract.
+The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
+Reviews fulfilling the smart-contract requirements are validated by the Ants-Review community of contributors.
+When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
+Reviews will be voted by the community via Quadratic Voting.In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
 Since it is in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit and therefore will fuel ethical behaviour.
@@
 Some criticism towards giving a monetary reward to reviewers tackle the fact that an extrinsic motivation (such as a token system) might decrease the intrinsic motivation that drives researchers to perform scientific contributions.
-Some experimental studies seem indeed to suggest that reviewers are more interested in reputational forms of recognition \cite{Warne-RewRev}.
-However, we think that engaging the whole community towards the peer-review process and rewarding each actor in it could diminish these effects.
+Some experimental studies seem indeed to suggest that reviewers are more interested in reputational forms of recognition \cite{Warne-RewRev,ZahIncent} and that material compensation affects the quality of reviews by 'undermining the moral motives that guide referees' behaviour \cite{SquazzIncent}.
+However, we think that engaging the whole community towards the peer-review process and rewarding each actor in it through gamified forms of reward and alternative voting systems could diminish these effects, but this is a speculation that needs to be experimentally tested.
 
 \subsection{A new community-driven standard?}
-A change is already happening in the publishing industry, especially with new born publishers opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
-As Tennant points out \cite{Tennant2017-F1000R}, if also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt in order to justify their added value.
+As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
+If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt in order to justify their added value.
 In our proposal we posed two possible integrations for Ants-Review, a simpler one which maintains part of the journals' power in the peer-review evaluation and more complex one that completely decouples the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.
@@
 \bibliographystyle{splncs04}
-\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-relatedwork.bib, ref3-system.bib,ref4-discuss.bib}
+\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-relatedwork.bib, ref3-system.bib,ref4-discuss.bib, ref5-extra.bib}
 

### 2020-07-10 paper-v1.tex
update erc20 token name and symbol by @naszam

@@
 AntsReview integrates few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline Ant, is the primary protocol token and can be staked into an AntReview.
-\newline Ant [see \ref{lst:code}] is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ant} and symbol \emph{ANT}.
+\newline ANTS, is the primary protocol token and can be staked into an AntReview.
+\newline ANTS [see \ref{lst:code}] is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
 
-\begin{lstlisting}[caption={Ant.sol},label={lst:code},language=Solidity]
+\begin{lstlisting}[caption={ANTS.sol},label={lst:code},language=Solidity]
 /// SPDX-License-Identifier: GPL-3.0
@@
 ///@author Nazzareno Massari
-///@notice Ant ERC20 Token
+///@notice ANTS ERC20 Token
 ///@dev All function calls are currently implemented without side effects through TDD approach
@@
 
+import "@openzeppelin/contracts/access/Ownable.sol";
 import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
 
-contract Ant is ERC20PresetMinterPauser {
+contract ANTS is Ownable, ERC20PresetMinterPauser {
 
   constructor()
-  ERC20PresetMinterPauser("Ant", "ANT")
+  ERC20PresetMinterPauser("Ants-Review", "ANTS")
   public {
@@
   \item via pseudo-anonimity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
-  \item via private transactions allowed by AZTEC Protocol security layer via zkAnt.
+  \item via private transactions allowed by AZTEC Protocol security layer via zkANTS.
 Future developments will allow to leverage on PLONK\cite{PLONK}proofs, a universal ZK-SNARK construction, to reduce gas costs and improve scalability.
@@
 The limitation of this type of solution concerning the protocol's privacy is due to the fact that blockchain and transactions are public, therefore the details of transactions are visible to anyone by browsing a block explorer (like Etherscan), and are subjected to data mining that could extract value and identify users in the blockchain.
-\newline To avoid that, Ants-Review will implement zkAnt, an Ant token wrapped into AZTEC Protocol.
-In the future zkAnt could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
+\newline To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol.
+In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
 \newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
@@
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
- An AntsReview DAO could be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
+ An AntsReview DAO could be formed in the future to allow ANTS stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
 \newline Hive. When Anters make a deposit into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
 \newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Ant and Chai, an ERC20 token that accrues interest from MakerDAO's DSR or Compound, with name \emph{Hive} and symbol \emph{HIVE}
-\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to promote anonymity and sent between the peer-reviewers that fulfilled the AntReview.
-\newline zkAnt, is an Ant token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkAnt will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline Hive will be implemented using a similar approach to Chai, an ERC20 token that accrues interest from MakerDAO's DSR or Compound, with name \emph{Hive} and symbol \emph{HIVE}
+\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for ANTS and wrapped into zkANTS to promote anonymity and sent between the peer-reviewers that fulfilled the AntReview.
+\newline zkANTS, is an Ants-Review token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkANTS will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ants-Review Token into zkANTS, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
 \newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.

### 2020-07-10 paper-v1.tex
cleanup by @naszam

@@
 ///@author Nazzareno Massari
-///@notice ANTS ERC20 Token
+///@notice Ants-Review ERC20 Token
 ///@dev All function calls are currently implemented without side effects through TDD approach

### 2020-07-23 paper-v1.tex
remove listing 1.1

--- 2020-07-10 paper-v1.tex
@@
 \graphicspath{ {./img/} }
-
-\input{solidity-highlighting.tex}
 
@@
 \newline ANTS, is the primary protocol token and can be staked into an AntReview.
-\newline ANTS [see \ref{lst:code}] is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-
-\begin{lstlisting}[caption={ANTS.sol},label={lst:code},language=Solidity]
-/// SPDX-License-Identifier: GPL-3.0
-pragma solidity 0.6.8;
-
-///@title Ants-Review
-///@author Nazzareno Massari
-///@notice ANTS ERC20 Token
-///@dev All function calls are currently implemented without side effects through TDD approach
-///@dev OpenZeppelin library is used for secure contract development
-
-import "@openzeppelin/contracts/access/Ownable.sol";
-import "@openzeppelin/contracts/presets/ERC20PresetMinterPauser.sol";
-
-contract ANTS is Ownable, ERC20PresetMinterPauser {
-
-  constructor()
-  ERC20PresetMinterPauser("Ants-Review", "ANTS")
-  public {
-
-  }
-
-}
-\end{lstlisting}
+\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
 

### 2020-07-23 paper-v1.tex
fix typo Ether

@@
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
-  \item to send the amount of ether for the reward.
+  \item to send the amount of Ether for the reward.
 \end{itemize}
@@
 In this way, only the Issuer can create a new AntReview.
-\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.When the AntReview is accepted by the Issuer, the bounty is paid among Peer-Reviewers.On top of that, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
+\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.When the AntReview is accepted by the Issuer, the bounty is paid among Peer-Reviewers.On top of that, the Issuer can cancel the AntReview at any time and withdraw the amount of Ether staked.
 \newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W.
@@
 \subsection{Possible developments}
-An AntReview, issued by an author would be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
+An AntReview, issued by an author would be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake Ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.

### 2020-07-23 paper-v1.tex
fix figure 1 ref

@@
 In the following sections we describe the architecture of the system and its building blocks.
-\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:
+\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart (See Figure \ref{fig:contracts}):
 

### 2020-07-23 paper-v1.tex
fix see implementation with ref

@@
 Thus, the system acts also as a reputation builder.
-\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews exchange to the same manuscript can have their tokens accrue interest over time (see Implementation).
+\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews exchange to the same manuscript can have their tokens accrue interest over time (see 3.2).
 

### 2020-07-23 paper-v1.tex
fix redundant meets
fix token symbol typo

@@
 The traditional peer-review process is completely controlled by the editor(s).
-The author(s) submit manuscript to the journal where an editorial team assesses if the paper meets meets the scopes of the journal and novelty criteria.
+The author(s) submit manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
 If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
@@
 Reviews fulfilling the smart-contract requirements are validated by the journal editors and voted via QV.
-When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANT}.
+When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANTS}.
     \item \textbf{Ants-Review process - scenario 2 (community-driven)}: The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform.
@@
 Reviews fulfilling the smart-contract requirements are validated by the Ants-Review community of contributors.
-When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
+When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANTS}.
 Reviews will be voted by the community via Quadratic Voting.In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.

### 2020-07-24 paper-v1.tex
add fig. 1 description

@@
 \label{fig:contracts}
+\medskip
+\small
+(\textbf{AntReview}) is the core of the protocol, it implements a bounty system with the functions listed.
+(\textbf{AntsReviewRoles}) is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
+(\textbf{ANTS}) is the native token used in the protocol that inherit the ERC20PresetMinterPauser library from OpenZeppelin, is linked to AntsReview and to Aztec Protocol to be wrapped into zkANTS to implement private transactions on Ethereum.
+(\textbf{IPFS}) represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as proof of existence into AntsReview.
+(\textbf{De-Fi}) represent the integration with De-Fi services like Dai and Chai, to be used as token in the protocol.
+(\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.
 \end{figure}

### 2020-07-24 paper-v1.tex
fix fig. 1 description

--- 2020-07-23 paper-v1.tex
@@
 \label{fig:contracts}
+\medskip
+\small
+(\textbf{AntsReview}) is the core of the protocol, it implements a bounty system with the functions listed.
+\newline (\textbf{AntsReviewRoles}) is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
+\newline (\textbf{ANTS}) is the native token used in the protocol that inherit the ERC20PresetMinterPauser library from OpenZeppelin, is linked to AntsReview and to Aztec Protocol to be wrapped into zkANTS to implement private transactions on Ethereum.
+\newline (\textbf{IPFS}) represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as proof of existence into AntsReview.
+\newline (\textbf{De-Fi}) represent the integration with De-Fi services like Dai and Chai, to be used as token in the protocol.
+(\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.
 \end{figure}

### 2020-07-24 paper-v1.tex
update fig. 1 description

--- 2020-07-23 paper-v1.tex
@@
 \label{fig:contracts}
+\medskip
+\small
+\textbf{AntsReview} is the core of the protocol, it implements a bounty system with the functions listed.
+\textbf{AntsReviewRoles} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
+\textbf{ANTS} is the native token used in the protocol that inherit the ERC20PresetMinterPauser library from OpenZeppelin, is linked to AntsReview and to Aztec Protocol to be wrapped into zkANTS to implement private transactions on Ethereum.
+\textbf{IPFS} represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as proof of existence into AntsReview.
+\textbf{De-Fi} represent the integration with De-Fi services like Dai and Chai, to be used as token in the protocol.
+(\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.
 \end{figure}

### 2020-07-24 paper-v1.tex
update fig. 1 description

@@
 \textbf{AntsReviewRoles} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
-\textbf{ANTS} is the native token used in the protocol that inherit the ERC20PresetMinterPauser library from OpenZeppelin, is linked to AntsReview and to Aztec Protocol to be wrapped into zkANTS to implement private transactions on Ethereum.
-\textbf{IPFS} represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as proof of existence into AntsReview.
-\textbf{De-Fi} represent the integration with De-Fi services like Dai and Chai, to be used as token in the protocol.
+\textbf{ANTS} is the native token used in the protocol that inherits the \textbf{ERC20PresetMinterPauser} library from OpenZeppelin, it is linked to AntsReview and to Aztec Protocol to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{IPFS} represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
+\textbf{De-Fi} represent the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as token in the protocol.
 (\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.

### 2020-07-24 paper-v1.tex
update fig. 1 description

--- 2020-07-24 paper-v1.tex
@@
 \small
-\textbf{AntsReview} is the core of the protocol, it implements a bounty system with the functions listed.
+\textbf{AntsReview} is the core contract of the protocol, it implements a bounty system with the functions listed.
 \textbf{AntsReviewRoles} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
-\textbf{ANTS} is the native token used in the protocol that inherit the ERC20PresetMinterPauser library from OpenZeppelin, is linked to AntsReview and to Aztec Protocol to be wrapped into zkANTS to implement private transactions on Ethereum.
-\textbf{IPFS} represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as proof of existence into AntsReview.
-\textbf{De-Fi} represent the integration with De-Fi services like Dai and Chai, to be used as token in the protocol.
+\textbf{ANTS} is the native token used in the protocol that inherits the \textbf{ERC20PresetMinterPauser} contract from OpenZeppelin, it is linked to AntsReview and to AZTEC Protocol to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{IPFS} represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
+\textbf{De-Fi} represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as token in the protocol.
 (\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.

### 2020-07-24 paper-v1.tex
update fig. 1 description

@@
 \textbf{AntsReviewRoles} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
-\textbf{ANTS} is the native token used in the protocol that inherits the \textbf{ERC20PresetMinterPauser} contract from OpenZeppelin, it is linked to AntsReview and to AZTEC Protocol to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{ANTS} is the native token used in the protocol that inherits the \textbf{ERC20PresetMinterPauser} contract from OpenZeppelin.
+It's linked to AntsReview and to AZTEC Protocol to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
 \textbf{IPFS} represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
-\textbf{De-Fi} represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as token in the protocol.
-(\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.
+\textbf{De-Fi} represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
+\textbf{OpenZeppelin} is the library used by the protocol for secure contract development, with the modules listed.
 \end{figure}

### 2020-07-25 paper-v1.tex
update fig. 1 description

--- 2020-07-24 paper-v1.tex
@@
 \includegraphics[scale=0.28]{AntsReview}
-\caption{Ants-Review Smart Contracts}
+\caption{\textbf{a}is the core contract of the protocol, it implements a bounty system with the functions listed.
+\textbf{b} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
+\textbf{c} is the native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin.
+It's linked to \textbf{a} and to \textbf{e}, to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{f} represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
+\textbf{g} represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
+\textbf{h} is the library used by the protocol for secure contract development, with the modules listed.}
 \label{fig:contracts}
-\medskip
-\small
-\textbf{AntsReview} is the core of the protocol, it implements a bounty system with the functions listed.
-\textbf{AntsReviewRoles} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
-\textbf{ANTS} is the native token used in the protocol that inherits the \textbf{ERC20PresetMinterPauser} library from OpenZeppelin, it is linked to AntsReview and to Aztec Protocol to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
-\textbf{IPFS} represent the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
-\textbf{De-Fi} represent the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as token in the protocol.
-(\textbf{OpenZeppelin}) is the library used by the protocol for secure contract development, with the modules listed.
 \end{figure}

### 2020-07-25 paper-v1.tex
clean up
fix fig. 1 description

@@
 \includegraphics[scale=0.28]{AntsReview}
-\caption{\textbf{a}is the core contract of the protocol, it implements a bounty system with the functions listed.
-\textbf{b} is the module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
-\textbf{c} is the native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin.
+\caption{\textbf{a} The core contract of the protocol, it implements a bounty system with the functions listed.
+\textbf{b} The module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
+\textbf{c} The native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin.
 It's linked to \textbf{a} and to \textbf{e}, to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
-\textbf{f} represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
-\textbf{g} represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
-\textbf{h} is the library used by the protocol for secure contract development, with the modules listed.}
+\textbf{f} Represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
+\textbf{g} Represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
+\textbf{h} The library used by the protocol for secure contract development, with the modules listed.}
 \label{fig:contracts}

### 2020-07-25 paper-v1.tex
alice and bob

@@
 \subsubsection{AntsReview}
-AntsReview is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
-\newline It implements a bounty-like system (AntReview) where an issuer (author or editor) is asked a series of actions to ensure transparency and consistency for the AntReview that he/she is creating:
+AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
+\newline It implements a bounty-like system (AntReview) where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
 \begin{itemize}
-  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}.
+  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
-  \item to send the amount of Ether for the reward.
+  \item to specify the amount of Ether for the reward, to be stored in the contract balance.
 \end{itemize}
+
+\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
+\newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
 
@@
 In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
-\newline Ants-Review exploits the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
+\newline Ants-Review is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
 \newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.

### 2020-07-25 paper-v1.tex
clean up

@@
 AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
-\newline It implements a bounty-like system (AntReview) where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
+\newline It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
 \begin{itemize}

### 2020-07-25 paper-v1.tex
fix AntsReview implementation

@@
 \begin{itemize}
-  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
+  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
@@
 \newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
+\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
 

### 2020-07-25 paper-v1.tex
clean up

@@
 \newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
-\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
+\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
 

### 2020-07-25 paper-v1.tex
clean up

@@
 
-\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
+\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
 \newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
@@
 In this way, only the Issuer can create a new AntReview.
-\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.When the AntReview is accepted by the Issuer, the bounty is paid among Peer-Reviewers.On top of that, the Issuer can cancel the AntReview at any time and withdraw the amount of Ether staked.
 \newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W.

### 2020-07-25 paper-v1.tex
clean up

@@
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
-  \item to specify the amount of Ether for the reward, to be stored in the contract balance.
+  \item to specify the amount of Ether for the reward, to be trasfered from Alice to the contract.
 \end{itemize}
@@
 In order to verify if a specific hash is included into a Merkle Tree by leveraging on \emph{MerkleProof.sol} (OpenZeppelin Library), we need to provide a proof, generated from the leaf of interest, that represents the ramification derived from the leaf, the root hash and, finally, the leaf we want to verify.
-\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity.
+\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using \emph{keccak256}, a cryptographic hashing algorithm available in Solidity.
 

### 2020-07-25 paper-v1.tex
clean up eoa length of key
add zkANTS to tokenomics
fix aztect 2.0

@@
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
+\newline zkANTS, is an Ants-Review token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
+\newline zkANTS will be implemented via AZTEC Protocol 2.0 (not yet released) that will allow to securely wrap the Ants-Review Token into zkANTS, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
 
@@
 
- Externally Owned Accounts (EOA) in Ethereum are controlled by private keys, are 20 bytes long and have no code.
+ Externally Owned Accounts (EOA) in Ethereum are controlled by private key.
 An user can send messages from an externally owned account by creating and signing a transaction.
@@
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for ANTS and wrapped into zkANTS to promote anonymity and sent between the peer-reviewers that fulfilled the AntReview.
-\newline zkANTS, is an Ants-Review token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkANTS will be implemented via AZTEC 2.0 (still in development) that will allow to securely wrap the Ants-Review Token into zkANTS, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
 \newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.

### 2020-07-25 paper-v1.tex
blockchain for science (inverted order), removed redundant paragraph in design section

@@
 Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.
+Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
+Those are: \emph{decentralization}, for which there are no trusted third parties; \emph{cryptographic hashing} and \emph{timestamping}, that create a digital footprint able to keep a traceable chronological record of research objects; \emph{immutability} or \emph{append-only}, for which data cannot be altered or retrieved.
 In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
-Finally, scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing and timestamping, that create a digital footprint able to keep a traceable chronological record of research objects; immutability or append-only, for which data cannot be altered or retrieved) set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
 \newline A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
@@
 
-\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community ('open report' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare \cite{ResSqu} and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable ('cascading' or 'portable peer-reviews').
+\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare \cite{ResSqu} and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
 
@@
 This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.
-
-There are two possible scenarios depending if Ants-Review integrates an existing journal or if Ants-Review becomes a platform completely decoupled from journals.
-
-\begin{enumerate}
-    \item \textbf{Ants-Review process - scenario 1 (journal-dependent)}: The author submits a manuscript to the journal.
-If the papers passes the stages of editorial decision (appropriateness of style and coherence with the journal's scope).
-The editor issues a bounty (\emph{bounty issuance}) for the paper review.
-Fulfillment rules are set in a smart-contract.
-The bounty prize could correspond to part of the article submission fees and article publication fees requested to the authors by the journal.
-Reviews fulfilling the smart-contract requirements are validated by the journal editors and voted via QV.
-When the reviews are accepted (\emph{bounty fulfillment}), reviewers are awarded a token called \emph{ANTS}.
-    \item \textbf{Ants-Review process - scenario 2 (community-driven)}: The author submits a manuscript to the pre-print service or to an hypothetical Ants-Review platform.
-The paper is accepted by the community for revision in its whatever format.
-The author issues a bounty (\emph{bounty issuance}) for the paper review.
-Fulfillment rules are set in a smart-contract.
-The bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
-Reviews fulfilling the smart-contract requirements are validated by the Ants-Review community of contributors.
-When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANTS}.
-Reviews will be voted by the community via Quadratic Voting.In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty.
-Since it is in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit and therefore will fuel ethical behaviour.
-
-\end{enumerate}
 

### 2020-07-25 paper-v1.tex
edit tokenomics

--- 2020-07-25 paper-v1.tex
@@
 AntsReview integrates few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS, is the primary protocol token and can be staked into an AntReview.
+\newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS, is an Ants-Review token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkANTS will be implemented via AZTEC Protocol 2.0 (not yet released) that will allow to securely wrap the Ants-Review Token into zkANTS, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline zkANTS, is a wrapper of ANTS that will be used inside the protocol to allow private transactions on mainnet among the agents, preserving their anonimity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
+\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote{\url{https://github.com/ethereum/EIPs/issues/1724}} will be used as template to build an AZTEC-compatible asset.
+\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions on mainnet.
 
@@
 \subsection{Possible developments}
-An AntReview, issued by an author would be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake Ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
+An AntReview, issued by an author would be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.

### 2020-07-25 paper-v1.tex
Updates from Overleaf

--- 2020-07-25 paper-v1.tex
@@
 Section 3 explains the proposed protocol on the Ethereum blockchain illustrating the system architecture and the current status of implementation.
-In Sect.
-4 we discuss the implication of our work.
+In Section 4 we discuss the implication of our work.
 Section 5 contains the conclusions.
@@
 \subsection{Related work} Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
-\newline It's also worth mentioning \emph{Publons}\cite{Publons}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage} of Science\cite{Peerage} and \emph{ResearchSquare}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
+\newline It's also worth mentioning \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
 Spearpoint\cite{ResearchCoin} proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees.
@@
 Bounties are a prize or monetary reward given for completing a task before a deadline \cite{BountyGit}.
-Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are Gitcoin \cite{Gitcoin} and The Bounties Network \cite{Bounty}.
+Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[3]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[4]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
 Incentives can be cryptographic tokens, unit of values registered on a blockchain network and that represent the quantity and quality of a service within a network.
@@
 \paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the Neuroscience Peer Review Consortium \cite{NeuroPeerCons} and independent companies like ResearchSquare \cite{ResSqu} and Peerage of Science \cite{Peerage}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
+Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[5]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
 
@@
 \subsubsection{AntsReview}
-AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet \cite{Rinkeby}.
+AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io/en/v0.6.8.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{}.\textsc{URL:}https://solidity.readthedocs.io/en/v0.6.8.}.
 \newline It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:

### 2020-07-25 paper-v1.tex
FOOTNOTES: all the websites URLs removed from references and turned into footnotes.

--- 2020-07-25 paper-v1.tex
@@
 \subsubsection{AntsReview}
-AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io/en/v0.6.8.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{}.\textsc{URL:}https://solidity.readthedocs.io/en/v0.6.8.}.
+AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
 \newline It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
@@
 
-AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library \cite{OZ}, through the creation of the Issuer and Peer-Reviewer Roles.
+AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
 \newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts.
@@
 \subsubsection{Tokenomics}
-AntsReview integrates few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS, is the primary protocol token and can be staked into an AntReview.
+AntsReview integrates ERC20 tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+\newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS, is an Ants-Review token wrapped into AZTEC Protocol \cite{AZTEC} ZK-SNARKs, that will be extended to PLONK \cite{PLONK} Proof to collapse the gas costs of private transactions on mainnet.
-\newline zkANTS will be implemented via AZTEC Protocol 2.0 (not yet released) that will allow to securely wrap the Ants-Review Token into zkANTS, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
+\newline zkANTS, is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
+\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[9]{\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
+\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
 
@@
 \begin{itemize}
-  \item via pseudo-anonimity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
+  \item via pseudo-anonymity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
   \item via private transactions allowed by AZTEC Protocol security layer via zkANTS.
@@
 \subsection{Possible developments}
-An AntReview, issued by an author would be seen as a poll, a container where Anters (members of the Ants-Review Community) can stake Ether or ERC20 tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ...
-with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate) \cite{DSR} or Compound \cite{Compound} to cite a few.
+An AntReview, issued by an author would be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[10]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[11]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...
+with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate)\footnote[12]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[13]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
  An AntsReview DAO could be formed in the future to allow ANTS stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
@@
 \newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for ANTS and wrapped into zkANTS to promote anonymity and sent between the peer-reviewers that fulfilled the AntReview.
-\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by Gitcoin \cite{Gitcoin} to match donations for Grants.
+\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by \emph{Gitcoin} to match donations for grants.
 This will allow to incentivise prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank the best Peer-Reviewers.

### 2020-07-26 paper-v1.tex
Integrated corrections by Evan in background/design/discussion, fixed references, added comments on the implementation part.  Removed §4.2 regarding criticism on rewarding scientists (it was not essential for the purpose of the paper and we gained some space). If reviewers ask it back, it can go into a footnote.

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{Bitcoin}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
 Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.
@@
 Those are: \emph{decentralization}, for which there are no trusted third parties; \emph{cryptographic hashing} and \emph{timestamping}, that create a digital footprint able to keep a traceable chronological record of research objects; \emph{immutability} or \emph{append-only}, for which data cannot be altered or retrieved.
-In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
+In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
 \newline A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
@@
 Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft.
-If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
-The same reviewers might be contacted again and if they want they can follow up the peer-review process.
+Depending on the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
+The same reviewers might be contacted again to continue the same peer-review process.
 This process can take multiple rounds and is a huge time investment both for authors and reviewers.
@@
 Researchers are motivated in doing peer-review for a sense of belonging and a desire to 'give back' to the community.
-A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science being published through sloppy and uncritical reviews.
+A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science be published through sloppy and uncritical reviews.
 \paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
@@
 
-\subsection{Related work} Some mild attempts to credit peer review has been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
+\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
 \newline It's also worth mentioning \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
@@
 
-\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to righteously attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
+\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
@@
 \paragraph{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}).
-In this way, the pool of reviewer is enriched and allows younger researchers to get the appropriate training through interactive feedback.
-Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, ensuring a virtuous loop of verification.
+In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback.
+Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification.
 \newline An interesting addition would be to introduce Quadratic Voting (QV) \cite{QVWeyl} for the reviews' evaluation.
@@
 \subsubsection{AntsReview}
-AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine (EVM), deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
-\newline It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
+AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
 \begin{itemize}
@@
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
-  \item to specify the amount of Ether for the reward, to be trasfered from Alice to the contract.
+  \item to specify the amount of Ether for the reward that will be transfered from Alice to the contract.
 \end{itemize}
 
-\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
+\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
 \newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
@@
 AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
-\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts.
+\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
 In this way, only the Issuer can create a new AntReview.
-\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W.
-Scott Stornetta \cite{TimeStamp-Haber}.
-Pioneers of the blockchain, cited by the Bitcoin whitepaper\cite{Bitcoin}, they were on a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application.
+\newline One of the key aspects of the protocol is the concept of Proof of Existence.
 In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
@@
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Zero-Knowledge \cite{ZeroKnoledge} proof is a mathematical cryptographic method that through value permutations allow one party (the prover) to prove to another (the verifier) the validity of a statement, without revealing the statement itself.
 \newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
-This will enable to run smart contracts at scale with quasi-instant transactions while still being secured by Ethereum.
+This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.
 
@@
 
-\subsection{Criticism}
-Some criticism towards giving a monetary reward to reviewers tackle the fact that an extrinsic motivation (such as a token system) might decrease the intrinsic motivation that drives researchers to perform scientific contributions.
-Some experimental studies seem indeed to suggest that reviewers are more interested in reputational forms of recognition \cite{Warne-RewRev,ZahIncent} and that material compensation affects the quality of reviews by 'undermining the moral motives that guide referees' behaviour \cite{SquazzIncent}.
-However, we think that engaging the whole community towards the peer-review process and rewarding each actor in it through gamified forms of reward and alternative voting systems could diminish these effects, but this is a speculation that needs to be experimentally tested.
-
 \subsection{A new community-driven standard?}
 As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
-If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt in order to justify their added value.
+If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value.
 In our proposal we posed two possible integrations for Ants-Review, a simpler one which maintains part of the journals' power in the peer-review evaluation and more complex one that completely decouples the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi and Keno Budde for useful comments and discussions and Marcelo Colmenero for the Pixel Art.
+\subsubsection{Acknowledgements} We would like to thank Matteo A.
+Tambussi and Keno Budde for useful comments and discussions; Evan C.
+Harris for internal review; Marcelo Colmenero for the pixel art in Figure 1.
 

### 2020-07-26 paper-v1.tex
Updates from Overleaf

@@
 \item \emph{AntsReview}, which manages access management and the core system.
-\item \emph{Tokenomics}, which manages the incentivization mechanism of the system.
+\item \emph{Tokenomics}, which manages the incentive mechanism of the system.
 \item \emph{Privacy}, which maintains the pseudo-anonymity of the system via AZTEC Protocol.
@@
 AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
-It implements a bounty-like system where Alice (issuer, author or editor) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
+It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
 \begin{itemize}
@@
 
-\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
-\newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
-\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
+Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
+Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
+If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
 

### 2020-07-26 paper-v1.tex
integrated corrections by @eharris128

@@
 AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
-It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where is asked a series of actions to ensure transparency and consistency for the AntReview that she is creating:
+It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
 \begin{itemize}
@@
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
-  \item to specify the amount of Ether for the reward that will be transfered from Alice to the contract.
+  \item to specify the amount of Ether for the reward that will be transferred from Alice to the contract.
 \end{itemize}
 
-Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
-Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
-If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.
+Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
+Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
+If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by sepcifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
 
-AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts}\textbf{b}).
+It's implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
 \newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 \subsubsection{Tokenomics}
-AntsReview integrates ERC20 tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+AntsReview integrates a few ERC20 tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
@@
 
- Externally Owned Accounts (EOA) in Ethereum are controlled by private key.
+EOA in Ethereum are controlled by private key.
 An user can send messages from an externally owned account by creating and signing a transaction.
@@
 As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
-If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value.
+If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value.
 In our proposal we posed two possible integrations for Ants-Review, a simpler one which maintains part of the journals' power in the peer-review evaluation and more complex one that completely decouples the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.

### 2020-07-26 paper-v1.tex
integrated corrections by @biancasama

@@
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
-InterPlanetary File System (IPFS) \cite{IPFS} is a decentralized content-addressable, peer-to-peer protocol which guarantees data immutability and unique file identification.
+InterPlanetary File System (IPFS) \cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes.
 \newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages into maintaining the privacy of both authors and reviewers in a double-blind approach.
@@
 \subsubsection{AntsReview}
-AntsReview (See Figure \ref{fig:contracts}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+AntsReview (See Figure \ref{fig:contracts}\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
 It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
 \begin{itemize}
-  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet, and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
+  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS} and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
   \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
@@
 \subsubsection{Tokenomics}
-AntsReview integrates a few ERC20 tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+AntsReview integrates a few \emph{ERC20}\footnote[8]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
@@
 \newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[9]{\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[9]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
 \newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
@@
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
+\newline Future developments will investigate viable solutions, for scaling the system, like \emph{ZK$^2$-Rollups}\footnote[10]{\emph{ZK-Rollups}.\textsc{URL:}\url{https://medium.com/aztec-protocol/aztec-fast-privacy-with-zk%C2%B2-rollup-7c742f45457}.} by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
 This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.

### 2020-07-26 paper-v1.tex
fix

@@
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Future developments will investigate viable solutions, for scaling the system, like \emph{ZK$^2$-Rollups}\footnote[10]{\emph{ZK-Rollups}.\textsc{URL:}\url{https://medium.com/aztec-protocol/aztec-fast-privacy-with-zk%C2%B2-rollup-7c742f45457}.} by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
+\newline Future developments will investigate viable solutions, for scaling the system, like \emph{ZK-Rollups}\footnote[10]{\emph{ZK-Rollups}.\textsc{URL:}\url{https://medium.com/aztec-protocol/aztec-fast-privacy-with-zk%C2%B2-rollup-7c742f45457}.} by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
 This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.

### 2020-07-26 paper-v1.tex
Updates from Overleaf

@@
 \subsubsection{Tokenomics}
-AntsReview integrates a few \emph{ERC20}\footnote[8]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
@@
 \newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[9]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
 \newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
@@
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Future developments will investigate viable solutions, for scaling the system, like \emph{ZK-Rollups}\footnote[10]{\emph{ZK-Rollups}.\textsc{URL:}\url{https://medium.com/aztec-protocol/aztec-fast-privacy-with-zk%C2%B2-rollup-7c742f45457}.} by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
+\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
 This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.
@@
 \subsection{Possible developments}
-An AntReview, issued by an author would be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[10]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[11]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...
-with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate)\footnote[12]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[13]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+An AntReview, issued by an author would be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[11]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[12]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...
+with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate)\footnote[13]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[14]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
  An AntsReview DAO could be formed in the future to allow ANTS stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.

### 2020-07-26 paper-v1.tex
clean up

@@
 \newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Future developments will investigate viable solutions, for scaling the system, like ZK-Rollups by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
+\newline Future developments will investigate viable solutions, for scaling the system, like ZK-ZK Rollup by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
 This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.

### 2020-07-26 paper-v1.tex
add ref fig. 1 letters

@@
 \begin{itemize}
-\item \emph{AntsReview}, which manages access management and the core system.
-\item \emph{Tokenomics}, which manages the incentive mechanism of the system.
-\item \emph{Privacy}, which maintains the pseudo-anonymity of the system via AZTEC Protocol.
+\item \emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
+\item \emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
+\item \emph{Privacy}, which maintains the pseudo-anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).
 \end{itemize}
@@
 \subsubsection{AntsReview}
-AntsReview (See Figure \ref{fig:contracts}\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+AntsReview (See Figure \ref{fig:contracts} \textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
 It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
@@
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts}\textbf{b}).
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts} \textbf{b}).
 It's implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
@@
 AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS, is the primary protocol ERC20 token and can be staked into an AntReview.
+\newline ANTS (See Figure \ref{fig:contracts}\textbf{c}), is the primary protocol ERC20 token and can be staked into an AntReview.
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS, is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
+\newline zkANTS (See Figure \ref{fig:contracts} \textbf{d}), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
 \newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.

### 2020-07-27 paper-v1.tex
clean up

@@
 \item \emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
-\item \emph{Privacy}, which maintains the pseudo-anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).
+\item \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).
 \end{itemize}
@@
 AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS (See Figure \ref{fig:contracts}\textbf{c}), is the primary protocol ERC20 token and can be staked into an AntReview.
+\newline ANTS (See Figure \ref{fig:contracts} \textbf{c}), is the primary protocol ERC20 token and can be staked into an AntReview.
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.

### 2020-07-27 paper-v1.tex
clean up discussion

@@
 \subsection{Possible developments}
-An AntReview, issued by an author would be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[11]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[12]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...
+An AntReview, issued by an author could be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[11]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[12]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...
 with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate)\footnote[13]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[14]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
- An AntsReview DAO could be formed in the future to allow ANTS stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
+An Ants-Review DAO could be formed in the future to allow ANTS stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
 \newline Hive. When Anters make a deposit into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.

### 2020-07-27 paper-v1.tex
Updates from Overleaf

@@
 \newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart (See Figure \ref{fig:contracts}):
-
-\begin{itemize}
-\item \emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
-\item \emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
-\item \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).
-\end{itemize}
+\emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
+\emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
+\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).
 
@@
 It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
-\begin{itemize}
-  \item to upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS} and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
-  \item to specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
-  \item to specify the amount of Ether for the reward that will be transferred from Alice to the contract.
-\end{itemize}
+ 1.
+To upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS} and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
+ 2. To specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
+ 3. To specify the amount of Ether for the reward that will be transferred from Alice to the contract.
 
@@
 In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
-\newline Ants-Review is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
-\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
-In order to verify if a specific hash is included into a Merkle Tree by leveraging on \emph{MerkleProof.sol} (OpenZeppelin Library), we need to provide a proof, generated from the leaf of interest, that represents the ramification derived from the leaf, the root hash and, finally, the leaf we want to verify.
-\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using \emph{keccak256}, a cryptographic hashing algorithm available in Solidity.
 
@@
 The anonymity of an agent in the system is achieved in two ways:
-
-\begin{itemize}
-  \item via pseudo-anonymity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
-  \item via private transactions allowed by AZTEC Protocol security layer via zkANTS.
+1. Via pseudo-anonymity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
+2.
+Via private transactions allowed by AZTEC Protocol security layer via zkANTS.
 Future developments will allow to leverage on PLONK\cite{PLONK}proofs, a universal ZK-SNARK construction, to reduce gas costs and improve scalability.
-\end{itemize}
 

### 2020-07-28 paper-v1.tex
Proof of Existence [merkle tree/proof of work removed] w/ @naszam

@@
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
-InterPlanetary File System (IPFS) \cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages into maintaining the privacy of both authors and reviewers in a double-blind approach.
+InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes.
+IPFS's hashes are then stored inside the smart contracts' state that is timestamped in the Ethereum Blockchain where it remains unaltered and indelible.
+This notarization process is called Proof of Existence (PoE).
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.
 
@@
 In the following sections we describe the architecture of the system and its building blocks.
-\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart (See Figure \ref{fig:contracts}):
+\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (See Figure \ref{fig:contracts}):
 \emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
@@
 In this way, only the Issuer can create a new AntReview.
-\newline One of the key aspects of the protocol is the concept of Proof of Existence.
-In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
 

### 2020-07-28 paper-v1.tex
see Figure a,b,c... @naszam

@@
 In the following sections we describe the architecture of the system and its building blocks.
-\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (See Figure \ref{fig:contracts}):
-\emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
-\emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
-\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).
+\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
+\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, a-b; f; h).
+\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, c-e; h}).
+\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, d).
 
 \subsubsection{AntsReview}
-AntsReview (See Figure \ref{fig:contracts} \textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
 It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
@@
 AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS (See Figure \ref{fig:contracts} \textbf{c}), is the primary protocol ERC20 token and can be staked into an AntReview.
+\newline ANTS (see Figure \ref{fig:contracts}, c), is the primary protocol ERC20 token and can be staked into an AntReview.
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (See Figure \ref{fig:contracts} \textbf{d}), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
+\newline zkANTS (see Figure \ref{fig:contracts}, d), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
 \newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.

### 2020-07-28 paper-v1.tex
Alice and Bob (beginning) @naszam

@@
 InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes.
-IPFS's hashes are then stored inside the smart contracts' state that is timestamped in the Ethereum Blockchain where it remains unaltered and indelible.
-This notarization process is called Proof of Existence (PoE).
+IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible.
+This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
 \newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.
@@
 
-\subsubsection{AntsReview}
+\subsubsection{AntsReview.}
 AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
-It implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}, where she have to complete a series of required tasks that are essential to creating a transparent and openly accessible AntReview:
- 1.
-To upload the file containing the requirements of the peer-review and the paper into IPFS\cite{IPFS} and specify the IPFS Hash to be stored in the Ethereum Blockchain as \emph{proof of existence}, a notarization process by wich a document hash is timestamped into the block of Ethereum where the transaction take place, that allow manual verification of the existence of the document.
- 2. To specify a deadline in the form of a unix timestamp after which the fulfillment will no longer be accepted.
- 3. To specify the amount of Ether for the reward that will be transferred from Alice to the contract.
-
-Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
+AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
+\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
+ \newline 1.
+\emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
+ \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
+ \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
+ \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
 Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
-If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by sepcifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
+If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
 

### 2020-07-28 paper-v1.tex
Figure caption. @naszam

@@
 \includegraphics[scale=0.28]{AntsReview}
-\caption{\textbf{a} The core contract of the protocol, it implements a bounty system with the functions listed.
-\textbf{b} The module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
-\textbf{c} The native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin.
-It's linked to \textbf{a} and to \textbf{e}, to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
-\textbf{f} Represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
-\textbf{g} Represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
-\textbf{h} The library used by the protocol for secure contract development, with the modules listed.}
+\caption{Exagones represent the protocol's smart contracts.
+Ellipse represents the smart contract inherited by AntsReview.
+Clouds represent integrations into the protocol.
+Rectangles represent smart contracts' libraries.
+\textbf{a)} Core contract of the protocol implementing a bounty system with the functions listed.
+\textbf{b)} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
+\textbf{c)} Native token used in the protocol that inherits the \textbf{d)} contract from \emph{OpenZeppelin}.
+It is linked to \textbf{a)} and to \textbf{e)}, wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{f)} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
+\textbf{g)} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
+\textbf{h)} Library used by the protocol for secure contract development with the modules listed.}
 \label{fig:contracts}
@@
 Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
-If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
+If Alice does not receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
 
@@
 \subsubsection{Supplementary material}
-Source Code, DOI: 10.5281/ZENODO.3829162
-\newline Demo (PoC), DOI: 10.5281/ZENODO.3829183
+Source Code, DOI: 10.5281/zenodo.3953999
+\newline Proof of Concept (PoC) DApp, \url{antsreview.on.fleek.co}
+\newline Demo (PoC), DOI: 10.5281/zenodo.3964466
 

### 2020-07-28 paper-v1.tex
Bold for figure numbers in caption/text. @naszam

@@
 Rectangles represent smart contracts' libraries.
-\textbf{a)} Core contract of the protocol implementing a bounty system with the functions listed.
-\textbf{b)} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
-\textbf{c)} Native token used in the protocol that inherits the \textbf{d)} contract from \emph{OpenZeppelin}.
-It is linked to \textbf{a)} and to \textbf{e)}, wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
-\textbf{f)} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
-\textbf{g)} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
-\textbf{h)} Library used by the protocol for secure contract development with the modules listed.}
+\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
+\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
+\textbf{c} Native token used in the protocol that inherits the \textbf{d} contract from \emph{OpenZeppelin}.
+It is linked to (\textbf{a}) and to (\textbf{e}), wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
+\textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
+\textbf{h} Library used by the protocol for secure contract development with the modules listed.}
 \label{fig:contracts}
@@
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
 AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
@@
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts} \textbf{b}).
-It's implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})).
+It is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
 \newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS (see Figure \ref{fig:contracts}, c), is the primary protocol ERC20 token and can be staked into an AntReview.
+\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})), is the primary protocol ERC20 token and can be staked into an AntReview.
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (see Figure \ref{fig:contracts}, d), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
+\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
 \newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.

### 2020-07-28 paper-v1.tex
AntsReview & Tokenomics. Switched paragraphs order (Privacy <-> Tokenomics).

@@
 \newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
-\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, a-b; f; h).
-\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, c-e; h}).
-\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, d).
+\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h})).
+\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d})).
+\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})}).
 
@@
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})).
-It is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
-\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
-In this way, only the Issuer can create a new AntReview.
-
-\subsubsection{Tokenomics}
-AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})), is the primary protocol ERC20 token and can be staked into an AntReview.
-\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
-\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
-\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), that is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
+\newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
 
@@
 The anonymity of an agent in the system is achieved in two ways:
-1. Via pseudo-anonymity granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent.
-2.
-Via private transactions allowed by AZTEC Protocol security layer via zkANTS.
+\newline 1. via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent;
+\newline 2.
+via private transactions allowed by AZTEC Protocol security layer via zkANTS.
 Future developments will allow to leverage on PLONK\cite{PLONK}proofs, a universal ZK-SNARK construction, to reduce gas costs and improve scalability.
@@
 This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.
+
+\subsubsection{Tokenomics}
+AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
+\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
+\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of the Ants-Review Community).
+zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
+\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
 

### 2020-07-28 paper-v1.tex
Pseudo-anonymity @naszam

@@
 \subsubsection{Privacy}
-The anonymity of an agent in the system is achieved in two ways:
-\newline 1. via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent;
-\newline 2.
-via private transactions allowed by AZTEC Protocol security layer via zkANTS.
-Future developments will allow to leverage on PLONK\cite{PLONK}proofs, a universal ZK-SNARK construction, to reduce gas costs and improve scalability.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol security layer via zkANTS.
 
-EOA in Ethereum are controlled by private key.
-An user can send messages from an externally owned account by creating and signing a transaction.
-The limitation of this type of solution concerning the protocol's privacy is due to the fact that blockchain and transactions are public, therefore the details of transactions are visible to anyone by browsing a block explorer (like Etherscan), and are subjected to data mining that could extract value and identify users in the blockchain.
-\newline To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol.
+\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys.
+However, the privacy is limited by the fact that both the blockchain and its transactions are public.
+Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
+\paragraph{Private transactions.}To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol.
 In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.

### 2020-07-28 paper-v1.tex
Privacy

@@
 This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs and homomorphic encryption (see § Privacy in 3.2).
 
@@
 \subsubsection{Privacy}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's Externally Owned Accounts (EOA) addresses that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol security layer via zkANTS.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.
 
@@
 Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
-\paragraph{Private transactions.}To avoid that, Ants-Review will implement zkANTS, an Ant token wrapped into AZTEC Protocol.
-In the future zkANTS could leverage on zkSNARKS and PLONK, allowing private transactions in the system to maintain the privacy and anonymity of Peer-Reviewers.
-\newline The AZTEC Protocol was conceived to enable privacy on public blockchains. It uses a series of zero-knowledge proofs (ZK-SNARKs) and homomorphic encryption to validate encrypted transactions.
-\newline ZK-SNARKs (Zero-Knowledge Succinct Non-Interactive Argument of Knowledge) \cite{ZKSNARKs} refers to a proof construction where one can prove possession of certain information, like a secret key, without revealing that information, and without any interaction between prover and verifier.
-\newline Future developments will investigate viable solutions, for scaling the system, like ZK-ZK Rollup by AZTEC Protocol, one of the options being developed for a type of layer 2 construction that runs on top of Ethereum to improve scalability.
-This will enable smart contracts to run  at scale with quasi-instant transactions while still being secured by Ethereum.
+\paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption to validate encrypted transactions.
+\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
+\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.
 
 \subsubsection{Tokenomics}
-AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+Ants-Review integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.

### 2020-07-28 paper-v1.tex
Privacy @naszam

@@
 This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs and homomorphic encryption (see § Privacy in 3.2).
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).
 

### 2020-07-28 paper-v1.tex
init discussion w/@naszam

@@
 In this session we discuss future developments not yet implemented and implications of AntsReview.
-\subsection{Possible developments}
+\subsection{Future developments}
+So far we have described how Ants-Review protocol can solve the limitations of the current peer-review  system (see 2.1).
+In particular the lack of recognition, the lack of transparency, fraud and misconduct are solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases arvia anonymity granted by AZTEC Protocol (see § Privacy in 3.2).
 An AntReview, issued by an author could be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[11]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[12]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...

### 2020-07-28 paper-v1.tex
Smoothie-time

--- 2020-07-28 paper-v1.tex
@@
 \paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption to validate encrypted transactions.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[9]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
 \newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
@@
 \subsubsection{Tokenomics}
-Ants-Review integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+Ants-Review integrates a few \emph{ERC20}\footnote[10]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
@@
 zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[11]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
 \newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
@@
 \section{Discussions}
-In this session we discuss future developments not yet implemented and implications of AntsReview.
-\subsection{Possible developments}
-An AntReview, issued by an author could be seen as a poll, a container where Anters can stake Ether or ERC20 tokens from DeFi services including Dai\footnote[11]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[12]{\emph{Chai}.\textsc{URL:}https://chai.money.}, ...
-with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR (Dai Saving Rate)\footnote[13]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[14]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
-An Ants-Review DAO could be formed in the future to allow ANTS stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
-\newline Hive. When Anters make a deposit into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
-\newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
-\newline Hive will be implemented using a similar approach to Chai, an ERC20 token that accrues interest from MakerDAO's DSR or Compound, with name \emph{Hive} and symbol \emph{HIVE}
-\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for ANTS and wrapped into zkANTS to promote anonymity and sent between the peer-reviewers that fulfilled the AntReview.
+We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1).
+In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers by the creation of the community of Anters.
+\subsection{Future developments}
+The Ants-Review Protocol will make the following integrations.
+An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens.
+Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[12]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[13]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[14]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[15]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+In particular, we are considering to implement another ERC20 token, called \emph{Hive}, symbol \emph{HIVE}, a wrapper of ANTS that represents the accrued interest of the Anters' stake into AntReviews.
+This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
+A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
 \newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by \emph{Gitcoin} to match donations for grants.
-This will allow to incentivise prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank the best Peer-Reviewers.
+This will allow to incentives prolific peer-peviewers and research and improve the stability of the system together with ideally a reward system to rank the best peer-reviewers.
 
 \subsection{A new community-driven standard?}
-As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (BioMed Central, ELife, Frontiers, PeerJ, F1000 Research).
+As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
 If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value.
@@
 
-\subsubsection{CRediT Authorship Contribution Statement}
- Bianca Trovò: Conceptualization, Investigation, Design, Writing - original draft, Writing - review \& editing.
-Nazzareno Massari: Project administration, Design, Software development, Visualization, Writing - review \& editing.
-Both authors equally contributed and supervised the project.
-
 \subsubsection{Declaration of Competing Interest}
 The authors declare no competing interests.
-
+\small{
 \subsubsection{Acknowledgements} We would like to thank Matteo A.
 Tambussi and Keno Budde for useful comments and discussions; Evan C.
-Harris for internal review; Marcelo Colmenero for the pixel art in Figure 1.
+Harris for internal review; Marcelo Colmenero for the pixel art in Figure 1.}
 

### 2020-07-28 paper-v1.tex
Final review w/ @naszam (after smoothie)

@@
 %
-\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author: bianca.trovo@alumni.unitn.it} \and
-Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
+\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
+Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}
 %
@@
 Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up a reputational metric.
-We designed a protocol of smart contracts called Ants-Review that allows authors or editors to issue a bounty call for peer-reviewing pseudo-anonymously but in an open report a scientific manuscript.
-If requirements are met, peer-reviews will be accepted and payed by the Issuer proportionally to their quality and  constructiveness, judged by the editor or the community via Quadratic Voting (QV).
+We designed a protocol of smart contracts called Ants-Review that allows authors or editors to issue a bounty for open anonymous peer-reviews.
+If requirements are met, peer-reviews will be accepted and payed by the issuer proportionally to their quality and  constructiveness.
 To promote ethical behaviour and inclusiveness the system could implement a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.
@@
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-Those are: \emph{decentralization}, for which there are no trusted third parties; \emph{cryptographic hashing} and \emph{timestamping}, that create a digital footprint able to keep a traceable chronological record of research objects; \emph{immutability} or \emph{append-only}, for which data cannot be altered or retrieved.
+Those are: \emph{consensus algorithm}, a deterministic computational trust that allows \emph{decentralization}, for which there are no trusted third parties; \emph{cryptographic hashing} and \emph{timestamping}, that create a digital footprint able to keep a traceable chronological record of research objects; \emph{immutability} or \emph{append-only}, for which data cannot be altered or retrieved.
 In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
@@
 In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy and in line with the values of Open Science.
-\newline The paper is structured as follows.
-Sections 2 presents research background and related work.
-Section 3 explains the proposed protocol on the Ethereum blockchain illustrating the system architecture and the current status of implementation.
-In Section 4 we discuss the implication of our work.
-Section 5 contains the conclusions.
 
@@
 The system implements cryptoeconomical incentives for building reputation in the community of users.
-\newline Other proposals to improve the peer-review system have instead focused on features such as decentralization, security \cite{Pevo,CryptSubmit,MarsChain}.
+\newline Other proposals to improve the peer-review system have instead focused on features such as decentralization \cite{DecentralSc2,DecentralSc1}, security \cite{Pevo,CryptSubmit,MarsChain}.
 
@@
 Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
-\newline A previous version of this paper can be found here \cite{AntsReview}.
+\newline The original proposal behind this paper can be found here \cite{AntsReview}.
 \newline Its design and implementation are exposed in the following section.
@@
 \includegraphics[scale=0.28]{AntsReview}
+\small{
 \caption{Exagones represent the protocol's smart contracts.
@@
 \textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
-\textbf{h} Library used by the protocol for secure contract development with the modules listed.}
+\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
 \label{fig:contracts}
@@
 \newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
- \newline 1.
-\emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
- \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
- \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
+ \begin{itemize}
+     \item \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
+     \item \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
+     \item \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
+\end{itemize}
  \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
@@
 
+\small{
 \subsubsection{Supplementary material}
-Source Code, DOI: 10.5281/zenodo.3953999
-\newline Proof of Concept (PoC) DApp, \url{antsreview.on.fleek.co}
-\newline Demo (PoC), DOI: 10.5281/zenodo.3964466
+Source code, DOI: 10.5281/zenodo.3953999; Proof of Concept (PoC) DApp, antsreview.on.fleek.co; Demo (PoC), DOI: 10.5281/zenodo.3964466.
 
@@
 The authors declare no competing interests.
-\small{
+
 \subsubsection{Acknowledgements} We would like to thank Matteo A.
@@
 \bibliographystyle{splncs04}
-\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-relatedwork.bib, ref3-system.bib,ref4-discuss.bib, ref5-extra.bib}
+\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-related.bib, ref3-system.bib,ref4-discuss.bib, ref5-extra.bib}
 

### 2020-07-28 paper-v1.tex
Latest revision with @naszam

@@
 Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
-Independent Blockchain Engineer, London, UK \\
+Blockchain Engineer, London, UK \\
 \email{nazzareno@nazzarenomassari.com}}
@@
 Bounties are a prize or monetary reward given for completing a task before a deadline \cite{BountyGit}.
-Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[3]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[4]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
+Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[4]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[5]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
 Incentives can be cryptographic tokens, unit of values registered on a blockchain network and that represent the quantity and quality of a service within a network.
@@
 \paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[5]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
+Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[6]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
 
@@
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[8]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
 AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
@@
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), that is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), that is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[9]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
 \newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 \paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[9]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[10]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
 \newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
@@
 \subsubsection{Tokenomics}
-Ants-Review integrates a few \emph{ERC20}\footnote[10]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+Ants-Review integrates a few \emph{ERC20}\footnote[11]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
@@
 zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[11]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[12]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
 \newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
@@
 An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens.
-Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[12]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[13]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[14]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[15]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[13]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[14]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[15]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[16]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
 In particular, we are considering to implement another ERC20 token, called \emph{Hive}, symbol \emph{HIVE}, a wrapper of ANTS that represents the accrued interest of the Anters' stake into AntReviews.

### 2020-09-19 paper-v1.tex
update implementation by @naszam + edit by @biancasama

@@
 If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
-The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves (single-blind review).
+The reviewers identity is usually only known to the editor but is hidden to the authors or the other reviewers themselves (single-blind review).
 Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft.
-Depending on the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
+Depending on if the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
 The same reviewers might be contacted again to continue the same peer-review process.
@@
 Thus, it does not lead to advancements in career or help securing grants.
-Researchers are motivated in doing peer-review for a sense of belonging and a desire to 'give back' to the community.
+Researchers are motivated to do peer-review by a sense of belonging and a desire to 'give back' to the community.
 A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science be published through sloppy and uncritical reviews.
 \paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
-Some studies have reported an improvement in the transparency and 'civility; of the review process when open reports are released according to the standards of open peer review.
-\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination, social prestige of the institution.
+Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of open peer review.
+\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination and social prestige of the institution.
 To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
@@
 Incentives can be cryptographic tokens, unit of values registered on a blockchain network and that represent the quantity and quality of a service within a network.
-\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals)  should be able to retribute with tokens, an internal cryptocurrency that can be spent externally.
+\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals)  should be able to contribute with tokens, an internal cryptocurrency that can be spent externally.
 The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
 Thus, the system acts also as a reputation builder.
-\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews exchange to the same manuscript can have their tokens accrue interest over time (see 3.2).
+\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews on the same manuscript can have their tokens accrue interest over time (see 3.2).
 
@@
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[8]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}.
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{Kovan Testnet}.\textsc{URL:}https://kovan.etherscan.io/.}.
 AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
@@
  \begin{itemize}
-     \item \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
-     \item \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
-     \item \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
+     \item \emph{upload of the files} containing the requirements of the peer-review and the paper to be reviewed into IPFS, whose hash is stored into the Ethereum blockchain as PoE;
+     \item \emph{specification of a deadline} in the form of a UNIX timestamp after which the fulfillment will no longer be accepted;
+     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer-reviews sent by the peer-reviewers;
 \end{itemize}
- \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
-Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
-If Alice does not receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
+ Bob (peer-reviewer) downloads the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
+The Approver can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
+If Alice does not receive any peer-review, she cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), that is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[9]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[9]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
 \newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 This second option, which requires further implementations, is the one we aim at.
-Indeed, we foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review with a reputation build within community and not journals.
+Indeed, we foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
 Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
@@
 \subsubsection{Supplementary material}
-Source code, DOI: 10.5281/zenodo.3953999; Proof of Concept (PoC) DApp, antsreview.on.fleek.co; Demo (PoC), DOI: 10.5281/zenodo.3964466.
+Source code, DOI: 10.5281/zenodo.3971044; 
+\newline DApp, https://ants-review.on.fleek.co;
 
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A.
-Tambussi and Keno Budde for useful comments and discussions; Evan C.
-Harris for internal review; Marcelo Colmenero for the pixel art in Figure 1.}
+\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers.}
 

### 2020-09-19 paper-v1.tex
update implementation by @naszam

@@
 AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{Kovan Testnet}.\textsc{URL:}https://kovan.etherscan.io/.}.
-AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
+AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
 \newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
@@
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[9]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
 \newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 \paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[10]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
 \newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
@@
 \subsubsection{Tokenomics}
-Ants-Review integrates a few \emph{ERC20}\footnote[11]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
@@
 zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[12]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
 \newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
@@
 An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens.
-Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[13]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[14]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[15]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[16]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[15]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
 In particular, we are considering to implement another ERC20 token, called \emph{Hive}, symbol \emph{HIVE}, a wrapper of ANTS that represents the accrued interest of the Anters' stake into AntReviews.
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers.}
+\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers.}
 

### 2020-09-19 paper-v1.tex
update implementation by @naszam

@@
 \end{itemize}
- Bob (peer-reviewer) downloads the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
+ Alice or the Issuers can at any time update the AntReview details (issuers, paper, requirements, deadline) with the function \emph{changeAntReview()} and add/remove the Approver with the functions \emph{addApprover()} and \emph{removeApprover()}.
+ Anters (members of the Ants-Review Community), can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send.
+ Bob (peer-reviewer) can download the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
 The Approver can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
-If Alice does not receive any peer-review, she cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.
+If Alice's AntReview does not receive any peer-review and the deadline expires, Anters can get a refund with the function \emph{refund()} for their contributions.
+In order to avoid residual balance, Alice can withdraw ANTS from her AntReview's balance, if the deadline expires, with the function \emph{withdrawAntReview()}, and the contract will transfer the amount specified to Alice and update the balance.
 
 Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
-\newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to be able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts.
+\newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
 
@@
 \newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of the Ants-Review Community).
+\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
 zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.

### 2020-09-19 paper-v1.tex
updates by @naszam

@@
  Bob (peer-reviewer) can download the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
+He can update the peer-review with the function \emph{updateReview()} by uploading the new version on IPFS.
 The Approver can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
 If Alice's AntReview does not receive any peer-review and the deadline expires, Anters can get a refund with the function \emph{refund()} for their contributions.
-In order to avoid residual balance, Alice can withdraw ANTS from her AntReview's balance, if the deadline expires, with the function \emph{withdrawAntReview()}, and the contract will transfer the amount specified to Alice and update the balance.
+In order to avoid residual balance, Alice can withdraw ANTS from the AntReview's balance, if the deadline expires, with the function \emph{withdrawAntReview()}, and the contract will transfer the amount specified to Alice and update the balance.
 

### 2020-09-20 paper-v1.tex
update fig. 1 description by @naszam

@@
 \textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
-\textbf{c} Native token used in the protocol that inherits the \textbf{d} contract from \emph{OpenZeppelin}.
-It is linked to (\textbf{a}) and to (\textbf{e}), wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
+\textbf{c} Native token used in the protocol. It is linked to (\textbf{a}), (\textbf{e}) and to (\textbf{d}).
+\textbf{d} Faucet to distribute \emph{ANTS} on Kovan Testnet for testing purposes. 
+\textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
 \textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.

### 2020-09-20 paper-v1.tex
cleanup
updates by @naszam

@@
 \centering
-\includegraphics[scale=0.28]{AntsReview}
+\includegraphics[scale=0.28]{Ants-Review}
 \small{
@@
 It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
-\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents (Alice & Bob).
+\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
+ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
 \newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.
@@
 \subsection{Future developments}
-The Ants-Review Protocol will make the following integrations.
-An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens.
-Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services, such as Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}, Chai\footnote[15]{\emph{Chai}.\textsc{URL:}https://chai.money.}, with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
-In particular, we are considering to implement another ERC20 token, called \emph{Hive}, symbol \emph{HIVE}, a wrapper of ANTS that represents the accrued interest of the Anters' stake into AntReviews.
-This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
+An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a liquidity pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.} .
+Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+In particular, we are considering to implement another ERC20 token, a pool token that represents the accrued interest of the Anters' stake into AntReviews.
+This token doesn't need to be locked in the protocol and it can be traded, sold, or held as the Anter desires.
 A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.

### 2020-09-20 paper-v1.tex
cleanup

@@
 \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d})).
-\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})}).
+\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})).
 
@@
 \subsection{Future developments}
-An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a liquidity pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.} .
+An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.} .
 Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.

### 2020-09-20 paper-v1.tex
update discussions by @naszam

@@
 A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by \emph{Gitcoin} to match donations for grants.
-This will allow to incentives prolific peer-peviewers and research and improve the stability of the system together with ideally a reward system to rank the best peer-reviewers.
+\newline Finally, a protocol upgrade under investigation would allow Anters to validate peer-reviews via an upvote/downvote system inspired by Discover \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (Status \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}), that automatically will pay out the reward to peer-reviewers based on the votes associated with their peer-reviews.
 

### 2020-09-20 paper-v1.tex
updates

--- 2020-09-20 paper-v1.tex
@@
 \subsection{Future developments}
-An interesting aspect of the protocol is the double function of an AntReview that is a the same time a bounty and a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.} .
-Therefore, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility of accruing interest over time via MakerDAO DSR (Dai Saving Rate)\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.} or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
-In particular, we are considering to implement another ERC20 token, a pool token that represents the accrued interest of the Anters' stake into AntReviews.
-This token doesn't need to be locked in the protocol and it can be traded, sold, or held as the Anter desires.
+An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}.
+Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
 A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, another concept under investigation is Quadratic Funding \cite{LiberalRadicalism}, used by \emph{Gitcoin} to match donations for grants.
-This will allow to incentives prolific peer-peviewers and research and improve the stability of the system together with ideally a reward system to rank the best peer-reviewers.
+\newline Finally, a protocol upgrade inspired by Discover \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (Status \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 

### 2020-09-20 paper-v1.tex
update future developments by naszam

@@
 A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, a protocol upgrade inspired by Discover \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (Status \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+\newline Finally, a protocol upgrade inspired by Discover \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (Status \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 

### 2020-09-20 paper-v1.tex
update fig. 1 + paper
Updates from Overleaf

@@
 As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
-If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value.
-In our proposal we posed two possible integrations for Ants-Review, a simpler one which maintains part of the journals' power in the peer-review evaluation and more complex one that completely decouples the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.
-This second option, which requires further implementations, is the one we aim at.
-Indeed, we foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
+If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
+In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.
+We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
+\newline Enlarging the pool of reviewers and accelerating the whole process might make Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
 We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.

### 2020-09-20 paper-v1.tex
Discussion: changes on 'A new standard'

@@
 \centering
-\includegraphics[scale=0.28]{Ants-Review}
+\includegraphics[scale=0.28]{AntsReview}
 \small{
@@
 We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers and accelerating the whole process might make Peer reviews requires a standard: building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer reviews: for example some aspects might be taken over by AI assistants leaving to the reviewers the sole task of evaluating the content of a paper (such as \emph{AIRA} \cite{}).
+Building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
 We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.

### 2020-09-20 paper-v1.tex
Design: removed QV, fixed the ranking of peer-review

@@
 Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification.
-\newline An interesting addition would be to introduce Quadratic Voting (QV) \cite{QVWeyl} for the reviews' evaluation.
-QV replaces the discrete concept of one-person-one-vote with the non-linear one of n vote at the cost of $n^2$ and is optimal in the context of multiple choices.
-If we consider scientific outputs as public goods, then the community can vote (with voting tokens) 'how much they care' for a specific peer-review.
-A rank of peer-reviews would result from the voting process, with a more fine-graded distribution that might reflect issues that have a high value to few people and low value to more people.
-\newline Finally, it's conceivable that the members of the community participate to the share of the tokens by voting to the best peer-reviews.
+An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1  Future developments).
+It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well.
 This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.
@@
 If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
-In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying concepts from mechanism design.
-We foresee that the future will evolve towards community-organized peer reviews: peer reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
+In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incetivization mechanisms.
+We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
 \newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer reviews: for example some aspects might be taken over by AI assistants leaving to the reviewers the sole task of evaluating the content of a paper (such as \emph{AIRA} \cite{}).
-Building smart-contracts for peer-reviews might set a first step in this direction and our work seems promising.
+Building smart-contracts for peer-reviews might set a first step in this standardization.
 We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A. Tambussi, Andy Tudhope, Mark Beylin, Evan C. Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers.}
+\subsubsection{Acknowledgements} We would like to thank Matteo A.
+Tambussi, Andy Tudhope, Mark Beylin, Evan C.
+Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers for useful comments and revisions.}
 

### 2020-09-20 paper-v1.tex
abstract

@@
 Therefore, scientific dissemination is affected in the timeliness, quality and fairness.
-Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up a reputational metric.
-We designed a protocol of smart contracts called Ants-Review that allows authors or editors to issue a bounty for open anonymous peer-reviews.
-If requirements are met, peer-reviews will be accepted and payed by the issuer proportionally to their quality and  constructiveness.
+Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation.
+We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews.
+If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their quality and value.
 To promote ethical behaviour and inclusiveness the system could implement a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.

### 2020-09-21 paper-v1.tex
Introduction: fixes, references.

@@
 If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their quality and value.
-To promote ethical behaviour and inclusiveness the system could implement a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.
+To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.
 \keywords{Blockchain \and Open Science \and Peer-review \and Incentivization.}
@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BCTs) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
-Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}.
-Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} where decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-Those are: \emph{consensus algorithm}, a deterministic computational trust that allows \emph{decentralization}, for which there are no trusted third parties; \emph{cryptographic hashing} and \emph{timestamping}, that create a digital footprint able to keep a traceable chronological record of research objects; \emph{immutability} or \emph{append-only}, for which data cannot be altered or retrieved.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BT) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
+Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
+Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
+Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the Proof of Existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping}, creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
 In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
-\newline A thorny issue in the academic system that can and should be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
-In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy and in line with the values of Open Science.
+\newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
+In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy \cite{TokenEcon} and in line with the values of open science.
 

### 2020-09-21 paper-v1.tex
Abstract v 2.

@@
 Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation.
-We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews.
-If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their quality and value.
-To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews, vote for the best ones and share the incentives with the referees.
-\keywords{Blockchain \and Open Science \and Peer-review \and Incentivization.}
+We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum.
+If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their assessed quality.
+To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews and vote for the best ones.
+\keywords{Blockchain \and Ethereum \and Peer-review \and Incentivization.}
 \end{abstract}
@@
 The traditional peer-review process is completely controlled by the editor(s).
-The author(s) submit manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
+The author(s) submits manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
 If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
@@
 Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft.
-Depending on if the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers.
+Depending on if the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript.
 The same reviewers might be contacted again to continue the same peer-review process.
@@
 \paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
-Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of open peer review.
+Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of \emph{open peer review}.
 \paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination and social prestige of the institution.
-To solve this problem some journals have implemented double-blind review process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
+To solve this problem some journals have implemented \emph{double-blind review process} (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
 \paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?".
@@
 \section{System concept}
-In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors.
+In this paper we propose Ants-Review, a new incentivisation mechanism built on Ethereum that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors.
 We imagine a final paper originating from the peer-review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts.

### 2020-09-21 paper-v1.tex
updates by @naszam

@@
 
-\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials.
-\newline It's also worth mentioning \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, a service integrated with ORCID (researcher identifier) that provides peer-review metric; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.}, a journal-independent free service for scientific peer review and publishing that provides also a peer-review of the reviews.
+\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials where performance, though, is assessed only in terms of quantity of reviews but not quality.
+\newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} that provide scientific peer review and also peer-reviews of the reviews.
 Spearpoint\cite{ResearchCoin} proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees.
@@
 Here we describe the main features of Ants-Review.
-\paragraph{Incentivisation and recognition.} A typical business model for open source software (OSS) movement is open-source bounty.
-Bounties are a prize or monetary reward given for completing a task before a deadline \cite{BountyGit}.
+\paragraph{Incentivisation and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
+Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
 Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[4]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[5]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
-Incentives can be cryptographic tokens, unit of values registered on a blockchain network and that represent the quantity and quality of a service within a network.
+Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
 \newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals)  should be able to contribute with tokens, an internal cryptocurrency that can be spent externally.
@@
 We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer reviews: for example some aspects might be taken over by AI assistants leaving to the reviewers the sole task of evaluating the content of a paper (such as \emph{AIRA} \cite{}).
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants(such as the \emph{Artificial Intelligence Review Assistant (AIRA)} \cite{} and ) leaving to the reviewers the sole task of evaluating the content of a paper .
 Building smart-contracts for peer-reviews might set a first step in this standardization.
-We hope that soon the value of peer review as 'academic capital' will be recognized by research funders and hiring committees.
+We hope that soon the value of peer review as public good will be recognized by research funders and hiring committees.
 

### 2020-09-21 paper-v1.tex
Discussion: AIRA ref.

@@
 Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
-\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals)  should be able to contribute with tokens, an internal cryptocurrency that can be spent externally.
+\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens.
 The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
@@
 We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants(such as the \emph{Artificial Intelligence Review Assistant (AIRA)} \cite{} and ) leaving to the reviewers the sole task of evaluating the content of a paper .
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
+\textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper.
 Building smart-contracts for peer-reviews might set a first step in this standardization.

### 2020-09-22 paper-v1.tex
Background: related work.

@@
 \newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} that provide scientific peer review and also peer-reviews of the reviews.
-Spearpoint\cite{ResearchCoin} proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees.
-\emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process.
-Avital \cite{AvitalToken} suggests a token-based peer-review payment system.
-\emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
+\newline Alternative proposals to improve the peer-review system with an incentivization mechanism on the blockchain have been made by Spearpoint \cite{ResearchCoin} who proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees; \emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process; Avital \cite{AvitalToken} suggests a token-based peer-review payment system; \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
 The system implements cryptoeconomical incentives for building reputation in the community of users.
-\newline Other proposals to improve the peer-review system have instead focused on features such as decentralization \cite{DecentralSc2,DecentralSc1}, security \cite{Pevo,CryptSubmit,MarsChain}.
+\emph{Decentralized Science} \cite{DecentralSc2,DecentralSc1}, \emph{Pevo}\cite{Pevo}, \emph{CryptSubmit}\cite{CryptSubmit} and \emph{MarsChain}\cite{MarsChain} have instead respectively focused on features such as decentralization and security.
 
@@
 Here we describe the main features of Ants-Review.
-\paragraph{Incentivisation and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
+\paragraph{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
 Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
@@
 
-\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and reviewers' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
 Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[6]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
@@
 If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
-In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incetivization mechanisms.
+In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
 We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.

### 2020-09-22 paper-v1.tex
General fixes: footnotes, references.

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies (BT) have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
-Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
+Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
@@
 \newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
-In this paper we propose a solution to the problem of reviewers recognition based on the principles of token economy \cite{TokenEcon} and in line with the values of open science.
+In this paper we propose a solution to the problem of reviewers recognition based on the principles of tokenomics \cite{TokenEcon} and in line with the values of open science.
 
@@
 However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues, here reviewed.
-\paragraph{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
+\subsubsection{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
 The traditional peer-review process is completely controlled by the editor(s).
@@
 This process can take multiple rounds and is a huge time investment both for authors and reviewers.
-An analysis of all papers published in PubMed for a time period of 30 years claims that the median review time is around 100 days\cite{Kendall-peerrev}.
-\paragraph{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
+An analysis of all papers published in \emph{PubMed} for a time period of 30 years claims that the median review time is around 100 days \cite{Kendall-peerrev}.
+\subsubsection{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
 Thus, it does not lead to advancements in career or help securing grants.
@@
 A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science be published through sloppy and uncritical reviews.
-\paragraph{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
+\subsubsection{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
 Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of \emph{open peer review}.
-\paragraph{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination and social prestige of the institution.
-To solve this problem some journals have implemented \emph{double-blind review process} (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
-\paragraph{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?".
-\paragraph{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists.
-\cite{tragedy-reviewers}.
+\subsubsection{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination and social prestige of the institution.
+To solve this problem some journals have implemented \emph{double-blind review} process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
+\subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?".
+\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers}.
 
 \subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials where performance, though, is assessed only in terms of quantity of reviews but not quality.
-\newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} that provide scientific peer review and also peer-reviews of the reviews.
-\newline Alternative proposals to improve the peer-review system with an incentivization mechanism on the blockchain have been made by Spearpoint \cite{ResearchCoin} who proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees; \emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process; Avital \cite{AvitalToken} suggests a token-based peer-review payment system; \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
+\newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews.
+\newline Alternative proposals to ours to improve the peer-review system with an incentivization mechanism on the blockchain have been made by Spearpoint \cite{ResearchCoin} who proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees; \emph{ScienceMiles} \cite{ScienceMiles} a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process; Avital \cite{AvitalToken} suggests a token-based peer-review payment system; \emph{INFINITCODEX (I8X)} \cite{I8X}, a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
 The system implements cryptoeconomical incentives for building reputation in the community of users.
-\emph{Decentralized Science} \cite{DecentralSc2,DecentralSc1}, \emph{Pevo}\cite{Pevo}, \emph{CryptSubmit}\cite{CryptSubmit} and \emph{MarsChain}\cite{MarsChain} have instead respectively focused on features such as decentralization and security.
+\emph{Decentralized Science} \cite{DecentralSc2,DecentralSc1}, \emph{Pevo} \cite{Pevo}, \emph{CryptSubmit} \cite{CryptSubmit} and \emph{MarsChain} \cite{MarsChain} have instead respectively focused on features such as decentralization and security.
 
@@
 Here we describe the main features of Ants-Review.
-\paragraph{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
+\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
 Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
-Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[4]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[5]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
+Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
 Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
@@
 Thus, the system acts also as a reputation builder.
-\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews on the same manuscript can have their tokens accrue interest over time (see 3.2).
 
-\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and reviewers' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[6]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
+\subsubsection{Transparency and re-usability of the records.} The peer-review history, including authors' replies and reviewers' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.}, that provide a scientific peer review service, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
 
-\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
+\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
@@
 
-\paragraph{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}).
+\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}).
 In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback.
@@
 Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
-A Decentralized Autonomous Organization (DAO) could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, a protocol upgrade inspired by Discover \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (Status \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+A Decentralized Autonomous Organization (DAO) \cite{Wan} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
+\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (\emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 
 \subsection{A new community-driven standard?}
-As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
+As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
 If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
 In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
-We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
+We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
 \newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.

### 2020-09-22 paper-v1.tex
Gained some lines to keep 12 pages.

@@
 
-Here we describe the main features of Ants-Review.
 \subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
@@
 This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts(EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).
 
-\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer}).
+\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
 In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback.
@@
 
-In the following sections we describe the architecture of the system and its building blocks.
 \newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
@@
 \subsubsection{Privacy}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent; via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.
 
-\paragraph{Pseudo-anonymity.}EOAs in Ethereum are controlled via private keys.
+\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys.
 However, the privacy is limited by the fact that both the blockchain and its transactions are public.
 Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
-\paragraph{Private transactions.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
+\paragraph{\textbf{Private transactions}.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
 It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
@@
 In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
-\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
+\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
 
@@
 Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
-A Decentralized Autonomous Organization (DAO) \cite{Wan} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
+A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
 \newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (\emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
@@
 Tambussi, Andy Tudhope, Mark Beylin, Evan C.
-Harris, Mitrasish Mukherjee and the external anonymous peer-reviewers for useful comments and revisions.}
+Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the UI/UX.}
 

### 2020-09-22 paper-v1.tex
Overall fixes (lost zSNARK reference)

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum}.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum-Wood}.
 Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
@@
 This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see § Privacy in 3.2).
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
 
@@
 Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification.
-An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1  Future developments).
+An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1).
 It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well.
@@
 \subsubsection{Privacy}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol\cite{AZTEC}'s security layer.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol \cite{AZTEC}'s security layer.
 
@@
 Source code, DOI: 10.5281/zenodo.3971044; 
-\newline DApp, https://ants-review.on.fleek.co;
+\newline DApp: https://ants-review.on.fleek.co;
 

### 2020-09-22 paper-v1.tex
Abstract/Intro: small fixes

@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum \cite{Ethereum-Wood}.
+From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of general purpose smart contracts introduced by Ethereum \cite{Ethereum-Wood}.
 Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the Proof of Existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping}, creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
-In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science.
+Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
+In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to 'scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
 \newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
@@
 If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
-The reviewers identity is usually only known to the editor but is hidden to the authors or the other reviewers themselves (single-blind review).
+The reviewers identity is usually only known to the editor but is hidden to the authors or the other reviewers themselves (\emph{single-blind review}).
 Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft.

### 2020-09-22 paper-v1.tex
Publons

@@
 The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}.
-However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues, here reviewed.
+However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.
 \subsubsection{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
-The traditional peer-review process is completely controlled by the editor(s).
+The traditional peer-review process is centralized around the publisher's editor(s).
 The author(s) submits manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
@@
 An analysis of all papers published in \emph{PubMed} for a time period of 30 years claims that the median review time is around 100 days \cite{Kendall-peerrev}.
-\subsubsection{Lack of recognition.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
+\subsubsection{Lack of recognition and incentives.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
 Thus, it does not lead to advancements in career or help securing grants.
 Researchers are motivated to do peer-review by a sense of belonging and a desire to 'give back' to the community.
-A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation or let bad science be published through sloppy and uncritical reviews.
+A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation \cite{HauserIncent} or let bad science be published through sloppy and uncritical reviews.
 \subsubsection{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
-Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of \emph{open peer review}.
-\subsubsection{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision, such as gender or cultural discrimination and social prestige of the institution.
+Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of \emph{open peer review} \cite{PeerRev-NatComm}.
+\subsubsection{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision \cite{Tennant2017-F1000R}, such as gender or cultural discrimination and social prestige of the institution.
 To solve this problem some journals have implemented \emph{double-blind review} process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
-\subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?".
-\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers}.
+\subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?" \cite{Tennant2017-F1000R}.
+\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.
 
-\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials where performance, though, is assessed only in terms of quantity of reviews but not quality.
-\newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews.
-\newline Alternative proposals to ours to improve the peer-review system with an incentivization mechanism on the blockchain have been made by Spearpoint \cite{ResearchCoin} who proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees; \emph{ScienceMiles} \cite{ScienceMiles} a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process; Avital \cite{AvitalToken} suggests a token-based peer-review payment system; \emph{INFINITCODEX (I8X)} \cite{I8X}, a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process.
-The system implements cryptoeconomical incentives for building reputation in the community of users.
-\emph{Decentralized Science} \cite{DecentralSc2,DecentralSc1}, \emph{Pevo} \cite{Pevo}, \emph{CryptSubmit} \cite{CryptSubmit} and \emph{MarsChain} \cite{MarsChain} have instead respectively focused on features such as decentralization and security.
+\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials \cite{Tennant2017-F1000R} where performance, though, is assessed only in terms of quantity of reviews but not quality \cite{Warne-RewRev}.
+\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.} provides a free metric service for track, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
 

### 2020-09-22 paper-v1.tex
Design: Bounty, token.

@@
 \subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
-Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
+Bounties are prizes or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
 Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
-Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
+Incentives can be represented by tokens, unit of values registered on blockchain networks.
 \newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens.

### 2020-09-22 paper-v1.tex
Updates/fixes: Roles, Supp Mat @naszam

@@
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
-InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes.
+InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes.
 IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible.
-This notarization process is called Proof of Existence (PoE)and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s Externally Owned Accounts (EOA) addresses, zero-knowledge proofs, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
+This notarization process is called proof of existence (PoE) and allows manual verification of the existence of the document.
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
 
-\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing abolishing the editorial selection process ('open participation', 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
+\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing by abolishing the editorial selection process through 'open participation' (or 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
 In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback.
@@
 \newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
-\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h})).
-\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d})).
+\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h}));
+\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d}));
 \emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})).
+\newline Agents in the platform are: the issuers, the peer-reviewers, the approver, the contributors (Anters, members of the Ants-Review Community).
 
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{Kovan Testnet}.\textsc{URL:}https://kovan.etherscan.io/.}.
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.\textsc{URL:}\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
 AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
@@
 \end{itemize}
- Alice or the Issuers can at any time update the AntReview details (issuers, paper, requirements, deadline) with the function \emph{changeAntReview()} and add/remove the Approver with the functions \emph{addApprover()} and \emph{removeApprover()}.
- Anters (members of the Ants-Review Community), can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send.
- Bob (peer-reviewer) can download the files relative to Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
+ Alice can at any time update the AntReview details (issuers, paper, requirements, deadline) with the function \emph{changeAntReview()} and add/remove the approver with the functions \emph{addApprover()} and \emph{removeApprover()}.
+ Anters (contributors) can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send. 
+ \newline Bob (peer-reviewer) can download the files relative to Alice's paper and its requirements by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
 He can update the peer-review with the function \emph{updateReview()} by uploading the new version on IPFS.
-The Approver can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
+ \newline Ted (approver) can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
 If Alice's AntReview does not receive any peer-review and the deadline expires, Anters can get a refund with the function \emph{refund()} for their contributions.
@@
 
-Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that it's used to define the Issuer and Peer-Reviewer Roles.
-\newline AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the Owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
+Access management of the Ants-Review protocol is defined and controlled by the \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
+AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
 
 \subsubsection{Privacy}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent and via private transactions allowed by AZTEC Protocol \cite{AZTEC}'s security layer.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC Protocol \cite{AZTEC}'s security layer.
 
@@
 \paragraph{\textbf{Private transactions}.}AZTEC Protocol  was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{ZKSNARKs} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.\textsc{URL:}https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
-\newline ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.
+\textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
+ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
 ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
-\newline Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}proofs, a universal ZK-SNARK construction that reduces gas costs and improves scalability.
+Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.
 
 \subsubsection{Tokenomics}
-Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.
+\textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
-\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
-zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}}, will be used as template to build an AZTEC-compatible asset.
-\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
+It's implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
+\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (Issuer and Reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
+It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
+
+\subsubsection{State of Art} The current state-of-the-art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
 
@@
 We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1).
-In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers by the creation of the community of Anters.
+In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters.
 \subsection{Future developments}
 An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}.
-Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.} to cite a few.
+Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.}, to cite a few.
 Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
 A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.\textsc{URL:}https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.} (\emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.}) and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.
+\textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a web3 browser by \emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 
@@
 
-\small{
-\subsubsection{Supplementary material}
+\subsubsection{Supplementary Material}
 Source code, DOI: 10.5281/zenodo.3971044; 
@@
 
+\small{
 \subsubsection{Declaration of Competing Interest}
@@
 Tambussi, Andy Tudhope, Mark Beylin, Evan C.
-Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the UI/UX.}
+Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}
 

### 2020-09-22 paper-v1.tex
cleanup by @naszam

@@
 \end{itemize}
- Alice can at any time update the AntReview details (issuers, paper, requirements, deadline) with the function \emph{changeAntReview()} and add/remove the approver with the functions \emph{addApprover()} and \emph{removeApprover()}.
+ Alice or the issuers can at any time update the AntReview details (issuers, paper, requirements, deadline) with the function \emph{changeAntReview()} and add/remove the approver with the functions \emph{addApprover()} and \emph{removeApprover()}.
  Anters (contributors) can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send. 
@@
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
-It's implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (Issuer and Reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
+It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
+\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (issuer and reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
 It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.

### 2020-09-24 paper-v1.tex
fix description fig 1 by @naszam
English fixes via Google autocorrection

@@
 Indeed, the process, which is very costly in terms of time and intellectual investment, not only is not remunerated by the journals but it is also not openly recognized by the academic community as a relevant scientific output for a researcher.
-Therefore, scientific dissemination is affected in the timeliness, quality and fairness.
+Therefore, scientific dissemination is affected in timeliness, quality and fairness.
 Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation.
 We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum.
-If requirements are met, peer-reviews will be accepted and payed by the approver proportionally to their assessed quality.
+If requirements are met, peer-reviews will be accepted and paid by the approver proportionally to their assessed quality.
 To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews and vote for the best ones.
@@
 \subsection{Peer-review: present problems and mild solutions}
-Peer review is still the only quality control mechanism devoted to evaluate scientific outcomes.
+Peer review is still the only quality control mechanism devoted to evaluating scientific outcomes.
 The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}.
@@
 \subsubsection{Social and cognitive biases.} Given the fact that anonymity is usually asymmetrically applied only for reviewers, many power related dynamics can influence the reviewers decision \cite{Tennant2017-F1000R}, such as gender or cultural discrimination and social prestige of the institution.
-To solve this problem some journals have implemented \emph{double-blind review} process (identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
+To solve this problem some journals have implemented \emph{double-blind review} process (the identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
 \subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?" \cite{Tennant2017-F1000R}.
-\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journals publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.
+\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.
 
@@
 Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
-Incentives can be represented by tokens, unit of values registered on blockchain networks.
+Incentives can be represented by tokens, units of values registered on blockchain networks.
 \newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens.
@@
 
-\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
+\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflicts of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
 InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes.
-IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remain unaltered and indelible.
+IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remains unaltered and indelible.
 This notarization process is called proof of existence (PoE) and allows manual verification of the existence of the document.
@@
 \textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
-\textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
+\textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
 \textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
@@
 ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
-Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.
+Future developments will allow leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.
 
@@
 It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as a template to build an AZTEC-compatible asset.
 
@@
 Building smart-contracts for peer-reviews might set a first step in this standardization.
-We hope that soon the value of peer review as public good will be recognized by research funders and hiring committees.
+We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.
 
@@
 \subsubsection{Acknowledgements} We would like to thank Matteo A.
-Tambussi, Andy Tudhope, Mark Beylin, Evan C.
+Tambussi, Andy Tudhope, Mark Beylin, Simona Pop, Evan C.
 Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}

### 2020-09-24 paper-v1.tex
Discussion: PrePrint Reviews.

@@
 Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
-\newline The original proposal behind this paper can be found here \cite{AntsReview}.
-\newline Its design and implementation are exposed in the following section.
+The original proposal behind this paper can be found here \cite{AntsReview}.
+Its design and implementation are exposed in the following section.
 
@@
 As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
-If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
-In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
+Recently, pre-print servers, such as arXiv and biorXiv, started integrating peer-review services into their platforms: \emph{PREreview} \footnote[20]{\emph{PREreview.}  \textsc{URL:} https://www.prereview.org}, \emph{PeerCommunityIn.} \footnote[21]{\emph{PeerCommunityIn} \textsc{URL:} https://peercommunityin.org}, \emph{Review Commons} \footnote[22]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review} \footnote[23]{\emph{PrePrint Review.} \textsc{URL:} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
+This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer-review platforms and justify their added value (\emph{ibidem}).
+In our proposal we also decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
 We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
 \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper.
-Building smart-contracts for peer-reviews might set a first step in this standardization.
+Building smart-contracts for peer-reviews might accelerate this novel process of standardization.
 We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.

### 2020-09-24 paper-v1.tex
Discussion: ref standard peer review

@@
 We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
 \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper.

### 2020-09-24 paper-v1.tex
fix fig. 1 refs by @naszam

@@
 Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
-Incentives can be represented by tokens, units of values registered on blockchain networks.
-\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens.
+Incentives can be represented by tokens, units of values registered on the blockchain.
+In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens.
 The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
@@
 \emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h}));
-\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{d}));
-\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, e, h})).
+\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{e}));
+\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
 \newline Agents in the platform are: the issuers, the peer-reviewers, the approver, the contributors (Anters, members of the Ants-Review Community).

### 2020-09-24 paper-v1.tex
fix peer review in implementation by @naszam

@@
 \textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
-\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
+\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
 \textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
@@
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.\textsc{URL:}\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a})) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.\textsc{URL:}\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
 AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
@@
  \begin{itemize}
-     \item \emph{upload of the files} containing the requirements of the peer-review and the paper to be reviewed into IPFS, whose hash is stored into the Ethereum blockchain as PoE;
+     \item \emph{upload of the files} containing the requirements of the peer review and the paper to be reviewed into IPFS, whose hash is stored into the Ethereum blockchain as PoE;
      \item \emph{specification of a deadline} in the form of a UNIX timestamp after which the fulfillment will no longer be accepted;
-     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer-reviews sent by the peer-reviewers;
+     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer reviews sent by the peer-reviewers;
 \end{itemize}
@@
  Anters (contributors) can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send. 
- \newline Bob (peer-reviewer) can download the files relative to Alice's paper and its requirements by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer-review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
-He can update the peer-review with the function \emph{updateReview()} by uploading the new version on IPFS.
- \newline Ted (approver) can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
-If Alice's AntReview does not receive any peer-review and the deadline expires, Anters can get a refund with the function \emph{refund()} for their contributions.
+ \newline Bob (peer-reviewer) can download the files relative to Alice's paper and the requirements of the peer review by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
+He can update the peer review with the function \emph{updateReview()} by uploading the new version on IPFS.
+ \newline Ted (approver) can accept the peer review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
+If Alice's AntReview does not receive any peer review and the deadline expires, Anters can get a refund with the function \emph{refund()} for their contributions.
 In order to avoid residual balance, Alice can withdraw ANTS from the AntReview's balance, if the deadline expires, with the function \emph{withdrawAntReview()}, and the contract will transfer the amount specified to Alice and update the balance.

### 2020-09-24 paper-v1.tex
cleanup

@@
 
-Access management of the Ants-Review protocol is defined and controlled by the \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
-AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is granted to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
+Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
+AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, granted by default to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
 

### 2020-09-24 paper-v1.tex
cleanup

@@
 \emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
-\newline Agents in the platform are: the issuers, the peer-reviewers, the approver, the contributors (Anters, members of the Ants-Review Community).
+\newline Agents in the platform are: issuers, peer-reviewers, approvers and contributors (Anters, members of the Ants-Review Community).
 
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts} (\textbf{a})) is the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine, deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.\textsc{URL:}\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a})), the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine, is deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.\textsc{URL:}\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
 AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.

### 2020-09-24 paper-v1.tex
cleanup

@@
 
-Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:} https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
 AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, granted by default to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 However, the privacy is limited by the fact that both the blockchain and its transactions are public.
-Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan) and are subject to data mining that could extract value and identify users in the blockchain.
+Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}.
+\textsc{URL:} https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
 \paragraph{\textbf{Private transactions}.}AZTEC Protocol was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[11]{\emph{Homomorphic Encryption}.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[12]{\emph{Homomorphic Encryption}.
 \textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
@@
 \subsubsection{Tokenomics}
-Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.
+Ants-Review integrates a few \emph{ERC20}\footnote[13]{\emph{EIP 20}.
 \textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
@@
 It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as a template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[14]{\emph{EIP  1724}.\textsc{URL:} https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.
 
@@
 \subsection{Future developments}
-An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}.
-Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:}https://compound.finance.}, to cite a few.
+An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[15]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}.
+Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:} https://compound.finance.}, to cite a few.
 Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
@@
 \newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.
-\textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a web3 browser by \emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:}https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+\textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a web3 browser by \emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:} https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 
@@
 \subsubsection{Acknowledgements} We would like to thank Matteo A.
-Tambussi, Andy Tudhope, Mark Beylin, Simona Pop, Evan C.
+Tambussi, Andy Tudhope, Mark Beylin, Evan C.
 Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}

### 2020-09-24 paper-v1.tex
Fixes

@@
 \usepackage{graphicx}
+\usepackage{dirtytalk}
 \graphicspath{ {./img/} }
@@
 \section{Introduction}
-From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system Bitcoin \cite{BitcoinSatoshi}, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of general purpose smart contracts introduced by Ethereum \cite{Ethereum-Wood}.
-Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
+Since the birth of Bitcoin\cite{BitcoinSatoshi} in 2008 as a peer-to-peer electronic cash system, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of general purpose smart contracts introduced by Ethereum \cite{Ethereum-Wood}.
+Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a `game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
-In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to 'scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
+Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the Proof of Existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
+In particular, a `blockchainified science'\cite{BlockchainforScience} could `reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
 \newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
@@
 Peer review is still the only quality control mechanism devoted to evaluating scientific outcomes.
-The purpose of peer review is "improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism." \cite{Gropp-PeerRevStress}.
-However, the system is 'ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.
+The purpose of peer review is \say{improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.} \cite{Gropp-PeerRevStress}.
+However, the system is `ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.
 \subsubsection{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
 The traditional peer-review process is centralized around the publisher's editor(s).
-The author(s) submits manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
+The author(s) submit the manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
 If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
@@
 An analysis of all papers published in \emph{PubMed} for a time period of 30 years claims that the median review time is around 100 days \cite{Kendall-peerrev}.
-\subsubsection{Lack of recognition and incentives.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the 'impact factor' of an author).
+\subsubsection{Lack of recognition and incentives.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the impact factor of an author).
 Thus, it does not lead to advancements in career or help securing grants.
-Researchers are motivated to do peer-review by a sense of belonging and a desire to 'give back' to the community.
+Researchers are motivated to do peer-review by a sense of belonging and a desire to `give back' to the community.
 A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation \cite{HauserIncent} or let bad science be published through sloppy and uncritical reviews.
-\subsubsection{Fraud and misconduct.} Due to the 'publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
+\subsubsection{Fraud and misconduct.} Due to the `publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
 Some studies have reported an improvement in the transparency and civility of the review process when open reports are released according to the standards of \emph{open peer review} \cite{PeerRev-NatComm}.
@@
 To solve this problem some journals have implemented \emph{double-blind review} process (the identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
-\subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: "Who watches the watchers?" \cite{Tennant2017-F1000R}.
+\subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: \say{Who watches the watchers?} \cite{Tennant2017-F1000R}.
 \subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.
-
-\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials \cite{Tennant2017-F1000R} where performance, though, is assessed only in terms of quantity of reviews but not quality \cite{Warne-RewRev}.
+\\
+\\
+Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual `badges', certificates of performance, citation in annual editorials \cite{Tennant2017-F1000R} where performance, though, is assessed only in terms of quantity of reviews but not quality \cite{Warne-RewRev}.
 \newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.} provides a free metric service for track, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
@@
 
-\subsubsection{Transparency and re-usability of the records.} The peer-review history, including authors' replies and reviewers' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.}, that provide a scientific peer review service, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').
+\subsubsection{Transparency and re-usability of the records.} The peer-review history, including reviewers' recommendations and authors' replies, should be openly and permanently accessible to the community (in the form of `open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.}, that provide a scientific peer review service, peer-reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer-reviews').
 
@@
 IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remains unaltered and indelible.
-This notarization process is called proof of existence (PoE) and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
+This notarization process is called Proof of Existence (PoE) and allows manual verification of the existence of the document.
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and Zero-Knowledge Proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
 
-\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing by abolishing the editorial selection process through 'open participation' (or 'open interaction', 'open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
+\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing by abolishing the editorial selection process through `open participation' (or `open interaction', `open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
 In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback.
@@
  Anters (contributors) can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send. 
- \newline Bob (peer-reviewer) can download the files relative to Alice's paper and the requirements of the peer review by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
+\\
+Bob (peer-reviewer) can download the files relative to Alice's paper and the requirements of the peer review by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
 He can update the peer review with the function \emph{updateReview()} by uploading the new version on IPFS.
- \newline Ted (approver) can accept the peer review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
+\\
+Ted (approver) can accept the peer review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
 If Alice's AntReview does not receive any peer review and the deadline expires, Anters can get a refund with the function \emph{refund()} for their contributions.
 In order to avoid residual balance, Alice can withdraw ANTS from the AntReview's balance, if the deadline expires, with the function \emph{withdrawAntReview()}, and the contract will transfer the amount specified to Alice and update the balance.
-
+\\
+\\
 Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:} https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
@@
 \paragraph{\textbf{Private transactions}.}AZTEC Protocol was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (ZK-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[12]{\emph{Homomorphic Encryption}.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[12]{\emph{Homomorphic Encryption}.
 \textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
-ZK-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
+zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
 ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
-Future developments will allow leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK} proofs, a universal zkSNARK construction that reduces gas costs and improves scalability.
+Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}, a universal zk-SNARK construction that reduces gas costs and improves scalability.
 
@@
 It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents (issuer and reviewer), preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
+A Faucet (see Figure \ref{fig:contracts}, (\text{d}) is implemented to distribute ANTS token on Kovan Testnet for testing purposes.
+\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
 It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
 In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[14]{\emph{EIP  1724}.\textsc{URL:} https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.
-
-\subsubsection{State of Art} The current state-of-the-art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
+\\
+\\
+The current state-of-the-art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
 
 \section{Discussions}
-We have described how Ants-Review protocol can solve the limitations of the current peer-review system (see 2.1).
-In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see § AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see § Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters.
+We have described how Ants-Review protocol can solve the limitations of the current peer review system (see 2.1).
+In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see §AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see §Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters.
 \subsection{Future developments}
@@
 A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, a protocol upgrade inspired by \emph{Discover} \footnote[18]{\emph{Discover.sol}.
-\textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a web3 browser by \emph{Status} \footnote[19]{\emph{Status}.\textsc{URL:} https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+\newline Finally, a protocol upgrade inspired by \emph{Discover}\footnote[18]{\emph{Discover.sol}.
+\textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a Web3 browser by \emph{Status}\footnote[19]{\emph{Status}.\textsc{URL:} https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 
@@
 As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
-Recently, pre-print servers, such as arXiv and biorXiv, started integrating peer-review services into their platforms: \emph{PREreview} \footnote[20]{\emph{PREreview.}  \textsc{URL:} https://www.prereview.org}, \emph{PeerCommunityIn.} \footnote[21]{\emph{PeerCommunityIn} \textsc{URL:} https://peercommunityin.org}, \emph{Review Commons} \footnote[22]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review} \footnote[23]{\emph{PrePrint Review.} \textsc{URL:} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
+Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[20]{\emph{PREreview.}  \textsc{URL:} https://www.prereview.org}, \emph{PeerCommunityIn.}\footnote[21]{\emph{PeerCommunityIn} \textsc{URL:} https://peercommunityin.org}, \emph{Review Commons}\footnote[22]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[23]{\emph{PrePrint Review.} \textsc{URL:} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
 This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer-review platforms and justify their added value (\emph{ibidem}).
 In our proposal we also decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
-We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
+We foresee that the future will evolve towards community-driven peer reviews: peer reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
 \newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
 \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper.
-Building smart-contracts for peer-reviews might accelerate this novel process of standardization.
+Building smart-contracts for peer reviews might accelerate this novel process of standardization.
 We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.
@@
 \section{Conclusion}
-In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process.
-We've shown how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
-We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-reviews.
+In this paper we addressed a crucial problem within scholarly academic communication: the peer review process.
+We have shown how blockchain technology could provide an efficient and viable solution to open up possible directions for a paradigm shift in scientific communication.
+We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer reviews.
 We exposed the architecture of our project for which we adopted cutting-edge tools from the open source blockchain ecosystem.

### 2020-09-24 paper-v1.tex
cleanup

@@
 Peer review is still the only quality control mechanism devoted to evaluating scientific outcomes.
-The purpose of peer review is \say{improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.} \cite{Gropp-PeerRevStress}.
+The purpose of peer review is \say{improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.}\cite{Gropp-PeerRevStress}.
 However, the system is `ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.
@@
 \subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: \say{Who watches the watchers?} \cite{Tennant2017-F1000R}.
-\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.
+\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists\cite{tragedy-reviewers,Warne-RewRev}.
 \\
@@
 Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual `badges', certificates of performance, citation in annual editorials \cite{Tennant2017-F1000R} where performance, though, is assessed only in terms of quantity of reviews but not quality \cite{Warne-RewRev}.
-\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.} provides a free metric service for track, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
+\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.} provides a free metric service for tracking, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
 
@@
 \subsection{Implementation}
+The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
+\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h}));
+\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{e}));
+\emph{Tokenomics -}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
+\newline Agents in the platform are: issuers, peer-reviewers, approvers and contributors (Anters, members of the Ants-Review Community).
 
@@
 
-\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (see Figure \ref{fig:contracts}):
-\emph{AntsReview}, which manages access management and the core system (see Figure \ref{fig:contracts}, (\textbf{a, b, f, h}));
-\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{e}));
-\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
-\newline Agents in the platform are: issuers, peer-reviewers, approvers and contributors (Anters, members of the Ants-Review Community).
-
 \subsubsection{AntsReview.}
@@
 \\
-\\
 Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:} https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
@@
 
-\subsubsection{Privacy}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC Protocol \cite{AZTEC}'s security layer.
+\subsubsection{Privacy.}
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC Protocol's security layer \cite{AZTEC}.
 
-\paragraph{\textbf{Pseudo-anonymity}.}EOAs in Ethereum are controlled via private keys.
+\paragraph{\textbf{Pseudo-anonymity}-}EOAs in Ethereum are controlled via private keys.
 However, the privacy is limited by the fact that both the blockchain and its transactions are public.
@@
 \textsc{URL:} https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
-\paragraph{\textbf{Private transactions}.}AZTEC Protocol was conceived to enable privacy on public blockchains.
+\paragraph{\textbf{Private transactions}-}AZTEC Protocol was conceived to enable privacy on public blockchains.
 It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[12]{\emph{Homomorphic Encryption}.
@@
 zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
-ZK-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
-Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK}, a universal zk-SNARK construction that reduces gas costs and improves scalability.
+zk-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
+Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK},
+a universal zk-SNARK construction that reduces gas costs and improves scalability.
 
-\subsubsection{Tokenomics}
+\subsubsection{Tokenomics.}
 Ants-Review integrates a few \emph{ERC20}\footnote[13]{\emph{EIP 20}.
-\textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
+\textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol.
 \newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
@@
 \\
-The current state-of-the-art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
+The current state of the art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
 

### 2020-09-24 paper-v1.tex
Paragraph Indentation removed.

@@
 AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
-\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
+\par In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
  \begin{itemize}
@@
      \item \emph{specification of a deadline} in the form of a UNIX timestamp after which the fulfillment will no longer be accepted;
-     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer reviews sent by the peer-reviewers;
+     \item \emph{specification of the Issuers and an Approver} to respectively modify the AntReview and approve the peer reviews sent by the peer-reviewers.
 \end{itemize}
@@
  Anters (contributors) can contribute to Alice's AntReview with the function \emph{contribute()}, by specifying the amount of ANTS they are willing to send. 
-\\
 Bob (peer-reviewer) can download the files relative to Alice's paper and the requirements of the peer review by leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by uploading the peer review on IPFS, whose hash is stored into Ethereum blockchain as PoE.
 He can update the peer review with the function \emph{updateReview()} by uploading the new version on IPFS.
-\\
 Ted (approver) can accept the peer review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the amount of ANTS that will be transferred as reward from the contract to Bob.
@@
 \subsubsection{Privacy.}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC Protocol's security layer \cite{AZTEC}.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC\cite{AZTEC} Protocol's security layer.
 
@@
 \\
-\\
-The current state of the art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
+\\ The current state of the art of Ants-Review is represented by version 0.2.0 (MVP) live on Ethereum Kovan Testnet (see Supplementary Material).
 

### 2020-09-24 paper-v1.tex
Push del c*zz*
fix footnotes & refs

@@
 Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual `badges', certificates of performance, citation in annual editorials \cite{Tennant2017-F1000R} where performance, though, is assessed only in terms of quantity of reviews but not quality \cite{Warne-RewRev}.
-\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.} provides a free metric service for tracking, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
+\newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.
+https://publons.com} provides a free metric service for tracking, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
 
@@
 Bounties are prizes or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
-Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}.
+Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[2]{\emph{Gitcoin}.
+https://gitcoin.co} and \emph{The Bounties Network}\footnote[3]{\emph{The Bounties Network}.
+https://bounties.network}.
 Incentives can be represented by tokens, units of values registered on the blockchain.
@@
 \subsubsection{Transparency and re-usability of the records.} The peer-review history, including reviewers' recommendations and authors' replies, should be openly and permanently accessible to the community (in the form of `open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.}, that provide a scientific peer review service, peer-reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer-reviews').
+Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.
+http://nprc.incf.org} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.
+https://www.researchsquare.com} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.
+https://www.peerageofscience.org}, that provide a scientific peer review service, peer-reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer-reviews').
 
@@
 \subsubsection{AntsReview.}
-AntsReview (see Figure \ref{fig:contracts} (\textbf{a})), the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine, is deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.\textsc{URL:}\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
-AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.\textsc{URL:}https://github.com/Bounties-Network/StandardBounties/blob/master/contracts/StandardBounties.sol.}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
-\par In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
+AntsReview (see Figure \ref{fig:contracts} (\textbf{a})), the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.
+https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine, is deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.
+\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
+AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.
+https://github.com/Bounties-Network/StandardBounties}) where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
+\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
  \begin{itemize}
@@
 
-\paragraph{\textbf{Pseudo-anonymity}-}EOAs in Ethereum are controlled via private keys.
+\paragraph{\textbf{Pseudo-anonymity.}}EOAs in Ethereum are controlled via private keys.
 However, the privacy is limited by the fact that both the blockchain and its transactions are public.
 Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}.
-\textsc{URL:} https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
-\paragraph{\textbf{Private transactions}-}AZTEC Protocol was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs)\cite{zSNARK} and homomorphic encryption\footnote[12]{\emph{Homomorphic Encryption}.
-\textsc{URL:}\newline https://vitalik.ca/general/2020/07/20/homomorphic.html.} to validate encrypted transactions.
+https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
+\paragraph{\textbf{Private transactions.}}AZTEC Protocol was conceived to enable privacy on public blockchains.
+It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions.
 zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
@@
 \subsubsection{Tokenomics.}
-Ants-Review integrates a few \emph{ERC20}\footnote[13]{\emph{EIP 20}.
-\textsc{URL:} https://eips.ethereum.org/EIPS/eip-20.} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol.
-\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
+Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.
+https://eips.ethereum.org/EIPS/eip-20.} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol.
+ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
 It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
 A Faucet (see Figure \ref{fig:contracts}, (\text{d}) is implemented to distribute ANTS token on Kovan Testnet for testing purposes.
-\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
+zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
 It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
-In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[14]{\emph{EIP  1724}.\textsc{URL:} https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.
+In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.
+https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.
 \\
@@
 \subsection{Future developments}
-An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[15]{\emph{Dai}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation.}.
-Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[16]{\emph{Pot}.\textsc{URL:}https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[17]{\emph{Compound}.\textsc{URL:} https://compound.finance.}, to cite a few.
+An interesting aspect of the protocol is the double function of an AntReview respectively as a bounty and as a pool to stake ERC20 tokens like Dai\footnote[14]{\emph{Dai}.
+https://docs.makerdao.com/smart-contract-modules/dai-module/dai-detailed-documentation}.
+Moreover, the duration of peer-reviews consents to connect the protocol to De-Fi services with the possibility for the community to accrue interest over time via MakerDAO Dai Saving Rate (Pot\footnote[15]{\emph{Pot}.
+https://docs.makerdao.com/smart-contract-modules/rates-module/pot-detailed-documentation.}) or Compound\footnote[16]{\emph{Compound}.
+https://compound.finance}, to cite a few.
 Therefore, an ERC20 \emph{pool token} would be automatically released by the protocol, representing the accrued interest on the Anters' stake over time that can be traded, sold, or held as the Anter desires.
 A Decentralized Autonomous Organization (DAO) \cite{Wang-DAO,DAOContr} could be formed in the future to allow ANTS stakers to participate in the governance of important aspects of the protocol, from smart contracts upgrades to minor changes in settings across the protocol.
-\newline Finally, a protocol upgrade inspired by \emph{Discover}\footnote[18]{\emph{Discover.sol}.
-\textsc{URL:}\newline https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol.}, a Web3 browser by \emph{Status}\footnote[19]{\emph{Status}.\textsc{URL:} https://status.im/.} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+\newline Finally, a protocol upgrade inspired by \emph{Discover}\footnote[17]{\emph{Discover.sol}.
+https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol}, a Web3 browser by \emph{Status}\footnote[18]{\emph{Status}.
+https://status.im/} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
 
@@
 As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
-Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[20]{\emph{PREreview.}  \textsc{URL:} https://www.prereview.org}, \emph{PeerCommunityIn.}\footnote[21]{\emph{PeerCommunityIn} \textsc{URL:} https://peercommunityin.org}, \emph{Review Commons}\footnote[22]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[23]{\emph{PrePrint Review.} \textsc{URL:} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
+Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn.}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
 This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer-review platforms and justify their added value (\emph{ibidem}).
@@
 We foresee that the future will evolve towards community-driven peer reviews: peer reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}.
-\textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper.
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)\cite{AIRA}} leaving to the reviewers the sole task of evaluating the content of a paper.
 Building smart-contracts for peer reviews might accelerate this novel process of standardization.
@@
 
+\small{
 \subsubsection{Supplementary Material}
@@
 
-\small{
 \subsubsection{Declaration of Competing Interest}

### 2020-09-25 paper-v1.tex
Fixed: title (caps), peer-reviews (removed -), acknowledgments.

@@
 %
-\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
+\title{Ants-Review: a Protocol for Open Anonymous Peer Reviews}
 %
@@
 \section{Introduction}
-Since the birth of Bitcoin\cite{BitcoinSatoshi} in 2008 as a peer-to-peer electronic cash system, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of general purpose smart contracts introduced by Ethereum \cite{Ethereum-Wood}.
+Since the birth of Bitcoin \cite{BitcoinSatoshi} in 2008 as a peer-to-peer electronic cash system, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of general purpose smart contracts introduced by Ethereum \cite{Ethereum-Wood}.
 Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a `game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
@@
 In particular, a `blockchainified science'\cite{BlockchainforScience} could `reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
-\newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer-review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
+\newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
 In this paper we propose a solution to the problem of reviewers recognition based on the principles of tokenomics \cite{TokenEcon} and in line with the values of open science.
@@
 \section{Background}
-\subsection{Peer-review: present problems and mild solutions}
+\subsection{Peer review: present problems and mild solutions}
 Peer review is still the only quality control mechanism devoted to evaluating scientific outcomes.
@@
 However, the system is `ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.
-\subsubsection{A slow multi-stage process.} The main issues affecting the effectiveness of peer-review is the delay between paper submission and journal acceptance for publication.
-The traditional peer-review process is centralized around the publisher's editor(s).
+\subsubsection{A slow multi-stage process.} The main issues affecting the effectiveness of peer review is the delay between paper submission and journal acceptance for publication.
+The traditional peer review process is centralized around the publisher's editor(s).
 The author(s) submit the manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
@@
 Depending on if the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript.
-The same reviewers might be contacted again to continue the same peer-review process.
+The same reviewers might be contacted again to continue the same peer review process.
 This process can take multiple rounds and is a huge time investment both for authors and reviewers.
 An analysis of all papers published in \emph{PubMed} for a time period of 30 years claims that the median review time is around 100 days \cite{Kendall-peerrev}.
-\subsubsection{Lack of recognition and incentives.} Peer-reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the impact factor of an author).
+\subsubsection{Lack of recognition and incentives.} Peer reviewing is an invisible activity purely conducted on voluntary basis, neither paid by the journals or officially credited via standard scientific metrics (such as the ones that establish the Impact Factor of an author).
 Thus, it does not lead to advancements in career or help securing grants.
 Researchers are motivated to do peer-review by a sense of belonging and a desire to `give back' to the community.
-A major consequence of not promoting incentives for the quality (and quantity) of peer-reviews is to either slow down publication of potentially good research which awaits for validation \cite{HauserIncent} or let bad science be published through sloppy and uncritical reviews.
+A major consequence of not promoting incentives for the quality (and quantity) of peer reviews is to either slow down publication of potentially good research which awaits for validation \cite{HauserIncent} or let bad science be published through sloppy and uncritical reviews.
 \subsubsection{Fraud and misconduct.} Due to the `publish or perish culture' pressures, unethical behaviour from reviewers has been occasionally reported, from abusive behaviour towards authors \cite{Smith2006,tragedy-reviewers} to identity fraud.
@@
 \section{System concept}
-In this paper we propose Ants-Review, a new incentivisation mechanism built on Ethereum that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors.
-We imagine a final paper originating from the peer-review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts.
+In this paper we propose Ants-Review, a new incentivisation mechanism built on Ethereum that issues open peer reviews to validate scientific papers while preserving the anonymity of its contributors.
+We imagine a final paper originating from the peer review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts.
 Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
@@
 
-\subsubsection{Transparency and re-usability of the records.} The peer-review history, including reviewers' recommendations and authors' replies, should be openly and permanently accessible to the community (in the form of `open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
-Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.
+\subsubsection{Transparency and re-usability of the records.} The peer review history, including reviewers' recommendations and authors' replies, should be openly and permanently accessible to the community (in the form of `open reports' of open peer reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge.
+Following the example of models offered by journals peer review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.
 http://nprc.incf.org} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.
 https://www.researchsquare.com} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.
-https://www.peerageofscience.org}, that provide a scientific peer review service, peer-reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer-reviews').
+https://www.peerageofscience.org}, that provide a scientific peer review service, peer reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer reviews').
 
@@
 
-\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer-reviewing by abolishing the editorial selection process through `open participation' (or `open interaction', `open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
+\subsubsection{Inclusiveness via gamification.} As a final step we propose that all the community is involved in the process of peer reviewing by abolishing the editorial selection process through `open participation' (or `open interaction', `open platform' \cite{OPR-Ross-Hellauer,RossHellauer-OPR}).
 In this way, the pool of reviewers is enriched and allows younger researchers to get the appropriate training through interactive feedback.
-Moreover, peer-reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification.
-An interesting addition would be to introduce a rank of peer-reviews resulting from the community feedback via a voting process (see 4.1).
-It's conceivable that the community members that engage in assessing the quality of peer-reviews could be incentivized as well.
-This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer-reviews would be also in the interest of the agents at play.
+Moreover, peer reviews could be evaluated, commented, criticised by the other members of the scientific community, enabling a virtuous loop of verification.
+An interesting addition would be to introduce a rank of peer reviews resulting from the community feedback via a voting process (see 4.1).
+It's conceivable that the community members that engage in assessing the quality of peer reviews could be incentivized as well.
+This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer reviews would be also in the interest of the agents at play.
 
@@
 \emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (see Figure  \ref{fig:contracts}, (\textbf{e}));
-\emph{Tokenomics -}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
-\newline Agents in the platform are: issuers, peer-reviewers, approvers and contributors (Anters, members of the Ants-Review Community).
+\emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
+\newline Agents in the platform are: issuers, peer reviewers, approvers and contributors (Anters, members of the Ants-Review Community).
 
@@
 \paragraph{\textbf{Private transactions.}}AZTEC Protocol was conceived to enable privacy on public blockchains.
-It uses Zero-Knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions.
+It uses zero-knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions.
 zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
@@
 https://github.com/dap-ps/discover/blob/master/contracts/Discover.sol}, a Web3 browser by \emph{Status}\footnote[18]{\emph{Status}.
-https://status.im/} and still under investigation would allow Anters to validate peer-reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer-reviews.
+https://status.im/} and still under investigation would allow Anters to validate peer reviews via an upvote/downvote system that will consent the protocol to automatically pay out the reward to the reviewers based on the votes associated with their peer reviews.
 
@@
 Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn.}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
-This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer-review platforms and justify their added value (\emph{ibidem}).
-In our proposal we also decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
+This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value (\emph{ibidem}).
+In our proposal we also decoupled the peer review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
 We foresee that the future will evolve towards community-driven peer reviews: peer reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)\cite{AIRA}} leaving to the reviewers the sole task of evaluating the content of a paper.
-Building smart-contracts for peer reviews might accelerate this novel process of standardization.
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)\cite{AIRA}} leaving to the reviewers the sole task of evaluating the content of a paper.
+Building smart contracts for peer reviews might accelerate this novel process of standardization.
 We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.
@@
 Source code, DOI: 10.5281/zenodo.3971044; 
-\newline DApp: https://ants-review.on.fleek.co;
+\newline DApp: https://ants-review.on.fleek.co.
 
@@
 Tambussi, Andy Tudhope, Mark Beylin, Evan C.
-Harris and the external anonymous peer-reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}
+Harris and the four external anonymous peer reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.
+The project was born during ETH Turin hackathon (April 24-26th 2020) and further developed in the Kernel Gitcoin program (July 7th - August 31st 2020).}
 

### 2020-09-25 paper-v1.tex
Minor errors, references.

@@
 We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum.
-If requirements are met, peer-reviews will be accepted and paid by the approver proportionally to their assessed quality.
+If requirements are met, peer reviews will be accepted and paid by the approver proportionally to their assessed quality.
 To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews and vote for the best ones.
@@
 Since the birth of Bitcoin \cite{BitcoinSatoshi} in 2008 as a peer-to-peer electronic cash system, blockchain technologies have spread far beyond the sole cryptocurrency domain, in particular after the implementation of general purpose smart contracts introduced by Ethereum \cite{Ethereum-Wood}.
-Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a `game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
+Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity, to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a `game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}.
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
@@
 In particular, a `blockchainified science'\cite{BlockchainforScience} could `reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
-\newline A thorny issue in the academic system that can - and should - be tackled by blockchain concerns the status and accreditation of peer review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
+\newline A thorny issue in the academic system that can - and we think it should - be tackled by blockchain concerns the status and accreditation of peer review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
 In this paper we propose a solution to the problem of reviewers recognition based on the principles of tokenomics \cite{TokenEcon} and in line with the values of open science.
@@
 \subsubsection{A slow multi-stage process.} The main issues affecting the effectiveness of peer review is the delay between paper submission and journal acceptance for publication.
-The traditional peer review process is centralized around the publisher's editor(s).
+The traditional peer review process is centralized around the journals' editor(s).
 The author(s) submit the manuscript to the journal where an editorial team assesses if the paper meets the scopes of the journal and novelty criteria.
@@
 Thus, it does not lead to advancements in career or help securing grants.
-Researchers are motivated to do peer-review by a sense of belonging and a desire to `give back' to the community.
+Researchers are motivated to do peer-review by a sense of belonging and a desire to `give back' to the community \cite{Warne-RewRev}.
 A major consequence of not promoting incentives for the quality (and quantity) of peer reviews is to either slow down publication of potentially good research which awaits for validation \cite{HauserIncent} or let bad science be published through sloppy and uncritical reviews.

### 2020-09-25 paper-v1.tex
Last fixes before submission.

@@
 \newline Partnering with publishers, the startup \emph{Publons}\footnote[1]{\emph{Publons}.
-https://publons.com} provides a free metric service for tracking, verification and recognition of publications, peer-reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
+https://publons.com} provides a free metric service for tracking, verification and recognition of publications, peer reviews and journal editing in a single researcher identifier that showcases a record of scientific activity and impact based on authors' productivity.
 
@@
 This notarization process is called Proof of Existence (PoE) and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and Zero-Knowledge Proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
 
@@
 \textbf{e} Integration with Aztec Protocol to wrap (\textbf{c}) into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
-\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
+\textbf{f} Integration with IPFS to upload papers, requirements and peer reviews and store the hash as \emph{PoE} into AntsReview (\textbf{a}).
 \textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
@@
 \subsubsection{Privacy.}
-The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC\cite{AZTEC} Protocol's security layer.
+The anonymity of an agent in the system is achieved in two ways: via pseudo-anonymity, granted through Ethereum's EOAs that can pseudo-obscure the identity of the agent, and via private transactions allowed by AZTEC \cite{AZTEC} Protocol's security layer.
 
@@
 Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}.
-https://etherscan.io/.}) and are subject to data mining that could extract value and identify users in the blockchain.
+https://etherscan.io/}) and are subject to data mining that could extract value and identify users in the blockchain.
 \paragraph{\textbf{Private transactions.}}AZTEC Protocol was conceived to enable privacy on public blockchains.
 It uses zero-knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions.
-zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier.
-zk-SNARKs are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
+zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier; they are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
 Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK},
@@
 Ants-Review integrates a few \emph{ERC20}\footnote[12]{\emph{EIP 20}.
-https://eips.ethereum.org/EIPS/eip-20.} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol.
+https://eips.ethereum.org/EIPS/eip-20} tokens, each of whom plays an integral role in the functioning and anonymity of the decentralized protocol.
 ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
@@
 In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.
-https://github.com/ethereum/EIPs/issues/1724.} will be used as a template to build an AZTEC-compatible asset.
+https://github.com/ethereum/EIPs/issues/1724} will be used as a template to build an AZTEC-compatible asset.
 \\
@@
 We have described how Ants-Review protocol can solve the limitations of the current peer review system (see 2.1).
-In particular we showed how the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see §AntsReview in 3.2); the social and cognitive biases via anonymity granted by AZTEC Protocol (see §Privacy in 3.2); the slowness of the process, the need for evaluation of the peer-reviews themselves and the need for increasing the number of reviewers through the creation of the community of Anters.
+In particular, the lack of recognition, the lack of transparency, fraud and misconduct can be solved via the Ants-Review Protocol (see §AntsReview in 3.2); the social and cognitive biases can be counteracted via anonymity granted by AZTEC Protocol (see §Privacy in 3.2); the slowness of the process, the need for evaluation of the peer reviews themselves and the need for increasing the number of reviewers can be worked out through the creation of the community of Anters.
 \subsection{Future developments}
@@
 As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}).
-Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn.}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
+Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
 This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value (\emph{ibidem}).

### 2020-09-25 article.tex
Final push (fixing bugs BibTex).

--- 2020-09-25 paper-v1.tex
@@
 \includegraphics[scale=0.28]{AntsReview}
-\small{
 \caption{Exagones represent the protocol's smart contracts.
@@
 \textbf{g} Integration with ERC20 tokens like \emph{Dai}, and De-Fi services like MakerDAO DSR to be used in the protocol.
-\textbf{h} Library used by the protocol for secure contract development with the modules listed.}}
+\textbf{h} Library used by the protocol for secure contract development with the modules listed.}
 \label{fig:contracts}
@@
 \\
-Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:} https://openzeppelin.com.} that is used to define the Issuer and Peer-Reviewer Roles.
+Access management of the Ants-Review protocol is defined and controlled by \emph{AntsReviewRoles} (see Figure \ref{fig:contracts} (\textbf{b})), implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Library\footnote[10]{\emph{OpenZeppelin Library}.\textsc{URL:} https://openzeppelin.com} that is used to define the Issuer and Peer-Reviewer Roles.
 AntsReviewRoles also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, granted by default to the owner of the smart contracts, to pause (or unpause) all the functions in case of a security emergency, such as an attack to the smart contracts.
@@
 It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
-A Faucet (see Figure \ref{fig:contracts}, (\text{d}) is implemented to distribute ANTS token on Kovan Testnet for testing purposes.
+A Faucet (see Figure \ref{fig:contracts}, (\textbf{d})) is implemented to distribute ANTS token on Kovan Testnet for testing purposes.
 zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
@@
 Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
-This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value (\emph{ibidem}).
+This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value.
 In our proposal we also decoupled the peer review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
@@
 Harris and the four external anonymous peer reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.
-The project was born during ETH Turin hackathon (April 24-26th 2020) and further developed in the Kernel Gitcoin program (July 7th - August 31st 2020).}
 
@@
 \bibliographystyle{splncs04}
-\bibliography{ref1-intro.bib,ref2-peerreview.bib,ref2-related.bib, ref3-system.bib,ref4-discuss.bib, ref5-extra.bib}
+\bibliography{references.bib}
 

### 2020-11-15 article.tex
quick recap

@@
 %
-\title{Ants-Review: a Protocol for Open Anonymous Peer Reviews}
+\title{Ants-Review: an Ethereum-Based Protocol for Peer Reviews}
 %
@@
 %
-\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
-Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}
+\author{Bianca Trovò\inst{1}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
+Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}
 %
@@
 %
-\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
-Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
+\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France
 \email{bianca.trovo@alumni.unitn.it}\\
-\and
-Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
-Blockchain Engineer, London, UK \\
+\and Smart Contract Engineer, London, United Kingdom \\
 \email{nazzareno@nazzarenomassari.com}}
@@
 To promote ethical behaviour and inclusiveness the system implements a gamified mechanism that allows the whole community to evaluate the peer-reviews and vote for the best ones.
-\keywords{Blockchain \and Ethereum \and Peer-review \and Incentivization.}
+\keywords{Blockchain \and Ethereum \and Peer-review \and Incentivization}
 \end{abstract}
@@
 
-\begin{figure}
+\begin{figure}[htp]
 \centering

### 2020-11-23 article.tex
Commit by @naszam

@@
 %
-\title{Ants-Review: an Ethereum-Based Protocol for Peer Reviews}
+\title{Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentiviced Open Peer Reviews}
 %
@@
 \author{Bianca Trovò\inst{1}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
-Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}
+Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{These authors equally contributed to this work.}}
 %
@@
 \email{bianca.trovo@alumni.unitn.it}\\
-\and Smart Contract Engineer, London, United Kingdom \\
+\and MakerDAO, Community Development, London, United Kingdom \\
 \email{nazzareno@nazzarenomassari.com}}

### 2020-11-23 article.tex
@biancasama's commits: declaration of interests, capital letters, spacing and minor things.

@@
 %
-\title{Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentiviced Open Peer Reviews}
+\title{Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentivized Open Peer Reviews}
 %
@@
 \author{Bianca Trovò\inst{1}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
-Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{These authors equally contributed to this work.}}
+Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{The two authors contributed equally to this work}}
 %
@@
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the Proof of Existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
+Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
 In particular, a `blockchainified science'\cite{BlockchainforScience} could `reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
@@
 Peer review is still the only quality control mechanism devoted to evaluating scientific outcomes.
-The purpose of peer review is \say{improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.}\cite{Gropp-PeerRevStress}.
+The purpose of peer review is, to cite \cite{Gropp-PeerRevStress}: \say{improving the quality of the published paper, determining the originality of the manuscript, determining the importance of the findings, detecting fraud, and detecting plagiarism.}.
 However, the system is `ﬂawed' and outdated \cite{Smith2006} and presents multifaceted issues \cite{Walker2015-trends}, here reviewed.
@@
 If the editorial decision is to send the manuscript for review, the handling editor personally selects potential reviewers.
-The reviewers identity is usually only known to the editor but is hidden to the authors or the other reviewers themselves (\emph{single-blind review}).
+The authors' identity is usually known to the reviewer but the reviewers' identity is hidden to the authors or among the other reviewers themselves (\emph{single-blind review}).
 Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript and sometimes substantially improving the draft.
@@
 To solve this problem some journals have implemented \emph{double-blind review} process (the identity of both authors and reviewers are masked) which seems to reduce the bias towards minorities.
-\subsubsection{Peer reviews need to be...reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: \say{Who watches the watchers?} \cite{Tennant2017-F1000R}.
-\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists\cite{tragedy-reviewers,Warne-RewRev}.
+\subsubsection{Peer reviews need to be...
+reviewed.} There is high variability in the reliability and depth of reviews and a recurrent question is: \say{Who watches the watchers?} \cite{Tennant2017-F1000R}.
+\subsubsection{Need for more reviewers.} There is a disproportion between the progressive increase in journal publications and the number of experienced reviewers selected for the task which demands an expansion of the reviewer's pool including early career scientists \cite{tragedy-reviewers,Warne-RewRev}.
 \\
@@
 
-\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties.
+\subsubsection{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by bounties.
 Bounties are prizes or monetary rewards given for completing a task before a deadline \cite{BountyGit}.
@@
 
-\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflicts of interest, it's important to be able to track back the identities of the contributors to a peer-review report.
+\subsubsection{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflicts of interest, it is important to be able to track back the identities of the contributors to a peer-review report.
 This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped.
@@
 IPFS' hashes are then stored inside the smart contracts' state that is timestamped into the Ethereum blocks where  the transactions take place; there, data remains unaltered and indelible.
-This notarization process is called Proof of Existence (PoE) and allows manual verification of the existence of the document.
-\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof, a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
+This notarization process is called proof of existence (PoE) and allows manual verification of the existence of the document.
+\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach via Ethereum’s externally owned accounts (EOA) addresses and zero-knowledge proof (ZKP), a cryptographic method where a party can prove to another party the possession of certain information, like a secret key, without revealing that information (see 3.2).
 
@@
 An interesting addition would be to introduce a rank of peer reviews resulting from the community feedback via a voting process (see 4.1).
-It's conceivable that the community members that engage in assessing the quality of peer reviews could be incentivized as well.
+It is conceivable that the community members that engage in assessing the quality of peer reviews could be incentivized as well.
 This solution would create a self-reinforcing ethical behaviour where the fair evaluation of peer reviews would be also in the interest of the agents at play.
@@
 \emph{Tokenomics}, which manages the incentive mechanism of the system (see Figure \ref{fig:contracts}, (\textbf{c, d, e, h})).
-\newline Agents in the platform are: issuers, peer reviewers, approvers and contributors (Anters, members of the Ants-Review Community).
+\newline Agents in the platform are: issuers, peer reviewers, approvers and contributors (or Anters, members of the Ants-Review Community).
 
@@
 Clouds represent integrations into the protocol.
-Rectangles represent smart contracts' libraries.
+Rectangles represent the smart contracts' libraries.
 \textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
@@
 AntsReview (see Figure \ref{fig:contracts} (\textbf{a})), the core of the smart contracts written in \emph{Solidity}\footnote[7]{\emph{Solidity}.
-https://solidity.readthedocs.io.}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine, is deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.
-\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121.}.
+https://solidity.readthedocs.io}, a contract-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM), is deployed on Ethereum Kovan Testnet\footnote[8]{\emph{AntsReview}.
+\newline https://kovan.etherscan.io/address/0x85be8F04482cBB920550d5469E4dEdD6e1788121}.
 AntsReview implements a bounty-like system (based on the \emph{StandardBounties} contract\footnote[9]{\emph{StandardBounties.sol}.
@@
 However, the privacy is limited by the fact that both the blockchain and its transactions are public.
-Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan \footnote[11]{\emph{Etherscan}.
+Therefore, the details of the transactions are visible to anyone by browsing a block explorer (such as Etherscan\footnote[11]{\emph{Etherscan}.
 https://etherscan.io/}) and are subject to data mining that could extract value and identify users in the blockchain.
 \paragraph{\textbf{Private transactions.}}AZTEC Protocol was conceived to enable privacy on public blockchains.
-It uses zero-knowledge Succinct Non-Interactive Argument of Knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions.
-zk-SNARKs are zero-knowledge proofs that require no interaction between prover and verifier; they are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
-Future developments will allow to leverage on Permutations over Lagrange-bases for Oecumenical Noninteractive arguments of Knowledge (PLONK) \cite{PLONK},
+It uses zero-knowledge succinct non-interactive argument of knowledge (zk-SNARKs) \cite{zSNARK} and homomorphic encryption \cite{HomEncr} to validate encrypted transactions.
+zk-SNARKs are ZKP that require no interaction between prover and verifier; they are used inside the Ants-Review protocol via the zkANTS token to allow private transactions between the agents.
+Future developments will allow to leverage on permutations over Lagrange-bases for oecumenical  noninteractive arguments of knowledge (PLONK) \cite{PLONK},
 a universal zk-SNARK construction that reduces gas costs and improves scalability.
@@
 ANTS (see Figure \ref{fig:contracts}, (\textbf{c})) is the primary protocol token and can be staked into an AntReview.
-It's implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
+It is implemented by inheriting \emph{ERC20.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
 A Faucet (see Figure \ref{fig:contracts}, (\textbf{d})) is implemented to distribute ANTS token on Kovan Testnet for testing purposes.
 zkANTS (see Figure \ref{fig:contracts}, (\textbf{e})) is a wrapper of ANTS that will be used inside the protocol to allow for private transactions among the agents of the protocol, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters.
-It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
+It will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine, \emph{ACE.sol}, a contract responsible for validating the set of AZTEC ZKPs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens.
 In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token that follows the EIP-1724 standard \footnote[13]{\emph{EIP  1724}.
@@
 Recently, pre-print servers, such as \emph{arXiv} and \emph{biorXiv}, started integrating peer-review services into their platforms: \emph{PREreview}\footnote[19]{\emph{PREreview.} https://www.prereview.org}, \emph{PeerCommunityIn}\footnote[20]{\emph{PeerCommunityIn} https://peercommunityin.org}, \emph{Review Commons}\footnote[21]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review}\footnote[22]{\emph{PrePrint Review.} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}.
-This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value.
+This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer review platforms and justify their added value \cite{Tennant2017-F1000R}.
 In our proposal we also decoupled the peer review process from the publishers giving it back to the scientific community and applying incentives from tokenomics.
 We foresee that the future will evolve towards community-driven peer reviews: peer reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
-\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)\cite{AIRA}} leaving to the reviewers the sole task of evaluating the content of a paper.
+\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)} \cite{AIRA} leaving to the reviewers the sole task of evaluating the content of a paper.
 Building smart contracts for peer reviews might accelerate this novel process of standardization.
 We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.
-
+\small{
 \section{Conclusion}
@@
 
-\small{
 \subsubsection{Supplementary Material}
-Source code, DOI: 10.5281/zenodo.3971044; 
-\newline DApp: https://ants-review.on.fleek.co.
+Source code, DOI: 10.5281/zenodo.3971044; DApp: https://ants-review.on.fleek.co.
 
 \subsubsection{Declaration of Competing Interest}
-The authors declare no competing interests.
+This work was developed during the ETHTurin Hackathon 2020 and the Kernel Fellowship program 2020. These organizations had no financial role in the design and implementation of this protocol.
 
@@
 Tambussi, Andy Tudhope, Mark Beylin, Evan C.
-Harris and the four external anonymous peer reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.
+Harris and the four external anonymous peer reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}
 

### 2020-11-23 article.tex
Latest commits.

@@
 %
-\title{Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentivized Open Peer Reviews}
+\title{Ants-Review: an Ethereum-Based Privacy-Oriented Protocol for Incentivized Open Peer Reviews}
 %
@@
 \subsubsection{Declaration of Competing Interest}
-This work was developed during the ETHTurin Hackathon 2020 and the Kernel Fellowship program 2020. These organizations had no financial role in the design and implementation of this protocol.
+This work was mainly developed during the ETHTurin Hackathon 2020 and the Gitcoin Kernel Fellowship program 2020.
+These organizations, as well as the authors' affiliations, had no financial role in the design and implementation of the protocol.
 

### 2020-12-24 article.tex
Prova: update affiliations but the title is suppressed because it's too long

@@
 %
-\author{Bianca Trovò\inst{1}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
-Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{The two authors contributed equally to this work}}
+\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
+Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}\thanks{The two authors contributed equally to this work}}
 %
@@
 %
-\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France
+\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France \and
+Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, UNICOG, INSERM U992, Paris-Saclay, France
 \email{bianca.trovo@alumni.unitn.it}\\
-\and MakerDAO, Community Development, London, United Kingdom \\
+\and MakerDAO, Community Development, London, United Kingdom \and
+WFIL Labs\\
 \email{nazzareno@nazzarenomassari.com}}
@@
 Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers).
-Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}.
-In particular, a `blockchainified science'\cite{BlockchainforScience} could `reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
+Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only}) \cite{ReviewBlockchain2019}.
+In particular, a `blockchainified science' \cite{BlockchainforScience} could `reduce waste' \cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.
 \newline A thorny issue in the academic system that can - and we think it should - be tackled by blockchain concerns the status and accreditation of peer review, the core process of scientific validation currently facing a crisis \cite{Gropp-PeerRevStress}.
@@
 Following the example of models offered by journals peer review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}.
-http://nprc.incf.org} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}.
-https://www.researchsquare.com} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.
+http://nprc.incf.org} and independent companies like \emph{ResearchSquare}\footnote[5]{\emph{ResearchSquare}.
+https://www.researchsquare.com} and \emph{Peerage of Science}\footnote[6]{\emph{Peerage of Science}.
 https://www.peerageofscience.org}, that provide a scientific peer review service, peer reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer reviews').
@@
 \subsubsection{Supplementary Material}
-Source code, DOI: 10.5281/zenodo.3971044; DApp: https://ants-review.on.fleek.co.
+Source code, DOI: 10.5281/zenodo.3971044;DApp: https://ants-review.on.fleek.co.
 

### 2020-12-24 article.tex
Prova titolo breve

@@
 %
-\title{Ants-Review: an Ethereum-Based Privacy-Oriented Protocol for Incentivized Open Peer Reviews}
+\title{Ants-Review: an Ethereum-Based Protocol for Incentivized Peer Reviews}
 %
@@
 \institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France \and
-Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, UNICOG, INSERM U992, Paris-Saclay, France
+Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, Cognitive Neuroimaging Unit, Saclay, France
 \email{bianca.trovo@alumni.unitn.it}\\
-\and MakerDAO, Community Development, London, United Kingdom \and
-WFIL Labs\\
+\and MakerDAO, Community Development, London, United Kingdom \\
 \email{nazzareno@nazzarenomassari.com}}

### 2020-12-24 article.tex
abstract update

@@
 Here, to solve this issue, we propose a blockchain-based incentive system that rewards scientists for peer-reviewing other scientists’ work and that builds up trust and reputation.
-We designed a protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum.
+We designed a privacy-oriented protocol of smart contracts called Ants-Review that allows authors to issue a bounty for open anonymous peer-reviews on Ethereum.
 If requirements are met, peer reviews will be accepted and paid by the approver proportionally to their assessed quality.

### 2021-02-15 article.tex
Changes for Springer

@@
 %
-\title{Ants-Review: an Ethereum-Based Protocol for Incentivized Peer Reviews}
+\title{Ants-Review: a Privacy-Oriented Protocol for Incentivized Open Peer-Reviews on Ethereum}
 %
@@
 Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, Cognitive Neuroimaging Unit, Saclay, France
-\email{bianca.trovo@alumni.unitn.it}\\
+\email{bianca.trovo@protonmail.com}\\
 \and MakerDAO, Community Development, London, United Kingdom \\
@@
 \subsubsection{Supplementary Material}
-Source code, DOI: 10.5281/zenodo.3971044;DApp: https://ants-review.on.fleek.co.
+Source code, DOI: 10.5281/zenodo.3971044; \\DApp: https://ants-review.on.fleek.co.
 
@@
 
-\subsubsection{Acknowledgements} We would like to thank Matteo A.
-Tambussi, Andy Tudhope, Mark Beylin, Evan C.
-Harris and the four external anonymous peer reviewers for useful comments and revisions; Mitrasish Mukherjee for contributions on the interface.}
+\subsubsection{Acknowledgements} We would like to thank Andy Tudhope, Mark Beylin, Matteo A.
+Tambussi, Evan C.
+Harris and the four external anonymous peer reviewers for useful comments and revisions; the FDAPP 2020 workshop chairs and speakers for questions and feedback; Mitrasish Mukherjee for contributions on the interface.}
 
